### 2024-11-22 article/aanda.tex
generate eps figure and begin to write article

%                                                                 aa.dem
% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
%                              according to the author-year natbib style

%
\documentclass{aa}

%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\begin{document}

   \title{Hydrodynamics of giant planet formation}

   \subtitle{I. Overviewing the $\kappa$-mechanism}

   \author{G. Wuchterl
          \inst{1}
          \and
          C. Ptolemy\inst{2}\fnmsep\thanks{Just to show the usage
          of the elements in the author field}
          }

   \institute{Institute for Astronomy (IfA), University of Vienna,
              T\"urkenschanzstrasse 17, A-1180 Vienna\\
              \email{wuchterl@amok.ast.univie.ac.at}
         \and
             University of Alexandria, Department of Geography, ...\\
             \email{c.ptolemy@hipparch.uheaven.space}
             \thanks{The university of heaven temporarily does not
                     accept e-mails}
             }

   \date{Received September 15, 1996; accepted March 16, 1997}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {To investigate the physical nature of the `nuc\-leated instability' of
   proto giant planets, the stability of layers
   in static, radiative gas spheres is analysed on the basis of Baker's
   standard one-zone model.}
  % aims heading (mandatory)
   {It is shown that stability
   depends only upon the equations of state, the opacities and the local
   thermodynamic state in the layer. Stability and instability can
   therefore be expressed in the form of stability equations of state
   which are universal for a given composition.}
  % methods heading (mandatory)
   {The stability equations of state are
   calculated for solar composition and are displayed in the domain
   $-14 \leq \lg \rho / \mathrm{[g\, cm^{-3}]} \leq 0 $,
   $ 8.8 \leq \lg e / \mathrm{[erg\, g^{-1}]} \leq 17.7$. These displays
   may be
   used to determine the one-zone stability of layers in stellar
   or planetary structure models by directly reading off the value of
   the stability equations for the thermodynamic state of these layers,
   specified
   by state quantities as density $\rho$, temperature $T$ or
   specific internal energy $e$.
   Regions of instability in the $(\rho,e)$-plane are described
   and related to the underlying microphysical processes.}
  % results heading (mandatory)
   {Vibrational instability is found to be a common phenomenon
   at temperatures lower than the second He ionisation
   zone. The $\kappa$-mechanism is widespread under `cool'
   conditions.}
  % conclusions heading (optional), leave it empty if necessary 
   {}

   \keywords{giant planet formation --
                $\kappa$-mechanism --
                stability of gas spheres
               }

   \maketitle
%
%-------------------------------------------------------------------

\section{Introduction}

   In the \emph{nucleated instability\/} (also called core
   instability) hypothesis of giant planet
   formation, a critical mass for static core  envelope
   protoplanets has been found. \citet{mizuno} determined
   the critical mass of the core to be about $12 \,M_\oplus$
   ($M_\oplus=5.975 \times 10^{27}\,\mathrm{g}$ is the Earth mass), which
   is independent of the outer boundary
   conditions and therefore independent of the location in the
   solar nebula. This critical value for the core mass corresponds
   closely to the cores of today's giant planets.

   Although no hydrodynamical study has been available many workers
   conjectured that a collapse or rapid contraction will ensue
   after accumulating the critical mass. The main motivation for
   this article
   is to investigate the stability of the static envelope at the
   critical mass. With this aim the local, linear stability of static
   radiative gas  spheres is investigated on the basis of Baker's
   (\citeyear{baker}) standard one-zone model.

   Phenomena similar to the ones described above for giant planet
   formation have been found in hydrodynamical models concerning
   star formation where protostellar cores explode
   (Tscharnuter \citeyear{tscharnuter}, Balluch \citeyear{balluch}),
   whereas earlier studies found quasi-steady collapse flows. The
   similarities in the (micro)physics, i.e., constitutive relations of
   protostellar cores and protogiant planets serve as a further
   motivation for this study.

%--------------------------------------------------------------------
\section{Baker's standard one-zone model}

%-------------------------------------- Two column figure (place early!)
   \begin{figure*}
   \centering
   %%%\includegraphics{empty.eps}
   %%%\includegraphics{empty.eps}
   %%%\includegraphics{empty.eps}
   \caption{Adiabatic exponent $\Gamma_1$.
               $\Gamma_1$ is plotted as a function of
               $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
               density $\mathrm{[g\,cm^{-3}]}$.}
              \label{FigGam}%
    \end{figure*}
%
   In this section the one-zone model of \citet{baker},
   originally used to study the Cephe{\"{\i}}d pulsation mechanism, will
   be briefly reviewed. The resulting stability criteria will be
   rewritten in terms of local state variables, local timescales and
   constitutive relations.

   \citet{baker} investigates the stability of thin layers in
   self-gravitating,
   spherical gas clouds with the following properties:
   \begin{itemize}
      \item hydrostatic equilibrium,
      \item thermal equilibrium,
      \item energy transport by grey radiation diffusion.
   \end{itemize}
   For the one-zone-model Baker obtains necessary conditions
   for dynamical, secular and vibrational (or pulsational)
   stability (Eqs.\ (34a,\,b,\,c) in Baker \citeyear{baker}). Using Baker's
   notation:
   %%begin novalidate
   \[
      \begin{array}{lp{0.8\linewidth}}
         M_{r}  & mass internal to the radius $r$     \\
         m               & mass of the zone                    \\
         r_0             & unperturbed zone radius             \\
         \rho_0          & unperturbed density in the zone     \\
         T_0             & unperturbed temperature in the zone \\
         L_{r0}          & unperturbed luminosity              \\
         E_{\mathrm{th}} & thermal energy of the zone
      \end{array}
   \]
   %%end novalidate
\noindent
   and with the definitions of the \emph{local cooling time\/}
   (see Fig.~\ref{FigGam})
   \begin{equation}
      \tau_{\mathrm{co}} = \frac{E_{\mathrm{th}}}{L_{r0}} \,,
   \end{equation}
   and the \emph{local free-fall time}
   \begin{equation}
      \tau_{\mathrm{ff}} =
         \sqrt{ \frac{3 \pi}{32 G} \frac{4\pi r_0^3}{3 M_{\mathrm{r}}}
}\,,
   \end{equation}
   Baker's $K$ and $\sigma_0$ have the following form:
   \begin{eqnarray}
      \sigma_0 & = & \frac{\pi}{\sqrt{8}}
                     \frac{1}{ \tau_{\mathrm{ff}}} \\
      K        & = & \frac{\sqrt{32}}{\pi} \frac{1}{\delta}
                        \frac{ \tau_{\mathrm{ff}} }
                             { \tau_{\mathrm{co}} }\,;
   \end{eqnarray}
   where $ E_{\mathrm{th}} \approx m (P_0/{\rho_0})$ has been used and
   \begin{equation}
   \begin{array}{l}
      \delta = - \left(
                    \frac{ \partial \ln \rho }{ \partial \ln T }
                 \right)_P \\
      e=mc^2
   \end{array}
   \end{equation}
   is a thermodynamical quantity which is of order $1$ and equal to $1$
   for nonreacting mixtures of classical perfect gases. The physical
   meaning of $ \sigma_0 $ and $K$ is clearly visible in the equations
   above. $\sigma_0$ represents a frequency of the order one per
   free-fall time. $K$ is proportional to the ratio of the free-fall
   time and the cooling time. Substituting into Baker's criteria, using
   thermodynamic identities and definitions of thermodynamic quantities,
   \begin{displaymath}
      \Gamma_1      = \left( \frac{ \partial \ln P}{ \partial\ln \rho}
                           \right)_{S}    \, , \;
      \chi^{}_\rho  = \left( \frac{ \partial \ln P}{ \partial\ln \rho}
                           \right)_{T}    \, , \;
      \kappa^{}_{P} = \left( \frac{ \partial \ln \kappa}{ \partial\ln P}
                           \right)_{T}
   \end{displaymath}
   \begin{displaymath}
      \nabla_{\mathrm{ad}} = \left( \frac{ \partial \ln T}
                             { \partial\ln P} \right)_{S} \, , \;
      \chi^{}_T       = \left( \frac{ \partial \ln P}
                             { \partial\ln T} \right)_{\rho} \, , \;
      \kappa^{}_{T}   = \left( \frac{ \partial \ln \kappa}
                             { \partial\ln T} \right)_{T}
   \end{displaymath}
   one obtains, after some pages of algebra, the conditions for
   \emph{stability\/} given
   below:
   \begin{eqnarray}
      \frac{\pi^2}{8} \frac{1}{\tau_{\mathrm{ff}}^2}
                ( 3 \Gamma_1 - 4 )
         & > & 0 \label{ZSDynSta} \\
      \frac{\pi^2}{\tau_{\mathrm{co}}
                   \tau_{\mathrm{ff}}^2}
                   \Gamma_1 \nabla_{\mathrm{ad}}
                   \left[ \frac{ 1- 3/4 \chi^{}_\rho }{ \chi^{}_T }
                          ( \kappa^{}_T - 4 )
                        + \kappa^{}_P + 1
                   \right]
        & > & 0 \label{ZSSecSta} \\
     \frac{\pi^2}{4} \frac{3}{\tau_{ \mathrm{co} }
                              \tau_{ \mathrm{ff} }^2
                             }
         \Gamma_1^2 \, \nabla_{\mathrm{ad}} \left[
                                   4 \nabla_{\mathrm{ad}}
                                   - ( \nabla_{\mathrm{ad}} \kappa^{}_T
                                     + \kappa^{}_P
                                     )
                                   - \frac{4}{3 \Gamma_1}
                                \right]
        & > & 0   \label{ZSVibSta}
   \end{eqnarray}
%
   For a physical discussion of the stability criteria see \citet{baker} or \citet{cox}.

   We observe that these criteria for dynamical, secular and
   vibrational stability, respectively, can be factorized into
   \begin{enumerate}
      \item a factor containing local timescales only,
      \item a factor containing only constitutive relations and
         their derivatives.
   \end{enumerate}
   The first factors, depending on only timescales, are positive
   by definition. The signs of the left hand sides of the
   inequalities~(\ref{ZSDynSta}), (\ref{ZSSecSta}) and (\ref{ZSVibSta})
   therefore depend exclusively on the second factors containing
   the constitutive relations. Since they depend only
   on state variables, the stability criteria themselves are \emph{
   functions of the thermodynamic state in the local zone}. The
   one-zone stability can therefore be determined
   from a simple equation of state, given for example, as a function
   of density and
   temperature. Once the microphysics, i.e.\ the thermodynamics
   and opacities (see Table~\ref{KapSou}), are specified (in practice
   by specifying a chemical composition) the one-zone stability can
   be inferred if the thermodynamic state is specified.
   The zone -- or in
   other words the layer -- will be stable or unstable in
   whatever object it is imbedded as long as it satisfies the
   one-zone-model assumptions. Only the specific growth rates
   (depending upon the time scales) will be different for layers
   in different objects.

%--------------------------------------------------- One column table
   \begin{table}
      \caption[]{Opacity sources.}
         \label{KapSou}
     $$ 
         \begin{array}{p{0.5\linewidth}l}
            \hline
            \noalign{\smallskip}
            Source      &  T / {[\mathrm{K}]} \\
            \noalign{\smallskip}
            \hline
            \noalign{\smallskip}
            Yorke 1979, Yorke 1980a & \leq 1700^{\mathrm{a}}     \\
%           Yorke 1979, Yorke 1980a & \leq 1700             \\
            Kr\"ugel 1971           & 1700 \leq T \leq 5000 \\
            Cox \& Stewart 1969     & 5000 \leq             \\
            \noalign{\smallskip}
            \hline
         \end{array}
     $$ 
   \end{table}
%
   We will now write down the sign (and therefore stability)
   determining parts of the left-hand sides of the inequalities
   (\ref{ZSDynSta}), (\ref{ZSSecSta}) and (\ref{ZSVibSta}) and thereby
   obtain \emph{stability equations of state}.

   The sign determining part of inequality~(\ref{ZSDynSta}) is
   $3\Gamma_1 - 4$ and it reduces to the
   criterion for dynamical stability
   \begin{equation}
     \Gamma_1 > \frac{4}{3}\,\cdot
   \end{equation}
   Stability of the thermodynamical equilibrium demands
   \begin{equation}
      \chi^{}_\rho > 0, \;\;  c_v > 0\, ,
   \end{equation}
   and
   \begin{equation}
      \chi^{}_T > 0
   \end{equation}
   holds for a wide range of physical situations.
   With
   \begin{eqnarray}
      \Gamma_3 - 1 = \frac{P}{\rho T} \frac{\chi^{}_T}{c_v}&>&0\\
      \Gamma_1     = \chi_\rho^{} + \chi_T^{} (\Gamma_3 -1)&>&0\\
      \nabla_{\mathrm{ad}}  = \frac{\Gamma_3 - 1}{\Gamma_1}         &>&0
   \end{eqnarray}
   we find the sign determining terms in inequalities~(\ref{ZSSecSta})
   and (\ref{ZSVibSta}) respectively and obtain the following form
   of the criteria for dynamical, secular and vibrational
   \emph{stability}, respectively:
   \begin{eqnarray}
      3 \Gamma_1 - 4 =: S_{\mathrm{dyn}}      > & 0 & \label{DynSta}  \\
%
      \frac{ 1- 3/4 \chi^{}_\rho }{ \chi^{}_T } ( \kappa^{}_T - 4 )
         + \kappa^{}_P + 1 =: S_{\mathrm{sec}} > & 0 & \label{SecSta} \\
%
      4 \nabla_{\mathrm{ad}} - (\nabla_{\mathrm{ad}} \kappa^{}_T
                             + \kappa^{}_P)
                             - \frac{4}{3 \Gamma_1} =: S_{\mathrm{vib}}
                                      > & 0\,.& \label{VibSta}
   \end{eqnarray}
   The constitutive relations are to be evaluated for the
   unperturbed thermodynamic state (say $(\rho_0, T_0)$) of the zone.
   We see that the one-zone stability of the layer depends only on
   the constitutive relations $\Gamma_1$,
   $\nabla_{\mathrm{ad}}$, $\chi_T^{},\,\chi_\rho^{}$,
   $\kappa_P^{},\,\kappa_T^{}$.
   These depend only on the unperturbed
   thermodynamical state of the layer. Therefore the above relations
   define the one-zone-stability equations of state
   $S_{\mathrm{dyn}},\,S_{\mathrm{sec}}$
   and $S_{\mathrm{vib}}$. See Fig.~\ref{FigVibStab} for a picture of
   $S_{\mathrm{vib}}$. Regions of secular instability are
   listed in Table~1.

%
%                                                One column figure
%----------------------------------------------------------------- 
   \begin{figure}
   \centering
   %%%\includegraphics[width=3cm]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%-----------------------------------------------------------------

\section{Conclusions}

   \begin{enumerate}
      \item The conditions for the stability of static, radiative
         layers in gas spheres, as described by Baker's (\citeyear{baker})
         standard one-zone model, can be expressed as stability
         equations of state. These stability equations of state depend
         only on the local thermodynamic state of the layer.
      \item If the constitutive relations -- equations of state and
         Rosseland mean opacities -- are specified, the stability
         equations of state can be evaluated without specifying
         properties of the layer.
      \item For solar composition gas the $\kappa$-mechanism is
         working in the regions of the ice and dust features
         in the opacities, the $\mathrm{H}_2$ dissociation and the
         combined H, first He ionization zone, as
         indicated by vibrational instability. These regions
         of instability are much larger in extent and degree of
         instability than the second He ionization zone
         that drives the Cephe{\"\i}d pulsations.
   \end{enumerate}

\begin{acknowledgements}
      Part of this work was supported by the German
      \emph{Deut\-sche For\-schungs\-ge\-mein\-schaft, DFG\/} project
      number Ts~17/2--1.
\end{acknowledgements}

% WARNING
%-------------------------------------------------------------------
% Please note that we have included the references to the file aa.dem in
% order to compile it, but we ask you to:
%
% - use BibTeX with the regular commands:
%   \bibliographystyle{aa} % style aa.bst
%   \bibliography{Yourfile} % your references Yourfile.bib
%
% - join the .bib files when you upload your source files
%-------------------------------------------------------------------

\begin{thebibliography}{}

  \bibitem[Baker(1966)]{baker} Baker, N. 1966,
      in Stellar Evolution,
      ed.\ R. F. Stein,\& A. G. W. Cameron
      (Plenum, New York) 333

   \bibitem[Balluch(1988)]{balluch} Balluch, M. 1988,
      A\&A, 200, 58

   \bibitem[Cox(1980)]{cox} Cox, J. P. 1980,
      Theory of Stellar Pulsation
      (Princeton University Press, Princeton) 165

   \bibitem[Cox(1969)]{cox69} Cox, A. N.,\& Stewart, J. N. 1969,
      Academia Nauk, Scientific Information 15, 1

   \bibitem[Mizuno(1980)]{mizuno} Mizuno H. 1980,
      Prog. Theor. Phys., 64, 544

   \bibitem[Tscharnuter(1987)]{tscharnuter} Tscharnuter W. M. 1987,
      A\&A, 188, 55

   \bibitem[Terlevich(1992)]{terlevich} Terlevich, R. 1992, in ASP Conf. Ser. 31, 
      Relationships between Active Galactic Nuclei and Starburst Galaxies, 
      ed. A. V. Filippenko, 13

   \bibitem[Yorke(1980a)]{yorke80a} Yorke, H. W. 1980a,
      A\&A, 86, 286

   \bibitem[Zheng(1997)]{zheng} Zheng, W., Davidsen, A. F., Tytler, D. \& Kriss, G. A.
      1997, preprint
\end{thebibliography}

\end{document}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Example below of non-structurated natbib references  
To use the v8.3 macros with this form of composition of bibliography, 
the option "bibyear" should be added to the command line 
"\documentclass[bibyear]{aa}".
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{}

  \bibitem[1966]{baker} Baker, N. 1966,
      in Stellar Evolution,
      ed.\ R. F. Stein,\& A. G. W. Cameron
      (Plenum, New York) 333

   \bibitem[1988]{balluch} Balluch, M. 1988,
      A\&A, 200, 58

   \bibitem[1980]{cox} Cox, J. P. 1980,
      Theory of Stellar Pulsation
      (Princeton University Press, Princeton) 165

   \bibitem[1969]{cox69} Cox, A. N.,\& Stewart, J. N. 1969,
      Academia Nauk, Scientific Information 15, 1

   \bibitem[1980]{mizuno} Mizuno H. 1980,
      Prog. Theor. Phys., 64, 544

   \bibitem[1987]{tscharnuter} Tscharnuter W. M. 1987,
      A\&A, 188, 55

   \bibitem[1992]{terlevich} Terlevich, R. 1992, in ASP Conf. Ser. 31, 
      Relationships between Active Galactic Nuclei and Starburst Galaxies, 
      ed. A. V. Filippenko, 13

   \bibitem[1980a]{yorke80a} Yorke, H. W. 1980a,
      A\&A, 86, 286

   \bibitem[1997]{zheng} Zheng, W., Davidsen, A. F., Tytler, D. \& Kriss, G. A.
      1997, preprint
\end{thebibliography}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Examples for figures using graphicx
A guide "Using Imported Graphics in LaTeX2e"  (Keith Reckdahl)
is available on a lot of LaTeX public servers or ctan mirrors.
The file is : epslatex.pdf 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------
%                 A figure as large as the width of the column
%-------------------------------------------------------------
   \begin{figure}
   \centering
   \includegraphics[width=\hsize]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%-------------------------------------------------------------
%                                    One column rotated figure
%-------------------------------------------------------------
   \begin{figure}
   \centering
   \includegraphics[angle=-90,width=3cm]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%-------------------------------------------------------------
%                        Figure with caption on the right side 
%-------------------------------------------------------------
   \begin{figure}
   \sidecaption
   \includegraphics[width=3cm]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%-------------------------------------------------------------
%                                Figure with a new BoundingBox 
%-------------------------------------------------------------
   \begin{figure}
   \centering
   \includegraphics[bb=10 20 100 300,width=3cm,clip]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%-------------------------------------------------------------
%                                      The "resizebox" command 
%-------------------------------------------------------------
   \begin{figure}
   \resizebox{\hsize}{!}
            {\includegraphics[bb=10 20 100 300,clip]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure}
%
%-------------------------------------------------------------
%                                             Two column Figure 
%-------------------------------------------------------------
   \begin{figure*}
   \resizebox{\hsize}{!}
            {\includegraphics[bb=10 20 100 300,clip]{empty.eps}
      \caption{Vibrational stability equation of state
               $S_{\mathrm{vib}}(\lg e, \lg \rho)$.
               $>0$ means vibrational stability.
              }
         \label{FigVibStab}
   \end{figure*}
%
%-------------------------------------------------------------
%                                             Simple A&A Table
%-------------------------------------------------------------
%
\begin{table}
\caption{Nonlinear Model Results}             % title of Table
\label{table:1}      % is used to refer this table in the text
\centering                          % used for centering table
\begin{tabular}{c c c c}        % centered columns (4 columns)
\hline\hline                 % inserts double horizontal lines
HJD & $E$ & Method\#2 & Method\#3 \\    % table heading 
\hline                        % inserts single horizontal line
   1 & 50 & $-837$ & 970 \\      % inserting body of the table
   2 & 47 & 877    & 230 \\
   3 & 31 & 25     & 415 \\
   4 & 35 & 144    & 2356 \\
   5 & 45 & 300    & 556 \\ 
\hline                                   %inserts single line
\end{tabular}
\end{table}
%
%-------------------------------------------------------------
%                                             Two column Table 
%-------------------------------------------------------------
%
\begin{table*}
\caption{Nonlinear Model Results}             
\label{table:1}      
\centering          
\begin{tabular}{c c c c l l l }     % 7 columns 
\hline\hline       
                      % To combine 4 columns into a single one 
HJD & $E$ & Method\#2 & \multicolumn{4}{c}{Method\#3}\\ 
\hline                    
   1 & 50 & $-837$ & 970 & 65 & 67 & 78\\  
   2 & 47 & 877    & 230 & 567& 55 & 78\\
   3 & 31 & 25     & 415 & 567& 55 & 78\\
   4 & 35 & 144    & 2356& 567& 55 & 78 \\
   5 & 45 & 300    & 556 & 567& 55 & 78\\
\hline                  
\end{tabular}
\end{table*}
%
%-------------------------------------------------------------
%                                          Table with notes 
%-------------------------------------------------------------
%
% A single note
\begin{table}
\caption{\label{t7}Spectral types and photometry for stars in the
  region.}
\centering
\begin{tabular}{lccc}
\hline\hline
Star&Spectral type&RA(J2000)&Dec(J2000)\\
\hline
69           &B1\,V     &09 15 54.046 & $-$50 00 26.67\\
49           &B0.7\,V   &*09 15 54.570& $-$50 00 03.90\\
LS~1267~(86) &O8\,V     &09 15 52.787&11.07\\
24.6         &7.58      &1.37 &0.20\\
\hline
LS~1262      &B0\,V     &09 15 05.17&11.17\\
MO 2-119     &B0.5\,V   &09 15 33.7 &11.74\\
LS~1269      &O8.5\,V   &09 15 56.60&10.85\\
\hline
\end{tabular}
\tablefoot{The top panel shows likely members of Pismis~11. The second
panel contains likely members of Alicante~5. The bottom panel
displays stars outside the clusters.}
\end{table}
%
% More notes
%
\begin{table}
\caption{\label{t7}Spectral types and photometry for stars in the
  region.}
\centering
\begin{tabular}{lccc}
\hline\hline
Star&Spectral type&RA(J2000)&Dec(J2000)\\
\hline
69           &B1\,V     &09 15 54.046 & $-$50 00 26.67\\
49           &B0.7\,V   &*09 15 54.570& $-$50 00 03.90\\
LS~1267~(86) &O8\,V     &09 15 52.787&11.07\tablefootmark{a}\\
24.6         &7.58\tablefootmark{1}&1.37\tablefootmark{a}   &0.20\tablefootmark{a}\\
\hline
LS~1262      &B0\,V     &09 15 05.17&11.17\tablefootmark{b}\\
MO 2-119     &B0.5\,V   &09 15 33.7 &11.74\tablefootmark{c}\\
LS~1269      &O8.5\,V   &09 15 56.60&10.85\tablefootmark{d}\\
\hline
\end{tabular}
\tablefoot{The top panel shows likely members of Pismis~11. The second
panel contains likely members of Alicante~5. The bottom panel
displays stars outside the clusters.\\
\tablefoottext{a}{Photometry for MF13, LS~1267 and HD~80077 from
Dupont et al.}
\tablefoottext{b}{Photometry for LS~1262, LS~1269 from
Durand et al.}
\tablefoottext{c}{Photometry for MO2-119 from
Mathieu et al.}
}
\end{table}
%
%-------------------------------------------------------------
%                                       Table with references 
%-------------------------------------------------------------
%
\begin{table*}[h]
 \caption[]{\label{nearbylistaa2}List of nearby SNe used in this work.}
\begin{tabular}{lccc}
 \hline \hline
  SN name &
  Epoch &
 Bands &
  References \\
 &
  (with respect to $B$ maximum) &
 &
 \\ \hline
1981B   & 0 & {\it UBV} & 1\\
1986G   &  $-$3, $-$1, 0, 1, 2 & {\it BV}  & 2\\
1989B   & $-$5, $-$1, 0, 3, 5 & {\it UBVRI}  & 3, 4\\
1990N   & 2, 7 & {\it UBVRI}  & 5\\
1991M   & 3 & {\it VRI}  & 6\\
\hline
\noalign{\smallskip}
\multicolumn{4}{c}{ SNe 91bg-like} \\
\noalign{\smallskip}
\hline
1991bg   & 1, 2 & {\it BVRI}  & 7\\
1999by   & $-$5, $-$4, $-$3, 3, 4, 5 & {\it UBVRI}  & 8\\
\hline
\noalign{\smallskip}
\multicolumn{4}{c}{ SNe 91T-like} \\
\noalign{\smallskip}
\hline
1991T   & $-$3, 0 & {\it UBVRI}  &  9, 10\\
2000cx  & $-$3, $-$2, 0, 1, 5 & {\it UBVRI}  & 11\\ %
\hline
\end{tabular}
\tablebib{(1)~\citet{branch83};
(2) \citet{phillips87}; (3) \citet{barbon90}; (4) \citet{wells94};
(5) \citet{mazzali93}; (6) \citet{gomez98}; (7) \citet{kirshner93};
(8) \citet{patat96}; (9) \citet{salvo01}; (10) \citet{branch03};
(11) \citet{jha99}.
}
\end{table}
%-------------------------------------------------------------
%                      A rotated Two column Table in landscape  
%-------------------------------------------------------------
\begin{sidewaystable*}
\caption{Summary for ISOCAM sources with mid-IR excess 
(YSO candidates).}\label{YSOtable}
\centering
\begin{tabular}{crrlcl} 
\hline\hline             
ISO-L1551 & $F_{6.7}$~[mJy] & $\alpha_{6.7-14.3}$ 
& YSO type$^{d}$ & Status & Comments\\
\hline
  \multicolumn{6}{c}{\it New YSO candidates}\\ % To combine 6 columns into a single one
\hline
  1 & 1.56 $\pm$ 0.47 & --    & Class II$^{c}$ & New & Mid\\
  2 & 0.79:           & 0.97: & Class II ?     & New & \\
  3 & 4.95 $\pm$ 0.68 & 3.18  & Class II / III & New & \\
  5 & 1.44 $\pm$ 0.33 & 1.88  & Class II       & New & \\
\hline
  \multicolumn{6}{c}{\it Previously known YSOs} \\
\hline
  61 & 0.89 $\pm$ 0.58 & 1.77 & Class I & \object{HH 30} & Circumstellar disk\\
  96 & 38.34 $\pm$ 0.71 & 37.5& Class II& MHO 5          & Spectral type\\
\hline
\end{tabular}
\end{sidewaystable*}
%-------------------------------------------------------------
%                      A rotated One column Table in landscape  
%-------------------------------------------------------------
\begin{sidewaystable}
\caption{Summary for ISOCAM sources with mid-IR excess 
(YSO candidates).}\label{YSOtable}
\centering
\begin{tabular}{crrlcl} 
\hline\hline             
ISO-L1551 & $F_{6.7}$~[mJy] & $\alpha_{6.7-14.3}$ 
& YSO type$^{d}$ & Status & Comments\\
\hline
  \multicolumn{6}{c}{\it New YSO candidates}\\ % To combine 6 columns into a single one
\hline
  1 & 1.56 $\pm$ 0.47 & --    & Class II$^{c}$ & New & Mid\\
  2 & 0.79:           & 0.97: & Class II ?     & New & \\
  3 & 4.95 $\pm$ 0.68 & 3.18  & Class II / III & New & \\
  5 & 1.44 $\pm$ 0.33 & 1.88  & Class II       & New & \\
\hline
  \multicolumn{6}{c}{\it Previously known YSOs} \\
\hline
  61 & 0.89 $\pm$ 0.58 & 1.77 & Class I & \object{HH 30} & Circumstellar disk\\
  96 & 38.34 $\pm$ 0.71 & 37.5& Class II& MHO 5          & Spectral type\\
\hline
\end{tabular}
\end{sidewaystable}
%
%-------------------------------------------------------------
%                              Table longer than a single page  
%-------------------------------------------------------------
% All long tables will be placed automatically at the end of the document
%
\longtab{
\begin{longtable}{lllrrr}
\caption{\label{kstars} Sample stars with absolute magnitude}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endfirsthead
\caption{continued.}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endhead
\hline
\endfoot
%%
Gl 33    & 6.37 & K2 V & 7.46 & S & 0.043170\\
Gl 66AB  & 6.26 & K2 V & 8.15 & S & 0.260478\\
Gl 68    & 5.87 & K1 V & 7.47 & P & 0.026610\\
         &      &      &      & H & 0.008686\\
Gl 86 
\footnote{Source not included in the HRI catalog. See Sect.~5.4.2 for details.}
         & 5.92 & K0 V & 10.91& S & 0.058230\\
\end{longtable}
}
%
%-------------------------------------------------------------
%                              Table longer than a single page
%                                            and in landscape, 
%                    in the preamble, use: \usepackage{lscape}
%-------------------------------------------------------------

% All long tables will be placed automatically at the end of the document
%
\longtab{
\begin{landscape}
\begin{longtable}{lllrrr}
\caption{\label{kstars} Sample stars with absolute magnitude}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endfirsthead
\caption{continued.}\\
\hline\hline
Catalogue& $M_{V}$ & Spectral & Distance & Mode & Count Rate \\
\hline
\endhead
\hline
\endfoot
%%
Gl 33    & 6.37 & K2 V & 7.46 & S & 0.043170\\
Gl 66AB  & 6.26 & K2 V & 8.15 & S & 0.260478\\
Gl 68    & 5.87 & K1 V & 7.47 & P & 0.026610\\
         &      &      &      & H & 0.008686\\
Gl 86
\footnote{Source not included in the HRI catalog. See Sect.~5.4.2 for details.}
         & 5.92 & K0 V & 10.91& S & 0.058230\\
\end{longtable}
\end{landscape}
}
%
%-------------------------------------------------------------
%               Appendices have to be placed at the end, after
%                                        \end{thebibliography}
%-------------------------------------------------------------
\end{thebibliography}

\begin{appendix} %First appendix
\section{Background galaxy number counts and shear noise-levels}
Because the optical images used in this analysis...
\begin{figure*}%f1
\includegraphics[width=10.9cm]{1787f23.eps}
\caption{Shown in greyscale is a...}
\label{cl12301}
\end{figure*}

In this case....
\begin{figure*}
\centering
\includegraphics[width=16.4cm,clip]{1787f24.ps}
\caption{Plotted above...}
\label{appfig}
\end{figure*}

Because the optical images...

\section{Title of Second appendix.....} %Second appendix
These studies, however, have faced...
\begin{table}
\caption{Complexes characterisation.}\label{starbursts}
\centering
\begin{tabular}{lccc}
\hline \hline
Complex & $F_{60}$ & 8.6 &  No. of  \\
...
\hline
\end{tabular}
\end{table}

The second method produces...
\end{appendix}
%
%
\end{document}

%
%-------------------------------------------------------------
%          For the appendices, table longer than a single page
%-------------------------------------------------------------

% Table will be print automatically at the end of the document, 
% after the whole appendices

\begin{appendix} %First appendix
\section{Background galaxy number counts and shear noise-levels}

% In the appendices do not forget to put the counter of the table 
% as an option

\longtab[1]{
\begin{longtable}{lrcrrrrrrrrl}
\caption{Line data and abundances ...}\\
\hline
\hline
Def & mol & Ion & $\lambda$ & $\chi$ & $\log gf$ & N & e &  rad & $\delta$ & $\delta$ 
red & References \\
\hline
\endfirsthead
\caption{Continued.} \\
\hline
Def & mol & Ion & $\lambda$ & $\chi$ & $\log gf$ & B & C &  rad & $\delta$ & $\delta$ 
red & References \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
A & CH & 1 &3638 & 0.002 & $-$2.551 &  &  &  & $-$150 & 150 &  Jorgensen et al. (1996) \\                    
\end{longtable}
}% End longtab
\end{appendix}

%-------------------------------------------------------------
%                   For appendices and landscape, large table:
%                    in the preamble, use: \usepackage{lscape}
%-------------------------------------------------------------

\begin{appendix} %First appendix
%
\longtab[1]{
\begin{landscape}
\begin{longtable}{lrcrrrrrrrrl}
...
\end{longtable}
\end{landscape}
}% End longtab
\end{appendix}

%%%% End of aa.dem

### 2024-11-22 article/article.tex
generate eps figure and begin to write article

\documentclass{aa}
\usepackage{graphicx}
\usepackage{txfonts}

\begin{document}

   \title{Self-interacting dark matter model without dark energy in cosmology}

   \author{Yixuan Zhu}

   \institute{Department of Astronomy, Beijing Normal University.
   Beijing 100875.
   PR China}

   \date{}

   \abstract{}

   \keywords{}

   \maketitle

\section{Introduction}

\section{The basic equations in the IDM model}

   We assume that the total density of the cosmic fluid obeys
   the collisional Boltzmann equation()
   \begin{equation}
      \dot{\rho}+3H\rho+\kappa\rho^2-2\Psi=0,
   \end{equation}
   where $\rho$ is the total energy-density of the cosmic fluid,
   containing dark matter, baryons, and any type of exotic energy,
   $\Psi$ is the rate of creation of DM particle pairs, and the
   annihilation parameter $\kappa(\geq0)$ is given by:
   \begin{equation}
      \kappa=\frac{\langle\sigma u\rangle}{M_x},\label{eq:2}
   \end{equation}
   where $\sigma$ is the cross-section for annihilation, $u$ is
   the mean particle velocity, and $M_x$ is the mass of the DM
   particle.
   Compared to the usual fluid equation, the effective pressure term
   is \begin{equation}
      P=\frac{\kappa\rho^2-\Psi}{3H}.
   \end{equation}
   When $\kappa\rho^2-\Psi<0,$ what means that the IDM particle
   creation term is larger than the annihilation item, IDM may serve
   as a negative pressure source in the global dynamics of the Universe,
   like the role of Dark Energy in the general cosmolgical models.

   Basilakos \& Plionis (2009) identified two functional forms for which
   the previous Boltzmann equation can be solved analytically.
   Refering to Appendix B in (), only one of these two is of interest
   because it provides a "$\propto a^{-3}$" dependence of the scale factor,
   which is \begin{equation}
      \Psi(a)=aH(a)R(a)=C_1(n+3)a^nH(a)+\kappa C_1^2a^{2m}.
   \end{equation}
   And the total energy density is
   \begin{equation}
      \rho(a)=C_1a^n+\frac{a^{-3}F(a)}{C_2-\int_1^{a}x^{-3}f(x)F(x)\mathrm{d}x},\label{eq:5}
   \end{equation}
   where $f(a)=-\kappa/[aH(a)],$ and the kernal function $F(a)$ has
   the form \begin{equation}
      F(a)=\exp\left[-2\kappa C_1\int_1^{a}\frac{x^{n-1}}{H(x)}\mathrm{d}x\right].
   \end{equation}
   The first term of Eq.(\ref{eq:5}) is the density corresponding to the
   residual matter creation that results from a possible disequilibrium
   between the particle creation and annihilation processes, while the second
   term can be viewed as the energy density of the self-IDM particles that are
   dominated by the annihilation process.

\subsection{Model 1: relation to the $\varLambda$CDM model}

   If $n=0$, the global density evolution can be transformed as
   \begin{equation}
      \rho(a)=C_1+a^{-3}\frac{e^{-2\kappa C_1(t-t_0)}}{C_2-\kappa Z(t)},
   \end{equation}
   where $Z(t)=\int_{t_0}^ta^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$().
   Using the usual unit-less $\Omega$-like parameterization, we obtain that
   \begin{equation}
      \left(\frac{H}{H_0}\right)^2=\Omega_{1,0}+\frac{\Omega_{1,0}\Omega_{2,0}a^{-3}e^{-2\kappa C_1(t-t_0)}}
      {\Omega_{1,0}+\kappa C_1\Omega_{2,0}Z(t)},
   \end{equation}
   where $\Omega_{1,0}=8\pi GC_1/3H_0^2$ and $\Omega_{2,0}=8\pi G/3H_0^2C_2$,
   which related to $\Omega_{\Lambda}$ and $\Omega_m$ in the $\Lambda$CDM model,
   respectively.
   From Eq.({\ref{eq:2}}), we can also give the mass of the DM particle
   related to the range of $\kappa C_1$(in the unit of Gyr${}^{-1}$)
   \begin{equation}
      M_x=\frac{3.325\times10^{-12}}{\kappa C_1}
      \frac{\langle\sigma u\rangle}{10^{-23}}h^2(1-\Omega_{2,0})\,\text{GeV},
   \end{equation}
   where $h\equiv H_0/[100\text{km/s/Mpc}]$.

\subsection{Model 2 : relation to the wCDM model}

   If $\kappa=0$, the global density evolution can be written as
   \begin{equation}
      \rho(a)=\mathcal{D}a^{-3}+C_1a^{n},
   \end{equation}
   where $\mathcal{D}=C_2-C-1$. The conditions in which the current 
   model acts as a quintessence cosmology are given by $\mathcal{D}>0,
   C_1>0,$ and $w_{\text{IDM}}=-1-n/3$. This solution is mathematically
   equivalent to that of the gravitational matter creation model of().
   The Hubble flow is now given by
   \begin{equation}
      \left(\frac{H}{H_0}\right)^2=\Omega_{2,0}a^{-3}+\Omega_{1,0}a^{n},
   \end{equation}
   where $\Omega_{2,0}=8\pi G\mathcal{D}/3H_0^2$ and 
   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.()

\section{Observational data}

\section{Constraint results}

\section{Conclusions}

\end{document}

### 2024-11-22 BAO/result.py

@@ -113,7 +113,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_1.svg')
+    plt.savefig('./pictures/bao_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -124,7 +124,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_2.svg')
+    plt.savefig('./pictures/bao_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-22 OHD/result.py

@@ -86,7 +86,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_1.svg')
+    plt.savefig('./pictures/ohd_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -98,7 +98,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_2.svg')
+    plt.savefig('./pictures/ohd_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-22 SNe/result2.py

@@ -80,7 +80,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_1.svg')
+    plt.savefig('./pictures/sne_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -92,7 +92,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_2.svg')
+    plt.savefig('./pictures/sne_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-22 multimethods/methods2.py

@@ -119,7 +119,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_1.svg')
+    plt.savefig('./pictures/ohd_sne_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -131,7 +131,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_2.svg')
+    plt.savefig('./pictures/ohd_sne_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-22 pdf_cdf.py

@@ -101,7 +101,7 @@ def main():
     plt.figure()
     sns.kdeplot(data=pdf, legend=True, bw_adjust=2, cut=0)
     plt.xlabel(r'$\Omega_{2,0}$')
-    plt.savefig('./pictures/pdf_1.svg')
+    plt.savefig('./pictures/pdf_1.eps')
     plt.show()
     # plot kc1 cdf
     cdf = pd.DataFrame({'OHD': flat_samples_OHD[:, 1], 'SN Ia': flat_samples_SNe[:, 1], 'OHD+SN Ia': flat_samples_m2[:, 1],
@@ -110,7 +110,7 @@ def main():
     sns.ecdfplot(data=cdf, legend=True)
     plt.grid()
     plt.xlabel(r'$\log_{10}(\kappa C_1/Gyr^{-1})$')
-    plt.savefig('./pictures/cdf_1.svg')
+    plt.savefig('./pictures/cdf_1.eps')
     plt.show()
     # plot mx cdf
     cdf_ = pd.DataFrame({'OHD': Mx_OHD, 'SN Ia': Mx_SNe, 'OHD+SN Ia': Mx_m2, 'BAO': Mx_BAO, 'OHD+SN Ia+BAO': Mx})
@@ -118,7 +118,7 @@ def main():
     sns.ecdfplot(data=cdf_, legend=True)
     plt.grid()
     plt.xlabel(r'$\log_{10}(M_x/GeV)$')
-    plt.savefig('./pictures/cdf_2.svg')
+    plt.savefig('./pictures/cdf_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-22 wIDM/BAO.py

@@ -47,7 +47,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_widm_1.svg')
+    plt.savefig('./pictures/bao_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -56,5 +56,5 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_widm_2.svg')
+    plt.savefig('./pictures/bao_widm_2.eps')
     plt.show()

### 2024-11-22 wIDM/OHD.py

@@ -47,7 +47,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_widm_1.svg')
+    plt.savefig('./pictures/ohd_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -56,7 +56,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_widm_2.svg')
+    plt.savefig('./pictures/ohd_widm_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-22 wIDM/SNe.py

@@ -47,7 +47,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_widm_1.svg')
+    plt.savefig('./pictures/sne_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -56,7 +56,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_widm_2.svg')
+    plt.savefig('./pictures/sne_widm_2.eps')
     plt.show()
 
 if __name__ == "__main__":

### 2024-11-22 wIDM/methods2.py

@@ -48,7 +48,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_widm_1.svg')
+    plt.savefig('./pictures/ohd_sne_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -57,5 +57,5 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_widm_2.svg')
+    plt.savefig('./pictures/ohd_sne_widm_2.eps')
     plt.show()

### 2024-11-22 wIDM/methods3.py

@@ -49,7 +49,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='m')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_bao_widm_1.svg')
+    plt.savefig('./pictures/ohd_sne_bao_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -58,5 +58,5 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='m')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_bao_widm_2.svg')
+    plt.savefig('./pictures/ohd_sne_bao_widm_2.eps')
     plt.show()

### 2024-11-25 article/article.tex
add data

@@
 
-   Basilakos \& Plionis (2009) identified two functional forms for which
+   \cite{refId0} identified two functional forms for which
    the previous Boltzmann equation can be solved analytically.
-   Refering to Appendix B in (), only one of these two is of interest
+   Refering to Appendix B in \cite{refId0}, only one of these two is of interest
    because it provides a "$\propto a^{-3}$" dependence of the scale factor,
@@
    \end{equation}
-   where $Z(t)=\int_{t_0}^ta^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$().
+   where $Z(t)=\int_{t_0}^ta^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$(\cite{refId0}).
    Using the usual unit-less $\Omega$-like parameterization, we obtain that
@@
    where $\Omega_{2,0}=8\pi G\mathcal{D}/3H_0^2$ and 
-   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.()
+   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.(\cite{refId0})
 
 \section{Observational data}
+
+   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
+   observational $H(z)$ data (OHD)(\cite{Zhang_2014};\cite{PhysRevD.71.123001};
+   \cite{M.Moresco_2012};\cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037}),
+   the Pantheon+ set of 1701 SNe Ia (), the CMB data from
+   Planck 2018 and the BAO data from DESI 2024.
+
+\subsection{The observational H(z) data}
+
+   It is widely known that the Hubble parameter $H(z)$ depends on
+   the differential age as a function of redshift $z$ in the form
+   \begin{equation}
+      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},
+   \end{equation}
+   which provides a direct measurement on $H(z)$ based on
+   $\mathrm{d}z/\mathrm{d}t$.
+   OHD measurements have recently been acquired mainly employing
+   cosmic chronometers (CC). The CC method is used to provide 33 observational
+   data points, which are taken in the redshift range [0, 1.965].
+   The Table \ref{tab:1} lists the OHD dataset used in this analysis.
+   In this case, $\chi^2$ can be defined as
+   \begin{equation}
+      \chi_{\text{OHD}}^2=\sum_i^{33}\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
+   \end{equation}
+
+   \begin{table}[htbp]
+      \caption{The OHD dataset}
+      \centering
+      \begin{tabular}{llll}
+         \hline\hline
+         $z$ & $H(z)$ & 1$\sigma$ uncertainty & Reference \\
+         \hline     
+         0.07 & 69 & $\pm$19.6 & \cite{Zhang_2014} \\
+         0.09 & 69 & $\pm$12 & \cite{PhysRevD.71.123001} \\
+         0.12 & 68.6 & $\pm$26.2 & \cite{Zhang_2014} \\
+         0.17 & 83 & $\pm$8 & \cite{PhysRevD.71.123001} \\
+         0.179 & 75 & $\pm$4 & \cite{M.Moresco_2012} \\
+         0.199 & 75 & $\pm$5 & \cite{M.Moresco_2012} \\
+         0.2 & 72.9 & $\pm$29.6 & \cite{Zhang_2014} \\
+         0.27 & 77 & $\pm$14 & \cite{PhysRevD.71.123001} \\
+         0.28 & 88.8 & $\pm$36.6 & \cite{Zhang_2014} \\
+         0.352 & 83 & $\pm$14 & \cite{M.Moresco_2012} \\
+         0.3802 & 83 & $\pm$13.5 & \cite{Moresco_2016}  \\
+         0.4 & 95 & $\pm$17 & \cite{PhysRevD.71.123001} \\
+         0.4004 & 77 & $\pm$10.2 & \cite{Moresco_2016} \\
+         0.4247 & 87.1 & $\pm$11.2 & \cite{Moresco_2016} \\
+         0.4497 & 92.8 & $\pm$12.9 & \cite{Moresco_2016} \\
+         0.47 & 89 & $\pm$34 & \cite{10.1093/mnras/stx301} \\
+         0.4783 & 80.9 & $\pm$9 & \cite{Moresco_2016} \\
+         0.48 & 97 & $\pm$62 & \cite{Daniel.Stern_2010} \\
+         0.593 & 104 & $\pm$13 & \cite{M.Moresco_2012} \\
+         0.68 & 92 & $\pm$8 & \cite{M.Moresco_2012} \\
+         0.75 & 98.8 & $\pm$33.6 & \cite{Borghi_2022} \\
+         0.781 & 105 & $\pm$12 & \cite{M.Moresco_2012} \\
+         0.8 & 113.1 & 15.1 & \cite{Jiao_2023} \\
+         0.875 & 125 & $\pm$17 & \cite{M.Moresco_2012} \\
+         0.88 & 90 & $\pm$40 & \cite{Daniel.Stern_2010} \\
+         0.9 & 117 & $\pm$23 & \cite{PhysRevD.71.123001} \\
+         1.037 & 154 & $\pm$20 & \cite{M.Moresco_2012} \\
+         1.3 & 168 & $\pm$17 & \cite{PhysRevD.71.123001} \\
+         1.363 & 160 & $\pm$33.6 & \cite{10.1093/mnrasl/slv037} \\
+         1.43 & 177 & $\pm$18 & \cite{PhysRevD.71.123001} \\
+         1.53 & 140 & $\pm$14 & \cite{PhysRevD.71.123001} \\
+         1.75 & 202 & $\pm$40 & \cite{PhysRevD.71.123001} \\
+         1.965 & 186.5 & $\pm$50.4 & \cite{10.1093/mnrasl/slv037} \\
+         \hline    
+      \end{tabular}
+      \label{tab:1}
+   \end{table}
+
+\subsection{The observational SNe Ia data}
+
+   SNe Ia have long been used as "standard candles". It is
 
@@
 
+\bibliographystyle{aa}
+\bibliography{reference}
+
 \end{document}

### 2024-11-25 BAO/result.py

@@ -113,7 +113,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_1.eps')
+    plt.savefig('./article/pictures/bao_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -124,7 +124,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_2.eps')
+    plt.savefig('./article/pictures/bao_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 CMB/dtauda.f90

@@ -1,0 +1,27 @@
+function dtauda(this,a)
+
+    use results
+
+    implicit none
+    class(CAMBdata) :: this
+    real(dl), intent(in) :: a
+    real(dl) :: dtauda
+    real(dl) :: list(100000,2)
+    integer :: i, j, iostat
+
+    open(10, file='temp.txt')
+    do i=1,100000
+        read(10, *, iostat=iostat) list(i,:)
+        if (iostat /= 0) exit
+    end do
+    close(10)
+    
+    j = sum(minloc(abs(a-list(:,1))))
+    if (j == 1) then
+        dtauda = list(1,2)
+    else
+        dtauda = (list(j,2)-list(j-1,2))/(list(j,1)-list(j-1,1))*(a-list(j,1))+list(j,2)
+    end if
+    write(*,*) 'a=', a, 'dtauda=', dtauda
+
+end function dtauda

### 2024-11-25 OHD/result.py

@@ -86,7 +86,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_1.eps')
+    plt.savefig('./article/pictures/ohd_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -98,7 +98,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_2.eps')
+    plt.savefig('./article/pictures/ohd_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 SNe/result2.py

@@ -80,7 +80,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_1.eps')
+    plt.savefig('./article/pictures/sne_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -92,7 +92,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_2.eps')
+    plt.savefig('./article/pictures/sne_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 multimethods/methods2.py

@@ -119,7 +119,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_1.eps')
+    plt.savefig('./article/pictures/ohd_sne_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -131,7 +131,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_2.eps')
+    plt.savefig('./article/pictures/ohd_sne_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 multimethods/methods3.py

@@ -178,7 +178,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='m')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_bao_1.eps')
+    plt.savefig('./article/pictures/ohd_sne_bao_1.eps')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -189,7 +189,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='m')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_bao_2.eps')
+    plt.savefig('./article/pictures/ohd_sne_bao_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 pdf_cdf.py

@@ -101,7 +101,7 @@ def main():
     plt.figure()
     sns.kdeplot(data=pdf, legend=True, bw_adjust=2, cut=0)
     plt.xlabel(r'$\Omega_{2,0}$')
-    plt.savefig('./pictures/pdf_1.eps')
+    plt.savefig('./article//pictures/pdf_1.eps')
     plt.show()
     # plot kc1 cdf
     cdf = pd.DataFrame({'OHD': flat_samples_OHD[:, 1], 'SN Ia': flat_samples_SNe[:, 1], 'OHD+SN Ia': flat_samples_m2[:, 1],
@@ -110,7 +110,7 @@ def main():
     sns.ecdfplot(data=cdf, legend=True)
     plt.grid()
     plt.xlabel(r'$\log_{10}(\kappa C_1/Gyr^{-1})$')
-    plt.savefig('./pictures/cdf_1.eps')
+    plt.savefig('./article/pictures/cdf_1.eps')
     plt.show()
     # plot mx cdf
     cdf_ = pd.DataFrame({'OHD': Mx_OHD, 'SN Ia': Mx_SNe, 'OHD+SN Ia': Mx_m2, 'BAO': Mx_BAO, 'OHD+SN Ia+BAO': Mx})
@@ -118,7 +118,7 @@ def main():
     sns.ecdfplot(data=cdf_, legend=True)
     plt.grid()
     plt.xlabel(r'$\log_{10}(M_x/GeV)$')
-    plt.savefig('./pictures/cdf_2.eps')
+    plt.savefig('./article/pictures/cdf_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 wIDM/BAO.py

@@ -47,7 +47,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_widm_1.eps')
+    plt.savefig('./article/pictures/bao_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -56,5 +56,5 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
     plt.tight_layout()
-    plt.savefig('./pictures/bao_widm_2.eps')
+    plt.savefig('./article/pictures/bao_widm_2.eps')
     plt.show()

### 2024-11-25 wIDM/OHD.py

@@ -47,7 +47,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_widm_1.eps')
+    plt.savefig('./article/pictures/ohd_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -56,7 +56,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_widm_2.eps')
+    plt.savefig('./article/pictures/ohd_widm_2.eps')
     plt.show()
 
 if __name__ == '__main__':

### 2024-11-25 wIDM/SNe.py

@@ -47,7 +47,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_widm_1.eps')
+    plt.savefig('./article/pictures/sne_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -56,7 +56,7 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()
-    plt.savefig('./pictures/sne_widm_2.eps')
+    plt.savefig('./article/pictures/sne_widm_2.eps')
     plt.show()
 
 if __name__ == "__main__":

### 2024-11-25 wIDM/methods3.py

@@ -49,7 +49,7 @@ def main():
     figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='m')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_bao_widm_1.eps')
+    plt.savefig('./article/pictures/ohd_sne_bao_widm_1.eps')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
@@ -58,5 +58,5 @@ def main():
     figure = corner.corner(combined_samples, levels=(0.6826,0.9544), labels=labels_, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='m')
     plt.tight_layout()
-    plt.savefig('./pictures/ohd_sne_bao_widm_2.eps')
+    plt.savefig('./article/pictures/ohd_sne_bao_widm_2.eps')
     plt.show()

### 2024-11-27 article/article.tex
rebuild the cmb methods and article

--- 2024-11-22 article/article.tex
@@
    We assume that the total density of the cosmic fluid obeys
-   the collisional Boltzmann equation()
+   the collisional Boltzmann equation
    \begin{equation}
@@
    as a negative pressure source in the global dynamics of the Universe,
-   like the role of Dark Energy in the general cosmolgical models.
+   like the role of Dark Energy in the general cosmological models.
 
-   Basilakos \& Plionis (2009) identified two functional forms for which
+   \cite{refId0} identified two functional forms for which
    the previous Boltzmann equation can be solved analytically.
-   Refering to Appendix B in (), only one of these two is of interest
+   Refering to Appendix B in \cite{refId0}, only one of these two is of interest
    because it provides a "$\propto a^{-3}$" dependence of the scale factor,
@@
    where $\Omega_{2,0}=8\pi G\mathcal{D}/3H_0^2$ and 
-   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.()
+   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.(\cite{refId0})
 
 \section{Observational data}
+
+   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
+   observational $H(z)$ data (OHD)(\cite{Zhang_2014};\cite{PhysRevD.71.123001};
+   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Moresco_2016};
+   \cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};\cite{Borghi_2022};
+   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (), the CMB data from
+   Planck 2018 and the BAO data from SDSS and DESI 2024.
+
+\subsection{The observational H(z) data}
+
+   It is widely known that the Hubble parameter $H(z)$ depends on
+   the differential age as a function of redshift $z$ in the form
+   \begin{equation}
+      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},
+   \end{equation}
+   which provides a direct measurement on $H(z)$ based on
+   $\mathrm{d}z/\mathrm{d}t$.
+   OHD measurements have recently been acquired mainly employing
+   cosmic chronometers (CC). The CC method is used to provide 33 observational
+   data points, which are taken in the redshift range [0.07, 1.965].
+   The Table \ref{tab:1} lists the OHD dataset used in this analysis.
+   In this case, $\chi^2$ can be defined as
+   \begin{equation}
+      \chi_{\text{OHD}}^2=\sum_i^{33}\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
+   \end{equation}
+
+   \begin{table}[htbp]
+      \caption{The OHD dataset}
+      \centering
+      \begin{tabular}{llll}
+         \hline\hline
+         $z$ & $H(z)$ & Reference \\
+         \hline     
+         0.07 & 69$\pm$19.6 & \cite{Zhang_2014} \\
+         0.09 & 69$\pm$12 & \cite{PhysRevD.71.123001} \\
+         0.12 & 68.6$\pm$26.2 & \cite{Zhang_2014} \\
+         0.17 & 83$\pm$8 & \cite{PhysRevD.71.123001} \\
+         0.179 & 75$\pm$4 & \cite{M.Moresco_2012} \\
+         0.199 & 75$\pm$5 & \cite{M.Moresco_2012} \\
+         0.2 & 72.9$\pm$29.6 & \cite{Zhang_2014} \\
+         0.27 & 77$\pm$14 & \cite{PhysRevD.71.123001} \\
+         0.28 & 88.8$\pm$36.6 & \cite{Zhang_2014} \\
+         0.352 & 83$\pm$14 & \cite{M.Moresco_2012} \\
+         0.3802 & 83$\pm$13.5 & \cite{Moresco_2016}  \\
+         0.4 & 95$\pm$17 & \cite{PhysRevD.71.123001} \\
+         0.4004 & 77$\pm$10.2 & \cite{Moresco_2016} \\
+         0.4247 & 87.1$\pm$11.2 & \cite{Moresco_2016} \\
+         0.4497 & 92.8$\pm$12.9 & \cite{Moresco_2016} \\
+         0.47 & 89$\pm$34 & \cite{10.1093/mnras/stx301} \\
+         0.4783 & 80.9$\pm$9 & \cite{Moresco_2016} \\
+         0.48 & 97$\pm$62 & \cite{Daniel.Stern_2010} \\
+         0.593 & 104$\pm$13 & \cite{M.Moresco_2012} \\
+         0.68 & 92$\pm$8 & \cite{M.Moresco_2012} \\
+         0.75 & 98.8$\pm$33.6 & \cite{Borghi_2022} \\
+         0.781 & 105$\pm$12 & \cite{M.Moresco_2012} \\
+         0.8 & 113.1$\pm$15.1 & \cite{Jiao_2023} \\
+         0.875 & 125$\pm$17 & \cite{M.Moresco_2012} \\
+         0.88 & 90$\pm$40 & \cite{Daniel.Stern_2010} \\
+         0.9 & 117$\pm$23 & \cite{PhysRevD.71.123001} \\
+         1.037 & 154$\pm$20 & \cite{M.Moresco_2012} \\
+         1.3 & 168$\pm$17 & \cite{PhysRevD.71.123001} \\
+         1.363 & 160$\pm$33.6 & \cite{10.1093/mnrasl/slv037} \\
+         1.43 & 177$\pm$18 & \cite{PhysRevD.71.123001} \\
+         1.53 & 140$\pm$14 & \cite{PhysRevD.71.123001} \\
+         1.75 & 202$\pm$40 & \cite{PhysRevD.71.123001} \\
+         1.965 & 186.5$\pm$50.4 & \cite{10.1093/mnrasl/slv037} \\
+         \hline    
+      \end{tabular}
+      \label{tab:1}
+   \end{table}
+
+\subsection{The observational SNe Ia data}
+
+   SNe Ia have long been used as "standard candles" to give a direct
+   measurement of their luminosity distance, and provides strong constraints
+   on cosmological parameters. We use the latest Pantheon+ data set of 1701 
+   SNe Ia samples, which covers the redshift range [0, 2.26].
+   \\We could use the simple likelihood function as
+   \begin{equation}
+      \chi_{S}^2=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
+   \end{equation}
+
+\subsection{The baryon acoustic oscillation data}
 

### 2024-11-27 CMB/dtauda.f90

@@ -1,27 +1,0 @@
-function dtauda(this,a)
-
-    use results
-
-    implicit none
-    class(CAMBdata) :: this
-    real(dl), intent(in) :: a
-    real(dl) :: dtauda
-    real(dl) :: list(100000,2)
-    integer :: i, j, iostat
-
-    open(10, file='temp.txt')
-    do i=1,100000
-        read(10, *, iostat=iostat) list(i,:)
-        if (iostat /= 0) exit
-    end do
-    close(10)
-    
-    j = sum(minloc(abs(a-list(:,1))))
-    if (j == 1) then
-        dtauda = list(1,2)
-    else
-        dtauda = (list(j,2)-list(j-1,2))/(list(j,1)-list(j-1,1))*(a-list(j,1))+list(j,2)
-    end if
-    write(*,*) 'a=', a, 'dtauda=', dtauda
-
-end function dtauda

### 2024-11-27 CMB/result.py

@@ -1,0 +1,115 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import emcee
+import corner
+import multiprocessing as mp
+import camb
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+from solution import solution
+from solution import const_c
+const_c /= 1000
+from cross_section import cross_section
+
+H0 = 67.5
+O20 = 0.3
+log_kC1 = -6.5
+
+file_path_TT = "./CMB/data/COM_PowerSpect_CMB-TT-full_R3.01.txt"
+data_TT = np.loadtxt(file_path_TT, skiprows=1)
+l_TT = data_TT[:,0]
+Dl_TT = data_TT[:,1]
+down_TT = data_TT[:,2]
+up_TT = data_TT[:,3]
+
+file_path_TE = "./CMB/data/COM_PowerSpect_CMB-TE-full_R3.01.txt"
+data_TE = np.loadtxt(file_path_TE, skiprows=1)
+l_TE = data_TE[:,0]
+Dl_TE = data_TE[:,1]
+down_TE = data_TE[:,2]
+up_TE = data_TE[:,3]
+
+file_path_EE = "./CMB/data/COM_PowerSpect_CMB-EE-full_R3.01.txt"
+data_EE = np.loadtxt(file_path_EE, skiprows=1)
+l_EE = data_EE[:,0]
+Dl_EE = data_EE[:,1]
+down_EE = data_EE[:,2]
+up_EE = data_EE[:,3]
+
+def chi_square(log_kC1, O20, H0):
+    z = solution(log_kC1, O20, H0)
+    a = 1 / (1 + z.y[0,:])
+    dota = -z.y[1,:] * a ** 2
+    dtauda = 1 / (a * dota) * const_c
+
+    pars = camb.set_params(H0=H0, ombh2=0.022, omch2=0.122, mnu=0.06, omk=0, tau=0.06,  
+                       As=2e-9, ns=0.965, halofit_version='mead', lmax=2600,
+                       a_list=a, dtauda_list=dtauda)
+    results = camb.get_results(pars)
+    powers = results.get_cmb_power_spectra(pars, CMB_unit='muK')
+    totCL = powers['total']
+    # totCL[:,0]=TT, totCL[:,1]=EE, totCL[:,3]=TE
[…]

### 2024-11-27 CMB/test.py

@@ -1,0 +1,64 @@
+import camb
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+from solution import solution
+from solution import const_c
+const_c /= 1000
+
+def main():
+    file_path_TT = "./CMB/data/COM_PowerSpect_CMB-TT-full_R3.01.txt"
+    data_TT = np.loadtxt(file_path_TT, skiprows=1)
+    l_TT = data_TT[:,0]
+    Dl_TT = data_TT[:,1]
+    down_TT = data_TT[:,2]
+    up_TT = data_TT[:,3]
+
+    file_path_TE = "./CMB/data/COM_PowerSpect_CMB-TE-full_R3.01.txt"
+    data_TE = np.loadtxt(file_path_TE, skiprows=1)
+    l_TE = data_TE[:,0]
+    Dl_TE = data_TE[:,1]
+    down_TE = data_TE[:,2]
+    up_TE = data_TE[:,3]
+
+    file_path_EE = "./CMB/data/COM_PowerSpect_CMB-EE-full_R3.01.txt"
+    data_EE = np.loadtxt(file_path_EE, skiprows=1)
+    l_EE = data_EE[:,0]
+    Dl_EE = data_EE[:,1]
+    down_EE = data_EE[:,2]
+    up_EE = data_EE[:,3]
+
+    z = solution(-6.5, 0.3, 67.3)
+    a = 1 / (1 + z.y[0,:])
+    dota = -z.y[1,:] * a ** 2
+    dtauda = 1 / (a * dota) * const_c
+
+    pars = camb.set_params(H0=67.3, ombh2=0.022, omch2=0.122, mnu=0.06, omk=0, tau=0.06,  
+                        As=2e-9, ns=0.965, halofit_version='mead', lmax=2600,
+                        a_list=a, dtauda_list=dtauda)
+    results = camb.get_results(pars)
+    powers = results.get_cmb_power_spectra(pars, CMB_unit='muK')
+    totCL = powers['total']
+    # totCL[:,0]=TT, totCL[:,1]=EE, totCL[:,3]=TE
+    th_TT = totCL[int(l_TT[0]):int(l_TT[-1])+1,0]
+    th_EE = totCL[int(l_EE[0]):int(l_EE[-1])+1,1]
[…]

### 2024-11-29 article/article.tex
move the cmb power sepctrum methods

@@
       M_x=\frac{3.325\times10^{-12}}{\kappa C_1}
-      \frac{\langle\sigma u\rangle}{10^{-23}}h^2(1-\Omega_{2,0})\,\text{GeV},
+      \frac{\langle\sigma u\rangle}{10^{-23}}h^2(1-\Omega_{2,0})\,\text{GeV},\label{eq:9}
    \end{equation}
@@
 
-\section{Observational data}
+\section{Dataset}
 
@@
    \cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};\cite{Borghi_2022};
-   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (), the CMB data from
+   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (\cite{Scolnic_2022}), the CMB data from
    Planck 2018 and the BAO data from SDSS and DESI 2024.
@@
 
-\subsection{The observational SNe Ia data}
+\subsection{Type Ia supernovae}
 
@@
    on cosmological parameters. We use the latest Pantheon+ data set of 1701 
-   SNe Ia samples, which covers the redshift range [0, 2.26].
-   \\We could use the simple likelihood function as
+   SNe Ia samples(\cite{Scolnic_2022}), which covers the redshift range [0, 2.26].
+
+   We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
+   host distances(\cite{Riess_2022}), which gives the $\mu_\text{data}$ and constrains $H_0$
+   in advance. To eliminate the influence of $M_b$, we give the likelihood function
+   as \begin{equation}
+      \chi_{\text{S}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
+   \end{equation}
+   where $A=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})^2/\sigma_i^2,
+   B=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})/\sigma_i^2,C=\sum_i^{1701}1/\sigma_i^2$,
+   the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
+   luminosity distance $d_L$ can be given as a function of redshift $z$
    \begin{equation}
-      \chi_{S}^2=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
+      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.
    \end{equation}
+   However, the Eq.(\ref{eq:9}) just need the $H_0$ to caculate the $M_x$
+   and we would still use the simple likelihood function as
+   \begin{equation}
+      \chi_{\text{SNe}}^2=A=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
+   \end{equation}
+   Apparently these two functions give the same constraints in $\Omega_{2,0}$
+   and $\kappa C_1$.
 
-\subsection{The baryon acoustic oscillation data}
+\subsection{Baryon acoustic oscillation}
+
+   The Baryon acoustic oscillation method (BAO) provides a key cosmological probe
+   sensitive to the cosmic expansion history with well-controlled systematics.
+   We use two BAO data sets from the SDSS(\cite{PhysRevD.103.083533}) and DESI 2024(\cite{desicollaboration2024desi2024vicosmological}),
+   which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
+
+   \begin{table}[htbp]
+      \caption{The BAO-only dataset from SDSS}
+      \centering
+      \begin{tabular}{lllll}
+         \hline\hline
+            $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
+            \hline
+            0.15 & & & 4.47$\pm$0.17 \\
+            0.38 & 10.23$\pm$0.17 & 25$\pm$0.76 & \\
+            0.51 & 13.36$\pm$0.21 & 22.33$\pm$0.58 & \\
+            0.7 & 17.86$\pm$0.33 & 19.33$\pm$0.53 & \\
+            0.85 & & & $18.33_{-0.62}^{+0.57}$ \\
+            1.48 & 30.69$\pm$0.8 & 13.26$\pm$0.55 & \\
+            2.33 & 37.6$\pm$1.9 & 8.93$\pm$0.28 & \\
+            2.33 & 37.3$\pm$1.7 & 9.08$\pm$0.34 & \\
+            \hline
+      \end{tabular}
+      \label{tab:2}
+   \end{table}
+
+   \begin{table}[htbp]
+      \caption{The BAO dataset from DESI 2024}
+      \centering
+      \begin{tabular}{lllll}
+         \hline\hline
+            $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
+            \hline
+            0.295 & & & 7.93$\pm$0.15 \\
+            0.51 & 13.62$\pm$0.25 & 20.98$\pm$0.61 & \\
+            0.706 & 16.85$\pm$0.32 & 20.08$\pm$0.6 & \\
+            0.93 & 21.71$\pm$0.28 & 17.88$\pm$0.35 & \\
+            1.317 & 27.79$\pm$0.69 & 13.82$\pm$0.42 & \\
+            1.491 & & & 26.07$\pm$0.67 \\
+            2.33 & 39.71$\pm$0.94 & 8.52$\pm$0.17 & \\
+            \hline
+      \end{tabular}
+      \label{tab:3}
+   \end{table}
+
+\subsection{Cosmic Microwave Background}
+
+   We adopt the $\Omega_bh^2$ from BBN,
+   give the constraint to $r_d$
 

### 2024-11-29 BAO/result.py

@@ -10,7 +10,6 @@ import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
 from solution import solution
 from solution import const_c
-const_c /= 1000
 from cross_section import cross_section
 
 # Prior values

### 2024-11-29 CMB/test.py

@@ -6,42 +6,47 @@ import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
 from solution import solution
 from solution import const_c
-const_c /= 1000
 
-def main():
-    file_path_TT = "./CMB/data/COM_PowerSpect_CMB-TT-full_R3.01.txt"
-    data_TT = np.loadtxt(file_path_TT, skiprows=1)
-    l_TT = data_TT[:,0]
-    Dl_TT = data_TT[:,1]
-    down_TT = data_TT[:,2]
-    up_TT = data_TT[:,3]
+file_path_TT = "./CMB/data/COM_PowerSpect_CMB-TT-full_R3.01.txt"
+data_TT = np.loadtxt(file_path_TT, skiprows=1)
+l_TT = data_TT[:,0]
+Dl_TT = data_TT[:,1]
+down_TT = data_TT[:,2]
+up_TT = data_TT[:,3]
 
-    file_path_TE = "./CMB/data/COM_PowerSpect_CMB-TE-full_R3.01.txt"
-    data_TE = np.loadtxt(file_path_TE, skiprows=1)
-    l_TE = data_TE[:,0]
-    Dl_TE = data_TE[:,1]
-    down_TE = data_TE[:,2]
-    up_TE = data_TE[:,3]
+file_path_TE = "./CMB/data/COM_PowerSpect_CMB-TE-full_R3.01.txt"
+data_TE = np.loadtxt(file_path_TE, skiprows=1)
+l_TE = data_TE[:,0]
+Dl_TE = data_TE[:,1]
+down_TE = data_TE[:,2]
+up_TE = data_TE[:,3]
 
-    file_path_EE = "./CMB/data/COM_PowerSpect_CMB-EE-full_R3.01.txt"
-    data_EE = np.loadtxt(file_path_EE, skiprows=1)
-    l_EE = data_EE[:,0]
-    Dl_EE = data_EE[:,1]
-    down_EE = data_EE[:,2]
-    up_EE = data_EE[:,3]
+file_path_EE = "./CMB/data/COM_PowerSpect_CMB-EE-full_R3.01.txt"
+data_EE = np.loadtxt(file_path_EE, skiprows=1)
+l_EE = data_EE[:,0]
+Dl_EE = data_EE[:,1]
+down_EE = data_EE[:,2]
+up_EE = data_EE[:,3]
 
-    z = solution(-6.5, 0.3, 67.3)
[…]

### 2024-11-29 SNe/result2.py

@@ -10,7 +10,6 @@ import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
 from solution import solution
 from solution import const_c
-const_c /= 1000
 from cross_section import cross_section
 
 H0 = 70.0

### 2024-12-02 article/article.tex
function has stiff point depend on the value of logkC1

@@
    \cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};\cite{Borghi_2022};
-   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (\cite{Scolnic_2022}), the CMB data from
-   Planck 2018 and the BAO data from SDSS and DESI 2024.
+   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (\cite{Scolnic_2022}),
+   the BAO data from SDSS and DESI 2024.
 
@@
    as \begin{equation}
-      \chi_{\text{S}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
+      \chi_{\text{SNe}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
    \end{equation}
@@
    \begin{equation}
-      \chi_{\text{SNe}}^2=A=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
+      \tilde{\chi}_{\text{SNe}}^2=A=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
    \end{equation}
@@
 
-\subsection{Cosmic Microwave Background}
-
-   We adopt the $\Omega_bh^2$ from BBN,
-   give the constraint to $r_d$
-
 \section{Constraint results}

### 2024-12-02 test.m

@@ -1,0 +1,45 @@
+% solution.m
+function test(log_kC1, O20, H0)
+    % Unit conversion
+    transfer = 3.24078e-20; % Conversion factor from km/s/Mpc to 1/Gyr
+    kC1 = 10^log_kC1 * transfer;
+    O10 = 1 - O20;
+    t0 = 1 / H0;
+    
+    % Solution interval
+    tspan = [t0, 0.0];
+    
+    % Initial value given at t0
+    zt0 = [0.0, -H0];
+    
+    % Solve the ODE
+    [t, z] = ode15s(@(t, z) function_(t, z, kC1, O10, H0), tspan, zt0);
+    
+    % Plot the results
+    figure;
+    plot(t, z(:, 1), 'DisplayName', 'z(t)');
+    hold on;
+    plot(t, z(:, 2), 'DisplayName', 'z''(t)');
+    xlabel('Time');
+    ylabel('Solution');
+    legend;
+    hold off;
+end
+
+function dz = function_(~, z, kC1, O10, H0)
+    % z(1) = z(t), z(2) = z'(t)
+    dz = zeros(2, 1);
+    dz(1) = z(2);
+    
+    % Reduce the use of parentheses, separate into numerator and denominator
+    numerator = ...
+        H0^4 * kC1 * O10^2 * (z(1)^4 + 1) + ...
+        3 * H0^4 * O10^2 * z(1)^2 * (2 * kC1 - 3 * z(2)) + ...
+        H0^4 * O10^2 * z(1)^3 * (4 * kC1 - 3 * z(2)) - ...
+        3 * H0^4 * O10^2 * z(2) + ...
+        5 * H0^2 * O10 * z(2)^3 - ...
+        kC1 * z(2)^4 + ...
+        H0^2 * O10 * z(1) * (4 * H0^2 * kC1 * O10 - 9 * H0^2 * O10 * z(2) + 5 * z(2)^3);
+    denominator = 2 * H0^2 * O10 * (1 + z(1))^2 * z(2);
+    dz(2) = numerator / denominator;
+end

### 2024-12-08 article/article.tex
qso constraints

@@
 \usepackage{txfonts}
+\graphicspath{{./pictures/}}
 
@@
       \left(\frac{H}{H_0}\right)^2=\Omega_{1,0}+\frac{\Omega_{1,0}\Omega_{2,0}a^{-3}e^{-2\kappa C_1(t-t_0)}}
-      {\Omega_{1,0}+\kappa C_1\Omega_{2,0}Z(t)},
+      {\Omega_{1,0}+\kappa C_1\Omega_{2,0}Z(t)},\label{eq:8}
    \end{equation}
@@
    host distances(\cite{Riess_2022}), which gives the $\mu_\text{data}$ and constrains $H_0$
-   in advance. To eliminate the influence of $M_b$, we give the likelihood function
+   in advance. To eliminate the influence of $M_b$, we give the $\chi^2$
    as \begin{equation}
@@
    \begin{equation}
-      \tilde{\chi}_{\text{SNe}}^2=A=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
+      \tilde{\chi}_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
    \end{equation}
-   Apparently these two functions give the same constraints in $\Omega_{2,0}$
-   and $\kappa C_1$.
+   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
+   covariance matrix of the SNe Ia data.
+
+   $B=\Delta^{\text{T}}C^{-1}$ and $C=\text{sum}(C^{-1})$.
+
+\subsection{Quasar}
+
+   The quasar gives a higher redshift
 
@@
    which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
+   The redshift is up to 2.33 both in the SDSS and the DESI 2024 dataset.
+
+   The $\chi^2$ function for the BAO data is defined as
+   \begin{equation}
+      \chi_{\text{BAO}}^2=\sum_i\frac{(D_{\text{th}}/r_{\text{d}}-D_{\text{data}}/r_{\text{d}})^2}{\sigma_i^2},
+   \end{equation}
+   where $D$ refers to $D_{\text{M}}$, $D_{\text{H}}$, or $D_{\text{V}}$, which ara given as
+   \begin{eqnarray}
+      D_{\text{M}}(z)&=&c\int_0^z\frac{\text{d}z'}{H(z')},\\
+      D_{\text{H}}(z)&=&\frac{c}{H(z)},\\
+      D_{\text{V}}(z)&=&\left[zD_{\text{M}}^2(z)D_{\text{H}}(z)\right]^{1/3},\\
+   \end{eqnarray}
+   and $r_{\text{d}}$ is the sound horizon at the drag epoch, which is given as
+   \begin{equation}
+      r_{\text{d}}=\int_{z_{\text{drag}}}^{\infty}\frac{c_s\text{d}z'}{H(z')}.
+   \end{equation}
+
+   However, the Eq.(\ref{eq:8}) just have a stiff point when $z\to\infty$, so the IDM
+   model can not give a constraint to the $r_{\text{d}}$ and we just try to use the cross
+   parameter $r_{\text{d}}h$ to give the constraints.
 

### 2024-12-08 QSO/qso_test.py

@@ -11,10 +11,10 @@ import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
 from solution import solution
 from solution import const_c
-from cross_section import cross_section
 
-file_path = "./QSO/data/table3.dat"
+file_path = "./data/table3.dat"
 data = np.loadtxt(file_path, skiprows=1, usecols=(3,11,12))
+data = data[data[:,0] <= 2]
 z = data[:,0]
 DM = data[:,1]
 e_DM = data[:,2]
@@ -61,7 +61,7 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.3, -5, 70])
+    initial = np.array([0.37, -2, 76])
     # soln = scipy.optimize.minimize(nll, initial)
     # pos = soln.x + 1e-4 * np.random.randn(50, 3)
     pos = initial + 1e-4 * np.random.randn(50, 3)
@@ -69,10 +69,10 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress=True)
+        sampler.run_mcmc(pos, 2500, progress=True)
 
     labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
+    flat_samples = sampler.get_chain(discard=400, flat=True)
     figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14})
     plt.tight_layout()

### 2024-12-08 QSO/result1.py

@@ -65,17 +65,17 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.3, -5, 70])
+    initial = np.array([0.35, -2, 70])
     soln = scipy.optimize.minimize(nll, initial)
     pos = soln.x + 1e-4 * np.random.randn(50, 3)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress=True)
+        sampler.run_mcmc(pos, 2500, progress=True)
 
     labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
+    flat_samples = sampler.get_chain(discard=400, flat=True)
     figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()

### 2024-12-08 QSO/result2.py

@@ -68,17 +68,17 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.3, -3, 70, -11, 0.6, 0.2])
+    initial = np.array([0.35, -2, 70, -11, 0.6, 0.2])
     soln = scipy.optimize.minimize(nll, initial)
     pos = soln.x + 1e-4 * np.random.randn(50, 6)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress=True)
+        sampler.run_mcmc(pos, 2500, progress=True)
 
     labels = [r'$\Omega_{2,0}$',r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$','$H_0$[km/s/Mpc]',r'$\beta$',r'$\gamma$',r'$\delta$']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
+    flat_samples = sampler.get_chain(discard=400, flat=True)
     figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
     plt.tight_layout()

### 2024-12-08 wIDM/caculus.py

@@ -53,6 +53,24 @@ def chi_square_SNe(O20, n, H0):
     chi2 = np.dot(delta_mu, np.dot(cov_matrix_inv, delta_mu))
     return chi2
 
+### QSO
+file_path = "./QSO/data/table3.dat"
+data = np.loadtxt(file_path, skiprows=1, usecols=(3,11,12))
+z_qso = data[:,0]
+DM = data[:,1]
+e_DM = data[:,2]
+
+def chi_square_QSO(O20, n, H0):
+    dl = []
+    for z in z_qso:
+        int_value = scipy.integrate.quad(H_ad, 0, z, args=(O20, n, H0))[0]
+        dl.append(const_c*(1 + z)*int_value)
+    dl = np.array(dl)
+    muth = 5 * np.log10(dl) + 25
+    delta_DM = muth - DM
+    chi2 = np.sum(delta_DM**2/e_DM**2)
+    return chi2
+
 ### BAO
 file_path_BAO = "./BAO/BAO.csv"
 pandata_BAO = np.loadtxt(file_path_BAO, delimiter=',', skiprows=1, usecols=(3, 4, 5, 6, 7, 8, 9))

### 2024-12-18 article/aas_template/sample631.tex
add cmb reduced paras

%% Beginning of file 'sample631.tex'
%%
%% Modified 2022 May  
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[linenumbers]{aastex631}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{March 1, 2021}
%\revised{April 1, 2021}
%\accepted{\today}

%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the argument.
%\submitjournal{PSJ}

%% For manuscript that include authors in collaborations, AASTeX v6.31
%% builds on the \collaboration command to allow greater freedom to 
%% keep the traditional author+affiliation information but only show
%% subsets. The \collaboration command now must appear AFTER the group
%% of authors in the collaboration and it takes TWO arguments. The last
%% is still the collaboration identifier. The text given in this
%% argument is what will be shown in the manuscript. The first argument
%% is the number of author above the \collaboration command to show with
%% the collaboration text. If there are authors that are not part of any
%% collaboration the \nocollaboration command is used. This command takes
%% one argument which is also the number of authors above to show. A
%% dashed line is shown to indicate no collaboration. This example manuscript
%% shows how these commands work to display specific set of authors 
%% on the front page.
%%
%% For manuscript without any need to use \collaboration the 
%% \AuthorCollaborationLimit command from v6.2 can still be used to 
%% show a subset of authors.
%
%\AuthorCollaborationLimit=2
%
%% will only show Schwarz & Muench on the front page of the manuscript
%% (assuming the \collaboration and \nocollaboration commands are
%% commented out).
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%\shorttitle{AASTeX v6.3.1 Sample article}
%\shortauthors{Schwarz et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
%% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{Template \aastex Article with Examples: 
v6.3.1\footnote{Released on March, 1st, 2021}}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.31 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affiliations. The change was necessary to implement 
%% auto-indexing of affiliations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% argument which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
%% present or in the LaTeX pathway, the OrcID icon will appear next to
%% the authors name.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.31 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.31 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

%\correspondingauthor{August Muench}
%\email{greg.schwarz@aas.org, gus.muench@aas.org}

\author[0000-0002-0786-7307]{Greg J. Schwarz}
\affiliation{American Astronomical Society \\
1667 K Street NW, Suite 800 \\
Washington, DC 20006, USA}

\author{August Muench}
\affiliation{American Astronomical Society \\
1667 K Street NW, Suite 800 \\
Washington, DC 20006, USA}

\collaboration{20}{(AAS Journals Data Editors)}

\author{F.X Timmes}
\affiliation{Arizona State University}
\affiliation{AAS Journals Associate Editor-in-Chief}

\author{Amy Hendrickson}
\altaffiliation{AASTeX v6+ programmer}
\affiliation{TeXnology Inc.}

\author{Julie Steffen}
\affiliation{AAS Director of Publishing}
\affiliation{American Astronomical Society \\
1667 K Street NW, Suite 800 \\
Washington, DC 20006, USA}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

This example manuscript is intended to serve as a tutorial and template for
authors to use when writing their own AAS Journal articles. The manuscript
includes a history of \aastex\ and includes figure and table examples to illustrate these features. Information on features not explicitly mentioned in the article can be viewed in the manuscript comments or more extensive online
documentation. Authors are welcome replace the text, tables, figures, and
bibliography with their own and submit the resulting manuscript to the AAS
Journals peer review system.  The first lesson in the tutorial is to remind
authors that the AAS Journals, the Astrophysical Journal (ApJ), the
Astrophysical Journal Letters (ApJL), the Astronomical Journal (AJ), and
the Planetary Science Journal (PSJ) all have a 250 word limit for the 
abstract\footnote{Abstracts for Research Notes of the American Astronomical 
Society (RNAAS) are limited to 150 words}.  If you exceed this length the
Editorial office will ask you to shorten it. This abstract has 161 words.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
%% https://astrothesaurus.org
%% You will be asked to selected these concepts during the submission process
%% but this old "keyword" functionality is maintained in case authors want
%% to include these concepts in their preprints.
\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}

\latex\ \footnote{\url{http://www.latex-project.org/}} is a document markup
language that is particularly well suited for the publication of
mathematical and scientific articles \citep{lamport94}. \latex\ was written
in 1985 by Leslie Lamport who based it on the \TeX\ typesetting language
which itself was created by Donald E. Knuth in 1978.  In 1988 a suite of
\latex\ macros were developed to investigate electronic submission and
publication of AAS Journal articles \citep{1989BAAS...21..780H}.  Shortly
afterwards, Chris Biemesdefer merged these macros and more into a \latex\
2.08 style file called \aastex.  These early \aastex\ versions introduced
many common commands and practices that authors take for granted today.
Substantial revisions
were made by Lee Brotzman and Pierre Landau when the package was updated to
v4.0.  AASTeX v5.0, written in 1995 by Arthur Ogawa, upgraded to \latex\ 2e
which uses the document class in lieu of a style file.  Other improvements
to version 5 included hypertext support, landscape deluxetables and
improved figure support to facilitate electronic submission.  
\aastex\ v5.2 was released in 2005 and introduced additional graphics
support plus new mark up to identifier astronomical objects, datasets and
facilities.

In 1996 Maxim Markevitch modified the AAS preprint style file, aaspp4.sty,
to closely emulate the very tight, two column style of a typeset
Astrophysical Journal article.  The result was emulateapj.sty.  A year
later Alexey Vikhlinin took over development and maintenance.  In 2001 he
converted emulateapj into a class file in \latex\ 2e and in 2003 Vikhlinin
completely rewrote emulateapj based on the APS Journal's RevTEX class.

During this time emulateapj gained growing acceptance in the astronomical
community as it filled an author need to obtain an approximate number of
manuscript pages prior to submission for cost and length estimates. The
tighter typeset also had the added advantage of saving paper when printing
out hard copies.

Even though author publication charges are no longer based on print pages
\footnote{see Section \ref{sec:pubcharge} in the Appendix for more details
about how current article costs are calculated.} the emulateapj class file
has proven to be extremely popular with AAS Journal authors.  An 
analysis of submitted \latex\ manuscripts in 2015 revealed that $\sim$65\%
either called emulateapj or have a commented emulateapj classfile call
indicating it was used at some stage of the manuscript construction.
Clearly authors want to have access to a tightly typeset version of the
article when corresponding with co-authors and for preprint submissions.

When planning the next \aastex\ release the popularity of emulateapj played
an important roll in the decision to drop the old base code and adopt and
modify emulateapj for \aastex\ v6.+ instead.  The change brings \aastex\
inline with what the majority of authors are already using while still
delivering new and improved features.  \aastex\ v6.0 through v6.31 were
written by Amy Hendrickson. The release dates were January 2016 (v6.0),
October 2016 (v6.1), January 2018 (v6.2), June 2019 (v6.3), and March 2020
(v6.31) respectively.

The rest of this article provides information and examples on how to create
your own AAS Journal manuscript with v6.31. The next section describes
the different manuscript styles available and how they differ from past
releases.  Section \ref{sec:floats} describes table and figure placement. 
Specific examples of a table, Section \ref{subsec:tables}, and a figure,
Section \ref{subsec:figures}, are also provided.  The last section,
\ref{sec:cite}, shows how recognize software and external data as first
class references in the manuscript bibliography.  An appendix is included
for additional information readers might find useful.
More documentation is embedded in the comments of this \latex\ file and in the online documentation at
\url{http://journals.aas.org/authors/aastex.html}.

\section{Manuscript styles} \label{sec:style}

The default style in \aastex\ v6.31 is a tight single column style, e.g. 10
point font, single spaced.  The single column style is very useful for
article with wide equations. It is also the easiest to style to work with
since figures and tables, see Section \ref{sec:floats}, will span the
entire page, reducing the need for address float sizing.

To invoke a two column style similar to the what is produced in
the published PDF copy use \\

\noindent {\tt\string\documentclass[twocolumn]\{aastex631\}}. \\

\noindent Note that in the two column style figures and tables will only
span one column unless specifically ordered across both with the ``*'' flag,
e.g. \\

\noindent{\tt\string\begin\{figure*\}} ... {\tt\string\end\{figure*\}}, \\
\noindent{\tt\string\begin\{table*\}} ... {\tt\string\end\{table*\}}, and \\
\noindent{\tt\string\begin\{deluxetable*\}} ... {\tt\string\end\{deluxetable*\}}. \\

\noindent This option is ignored in the onecolumn style.

Some other style options are outlined in the commented sections of this 
article.  Any combination of style options can be used.

Authors are required to provide line numbering in the manuscript. Line numbering makes it easier for the review to references specific places in the manuscript.
This functionality has been built into AASTeX since v6.0.  The {\tt\string linenumbers} style option invokes the lineno style file to number each article line in the left margin.

There is also a new {\tt\string modern} option that uses a Daniel
Foreman-Mackey and David Hogg design to produce stylish, single column
output that has wider left and right margins. It is designed to have fewer
words per line to improve reader retention. It also looks better on devices
with smaller displays such as smart phones.

The {\tt\string anonymous} option will prevent the author and affiliations
from being shown in the compiled pdf copy. This option allows the author 
to keep this critical information in the latex file but prevent the reviewer
from seeing it during peer review if dual anonymous review (DAR) is requested. 
Likewise, acknowledgments can also be hidden if placed in the new 
{\tt\string\begin\{acknowledgments\}} ... {\tt\string\end\{acknowledgments\}}
environment. The use of this option is highly recommended for PSJ submissions. 
Advice for anonymizing your manuscript for DAR is provided at 
\url{https://journals.aas.org/manuscript-preparation/#dar}.

\section{Floats} \label{sec:floats}

Floats are non-text items that generally can not be split over a page.
They also have captions and can be numbered for reference.  Primarily these
are figures and tables but authors can define their own. \latex\ tries to
place a float where indicated in the manuscript but will move it later if
there is not enough room at that location, hence the term ``float''.

Authors are encouraged to embed their tables and figures within the text as
they are mentioned.  Please do not place the figures and text at the end of
the article as was the old practice.  Editors and the vast majority of
referees find it much easier to read a manuscript with embedded figures and
tables.

Depending on the number of floats and the particular amount of text and
equations present in a manuscript the ultimate location of any specific
float can be hard to predict prior to compilation. It is recommended that
authors textbf{not} spend significant time trying to get float placement
perfect for peer review.  The AAS Journal's publisher has sophisticated
typesetting software that will produce the optimal layout during
production.

Note that authors of Research Notes are only allowed one float, either one
table or one figure.

For authors that do want to take the time to optimize the locations of
their floats there are some techniques that can be used.  The simplest
solution is to placing a float earlier in the text to get the position
right but this option will break down if the manuscript is altered.
A better method is to force \latex\ to place a
float in a general area with the use of the optional {\tt\string [placement
specifier]} parameter for figures and tables. This parameter goes after
{\tt\string \begin\{figure\}}, {\tt\string \begin\{table\}}, and
{\tt\string \begin\{deluxetable\}}.  The main arguments the specifier takes
are ``h'', ``t'', ``b'', and ``!''.  These tell \latex\ to place the float
\underline{h}ere (or as close as possible to this location as possible), at
the \underline{t}op of the page, and at the \underline{b}ottom of the page.
The last argument, ``!'', tells \latex\ to override its internal method of
calculating the float position.  A sequence of rules can be created by
using multiple arguments.  For example, {\tt\string \begin\{figure\}[htb!]}
tells \latex\ to try the current location first, then the top of the page
and finally the bottom of the page without regard to what it thinks the
proper position should be.  Many of the tables and figures in this article
use a placement specifier to set their positions.

Note that the \latex\ {\tt\string tabular} environment is not a float.  Only
when a {\tt\string tabular} is surrounded by {\tt\string\begin\{table\}} ...
{\tt\string\end\{table\}} is it a true float and the rules and suggestions
above apply.

In AASTeX v6.31 all deluxetables are float tables and thus if they are
longer than a page will spill off the bottom. Long deluxetables should
begin with the {\tt\string\startlongtable} command. This initiates a
longtable environment.  Authors might have to use {\tt\string\clearpage} to
isolate a long table or optimally place it within the surrounding text.

\subsection{Tables} \label{subsec:tables}

Tables can be constructed with \latex's standard table environment or the
\aastex's deluxetable environment. The deluxetable construct handles long
tables better but has a larger overhead due to the greater amount of
defined mark up used set up and manipulate the table structure.  The choice
of which to use is up to the author.

Tables longer than 250 data lines and complex tables should only have a
short example table with the full data set available in the machine
readable format.  The machine readable table will be available in the HTML
version of the article with just a short example in the PDF. Authors are
required to indicate in the table comments that the data in machine 
readable format in the full article.
Authors are encouraged to create their own machine
readable tables using the online tool at
\url{http://authortools.aas.org/MRT/upload.html} but the data editors will review and edit all submissions prior to publication.

Full details on how to create the different types of tables are given in the AASTeX guidelines at \url{http://journals.aas.org/authors/aastex.html}

\subsubsection{Splitting a table into multiple horizontal components}

Since the AAS Journals are now all electronic with no print version there is
no reason why tables can not be as wide as authors need them to be.
However, there are some artificial limitations based on the width of a
print page.  The old way around this limitation was to rotate into 
landscape mode and use the smallest available table font
sizes, e.g. {\tt\string\tablewidth}, to get the table to fit.
Unfortunately, this was not always enough but now there is a new way to break
a table into two or three components so that it flows down a page by
invoking a new table type, splittabular or splitdeluxetable. Within these
tables a new ``B'' column separator is introduced.  Much like the vertical
bar option, ``$\vert$'', that produces a vertical table lines 
the new ``B'' separator indicates where to \underline{B}reak
a table.  Up to two ``B''s may be included.

Table \ref{tab:deluxesplit} 
shows how to split a wide deluxetable into three parts with
the {\tt\string\splitdeluxetable} command.  The {\tt\string\colnumbers}
option is on to show how the automatic column numbering carries through the
second table component.

\begin{splitdeluxetable*}{lccccBcccccBcccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt} 
%\tablenum{1}
\tablecaption{Measurements of Emission Lines: two breaks \label{tab:deluxesplit}}
\tablehead{
\colhead{Model} & \colhead{Component}& \colhead{Shift} & \colhead{FWHM} &
\multicolumn{10}{c}{Flux} \\
\colhead{} & \colhead{} & \colhead{($\rm
km~s^{-1}$)}& \colhead{($\rm km~s^{-1}$)} & \multicolumn{10}{c}{($\rm
10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
\cline{5-14}
\colhead{} & \colhead{} &
\colhead{} & \colhead{} & \colhead{Ly$\alpha$} & \colhead{N\,{\footnotesize
V}} & \colhead{Si\,{\footnotesize IV}} & \colhead{C\,{\footnotesize IV}} &
\colhead{Mg\,{\footnotesize II}} & \colhead{H$\gamma$} & \colhead{H$\beta$}
& \colhead{H$\alpha$} & \colhead{He\,{\footnotesize I}} &
\colhead{Pa$\gamma$}
} 
\colnumbers
\startdata 
{       }& BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\ 
{Model 1}& IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
{       }& NELs& \nodata &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
\hline
{       }& BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
{Model 2}& IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
{       }& NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$&
     147$\pm       22$\\
\enddata
\tablecomments{This is an example of how to split a deluxetable. You can
split any table with this command into two or three parts.  The location of
the split is given by the author based on the placement of the ``B''
indicators in the column identifier preamble.  For more information please
look at the new \aastex\ instructions.}
\end{splitdeluxetable*}

\subsection{Figures\label{subsec:figures}}

%% The "ht!" tells LaTeX to put the figure "here" first, at the "top" next
%% and to override the normal way of calculating a float position
\begin{figure}[ht!]
\plotone{samplefig.png}
\caption{The cost for an author to publish an article has trended downward
over time. This figure shows the average cost of an article from 1990 to 2020 in 2021 adjusted dollars. 
\label{fig:general}}
\end{figure}

Authors can include a wide number of different graphics with their articles
but encapsulated postscript (EPS) or portable document format (PDF) are
encouraged. These range from general figures all authors are familiar with
to new enhanced graphics that can only be fully experienced in HTML.  The
later include figure sets, animations and interactive figures.  All
enhanced graphics require a static two dimensional representation in the
manuscript to serve as the example for the reader. All figures should
include detailed and descriptive captions.  These captions are absolutely
critical for readers for whom the enhanced figure is inaccessible either
due to a disability or offline access.

Figure \ref{fig:general} shows the changes in the author publication charges (APCs) from 1990 to 2020 in the AAS Journals. The primary command for creating figures is the {\tt\string\includegraphics} command. Full details can be found \break
\url{https://en.wikibooks.org/wiki/LaTeX/Importing\_Graphics\#Including\_graphics}.

\subsection{Enhanced graphics}

Enhanced graphics have an example figure to serve as an example for the
reader and the full graphical item available in the published HTML article.
This includes Figure sets, animations, and interactive figures. The 
Astronomy Image Explorer (\url{http://www.astroexplorer.org/}) provides 
access to all the figures published in the AAS Journals since they offered
an electronic version which was in the mid 1990s. You can filter image
searches by specific terms, year, journal, or type. The type filter is 
particularly useful for finding all published enhanced graphics. As of
May 2022 there are over 4500 videos, 1600 figure sets, and 125 interactive
figures. Authors should review the AASTeX guidebook at \url{http://journals.aas.org/authors/aastex/aasguide.html} to see how to represent these enhanced graphics in their own manuscripts.

\section{Software and third party data repository citations} \label{sec:cite}

The AAS Journals would like to encourage authors to change software and
third party data repository references from the current standard of a
footnote to a first class citation in the bibliography.  As a bibliographic
citation these important references will be more easily captured and credit
will be given to the appropriate people.

The first step to making this happen is to have the data or software in
a long term repository that has made these items available via a persistent
identifier like a Digital Object Identifier (DOI).  A list of repositories
that satisfy this criteria plus each one's pros and cons are given at \break
\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.

In the bibliography the format for data or code follows this format: \\

\noindent author year, title, version, publisher, prefix:identifier\\

\citet{2015ApJ...805...23C} provides a example of how the citation in the
article references the external code at
\doi{10.5281/zenodo.15991}.  Unfortunately, bibtex does
not have specific bibtex entries for these types of references so the
``@misc'' type should be used.  The Repository tutorial explains how to
code the ``@misc'' type correctly.  The most recent aasjournal.bst file,
available with \aastex\ v6, will output bibtex ``@misc'' type properly.

%% IMPORTANT! The old "\acknowledgment" command has be depreciated. It was
%% not robust enough to handle our new dual anonymous review requirements and
%% thus been replaced with the acknowledgment environment. If you try to 
%% compile with \acknowledgment you will get an error print to the screen
%% and in the compiled pdf.
%% 
%% Also note that the akcnowlodgment environment does not support long amounts of text. If you have a lot of people and institutions to acknowledge, do not use this command. Instead, create a new \section{Acknowledgments}.
\begin{acknowledgments}
We thank all the people that have made this AASTeX what it is today.  This
includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
for the new "modern" style design. Considerable help was provided via bug
reports and hacks from numerous people including Patricio Cubillos, Alex
Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
Gagne.
\end{acknowledgments}

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

\vspace{5mm}
\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
CTIO:1.5m,CXO}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manuscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  
          Cloudy \citep{2013RMxAA..49..137F}, 
          Source Extractor \citep{1996A&AS..117..393B}
          }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

\appendix

\section{Appendix information}

Appendices can be broken into separate sections just like in the main text.
The only difference is that each appendix section is indexed by a letter
(A, B, C, etc.) instead of a number.  Likewise numbered equations have
the section letter appended.  Here is an equation as an example.
\begin{equation}
I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
\end{equation}
Appendix tables and figures should not be numbered like equations. Instead
they should continue the sequence from the main article body.

\section{Gold Open Access}

As of January 1st, 2022, all of the AAS Journals articles became open access, meaning that all content, past, present and future, is available to anyone to read and download. A page containing frequently asked questions is available at \url{https://journals.aas.org/oa/}.

\section{Author publication charges} \label{sec:pubcharge}

In April 2011 the traditional way of calculating author charges based on 
the number of printed pages was changed.  The reason for the change
was due to a recognition of the growing number of article items that could not 
be represented in print. Now author charges are determined by a number of
digital ``quanta''.  A single quantum is 350 words, one figure, one table,
and one enhanced digital item.  For the latter this includes machine readable
tables, figure sets, animations, and interactive figures.  The current cost
for the different quanta types is available at 
\url{https://journals.aas.org/article-charges-and-copyright/#author_publication_charges}. 
Authors may use the online length calculator to get an estimate of 
the number of word and float quanta in their manuscript. The calculator 
is located at \url{https://authortools.aas.org/Quanta/newlatexwordcount.html}.

\section{Rotating tables} \label{sec:rotate}

The process of rotating tables into landscape mode is slightly different in
\aastex v6.31. Instead of the {\tt\string\rotate} command, a new environment
has been created to handle this task. To place a single page table in a
landscape mode start the table portion with
{\tt\string\begin\{rotatetable\}} and end with
{\tt\string\end\{rotatetable\}}.

Tables that exceed a print page take a slightly different environment since
both rotation and long table printing are required. In these cases start
with {\tt\string\begin\{longrotatetable\}} and end with
{\tt\string\end\{longrotatetable\}}. Table \ref{chartable} is an
example of a multi-page, rotated table. The {\tt\string\movetabledown}
command can be used to help center extremely wide, landscape tables. The
command {\tt\string\movetabledown=1in} will move any rotated table down 1
inch.

A handy "cheat sheet" that provides the necessary \latex\ to produce 17 
different types of tables is available at \url{http://journals.aas.org/authors/aastex/aasguide.html#table_cheat_sheet}.

\section{Using Chinese, Japanese, and Korean characters}

Authors have the option to include names in Chinese, Japanese, or Korean (CJK) 
characters in addition to the English name. The names will be displayed 
in parentheses after the English name. The way to do this in AASTeX is to 
use the CJK package available at \url{https://ctan.org/pkg/cjk?lang=en}.
Further details on how to implement this and solutions for common problems,
please go to \url{https://journals.aas.org/nonroman/}.

%% For this sample we use BibTeX plus aasjournals.bst to generate the
%% the bibliography. The sample631.bib file was populated from ADS. To
%% get the citations to show in the compiled file do the following:
%%
%% pdflatex sample631.tex
%% bibtext sample631
%% pdflatex sample631.tex
%% pdflatex sample631.tex

\bibliography{sample631}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample631.tex'.

### 2024-12-18 article/article.tex
add cmb reduced paras

@@
-\documentclass{aa}
-\usepackage{graphicx}
-\usepackage{txfonts}
+\documentclass[twocolumn]{aastex631}
+\newcommand{\vdag}{(v)^\dagger}
+\newcommand\aastex{AAS\TeX}
+\newcommand\latex{La\TeX}
 \graphicspath{{./pictures/}}
@@
 
-   \author{Yixuan Zhu}
-
-   \institute{Department of Astronomy, Beijing Normal University.
+   \author{Yixuan Zhu}\affiliation{Department of Astronomy, Beijing Normal University.
    Beijing 100875.
@@
 
-   \date{}
+   \begin{abstract}
 
-   \abstract{}
+   \end{abstract}
 
    \keywords{}
-
-   \maketitle
 
@@
 
-\subsection{Model 1: relation to the $\varLambda$CDM model}
+\subsection{Model 1: relation to the LambdaCDM model}
 
@@
    We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
-   host distances(\cite{Riess_2022}), which gives the $\mu_\text{data}$ and constrains $H_0$
+   host distances(\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and constrains $H_0$
    in advance. To eliminate the influence of $M_b$, we give the $\chi^2$
@@
    covariance matrix of the SNe Ia data.
-
    $B=\Delta^{\text{T}}C^{-1}$ and $C=\text{sum}(C^{-1})$.
@@
 
-   The quasar gives a higher redshift
+   The quasar gives a higher redshift than SNe Ia.
+   We use the QSO dataset from \cite{Lusso_2020}, which gives
+   2421 samples with the ultraviolet (UV) and X-ray luminosity.
+   The redshift is up to $\simeq7.5$.
+
+   The $L_X-L_{UV}$ relation of quasar is usually written as
+   \begin{equation}
+      L_X=\beta+\gamma\log L_{UV},
+   \end{equation}
+   which gives that
+   \begin{equation}
+      \log_{10}(F_X)=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
+                    +2(\gamma-1)\log_{10}(d_L),
+   \end{equation}
+   where $d_L$ is the luminosity distance same as which in the SNe Ia,Eq.15
+   so the $\chi^2$ function for the QSO data can be defined as
+   \begin{equation}
+      \chi_{\text{QSO}}^2=\sum_i^{2421}\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
+      -\ln(2\pi s_i^2),
+   \end{equation}
+   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
+   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
+   $\delta_i$ reprensent the instrinsic dispersion.
 
@@
       D_{\text{H}}(z)&=&\frac{c}{H(z)},\\
-      D_{\text{V}}(z)&=&\left[zD_{\text{M}}^2(z)D_{\text{H}}(z)\right]^{1/3},\\
+      D_{\text{V}}(z)&=&\left[zD_{\text{M}}^2(z)D_{\text{H}}(z)\right]^{1/3},
    \end{eqnarray}
@@
 
+\subsection{Reduced CMB parameters}
+
+   We used the reduced CMB parameters $\{l_A,R,z_{*}\}$ from Planck 2018
+   to constrains the model. The reduced CMB parameters are
+   \begin{equation}
+      l_A=\frac{\pi r(z_{*})}{r_s(z_{*})}
+   \end{equation}
+   which refer to acoustic scale, and the shift parameter is given as
+   \begin{equation}
+      R=H_0\sqrt{\Omega_{m0}}r(z_{*})\sim H_0\sqrt{\Omega_{2,0}}r(z_{*}),
+   \end{equation}
+   where $r(z_{*})$ and $r_s(z_{*})$ are defined as
+   \begin{eqnarray}
+      r(z_{*})=\int_0^{z_{*}}\frac{z'\mathrm{d}z'}{H(z')},\\
+      r_s(z_{*})=\int_{z_{*}}^{\infty}\frac{c_s\mathrm{d}z'}{H(z')}.
+   \end{eqnarray}
+   As the same as what we do in BAO data, we choose the cross parameter
+   $r_s(z_{*})h$ and give the $z_{*}\simeq1090$ to constrain the model.
+
 \section{Constraint results}
@@
 
-\bibliographystyle{aa}
 \bibliography{reference}
+\bibliographystyle{aasjournal}
 

### 2024-12-18 QSO/result2.py

@@ -44,7 +44,7 @@ def logFX_z(log_kC1, O20, H0, beta, gamma):
 
 def chi_square(log_kC1, O20, H0, beta, gamma, delta):
     delta_fx = logFX_z(log_kC1, O20, H0, beta, gamma) - logFX
-    sigma_2 = e_logFX**2 + delta**2
+    sigma_2 = e_logFX**2 + gamma**2*e_logFUV**2 + delta**2
     chi2 = np.sum(delta_fx**2/sigma_2)
     extra = np.sum(np.log(2*np.pi*sigma_2))
     return chi2 + extra
@@ -69,8 +69,9 @@ def lnprob(paras):
 def main():
     nll = lambda *args: -lnlike(*args)
     initial = np.array([0.35, -2, 70, -11, 0.6, 0.2])
-    soln = scipy.optimize.minimize(nll, initial)
-    pos = soln.x + 1e-4 * np.random.randn(50, 6)
+    # soln = scipy.optimize.minimize(nll, initial)
+    # pos = soln.x + 1e-4 * np.random.randn(50, 6)
+    pos = initial + 1e-4 * np.random.randn(50, 6)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:

### 2024-12-18 wIDM/OHD.py

@@ -39,7 +39,7 @@ def main():
         sampler.run_mcmc(pos, 5000, progress = True)
 
     labels = [r'$\Omega_{2,0}$', '$n$', '$H_0$[km/s/Mpc]']
-    flat_samples = sampler.get_chain(discard=100, flat=True)
+    flat_samples = sampler.get_chain(discard=200, flat=True)
     figure = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
                             title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
     plt.tight_layout()

### 2024-12-18 wIDM/caculus.py

@@ -54,8 +54,8 @@ def chi_square_SNe(O20, n, H0):
     return chi2
 
 ### QSO
-file_path = "./QSO/data/table3.dat"
-data = np.loadtxt(file_path, skiprows=1, usecols=(3,11,12))
+file_path_QSO = "./QSO/data/table3.dat"
+data = np.loadtxt(file_path_QSO, skiprows=1, usecols=(3,11,12))
 z_qso = data[:,0]
 DM = data[:,1]
 e_DM = data[:,2]

### 2024-12-22 article/article.tex
use getdist to draw the mcmc result

@@
 
-\subsection{Model 1: relation to the LambdaCDM model}
+\subsection{Model 1: relation to the ΛCDM model}
 
@@
    To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
-   observational $H(z)$ data (OHD)(\cite{Zhang_2014};\cite{PhysRevD.71.123001};
-   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Moresco_2016};
-   \cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};\cite{Borghi_2022};
-   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (\cite{Scolnic_2022}),
-   the BAO data from SDSS and DESI 2024.
+   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001};
+   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Zhang_2014};
+   \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
+   \cite{Borghi_2022};\cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia 
+   (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
+   the BAO data from SDSS and DESI 2024, and the reduced CMB parameters
+   from Planck 2018.
 
@@
    We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
-   host distances(\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and constrains $H_0$
-   in advance. To eliminate the influence of $M_b$, we give the $\chi^2$
-   as \begin{equation}
-      \chi_{\text{SNe}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
+   host distances(\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
+   give the $\chi^2$ as 
+   \begin{equation}
+      \chi_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
    \end{equation}
-   where $A=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})^2/\sigma_i^2,
-   B=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})/\sigma_i^2,C=\sum_i^{1701}1/\sigma_i^2$,
-   the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
+   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
+   covariance matrix of the SNe Ia data, the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
    luminosity distance $d_L$ can be given as a function of redshift $z$
    \begin{equation}
-      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.
+      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.\label{eq:15}
    \end{equation}
-   However, the Eq.(\ref{eq:9}) just need the $H_0$ to caculate the $M_x$
-   and we would still use the simple likelihood function as
+   To eliminate the advanced restriction to $H_0$ from $M_b$, we adopt
+   the likelihood function as
    \begin{equation}
-      \tilde{\chi}_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
+      \widetilde{\chi}_{\text{SNe}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
    \end{equation}
-   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
-   covariance matrix of the SNe Ia data.
-   $B=\Delta^{\text{T}}C^{-1}$ and $C=\text{sum}(C^{-1})$.
+   where $A=\Delta^{\text{T}}C^{-1}\Delta,B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
+   Apparently these two functions give the same constraints in $\Omega_{2,0}$ and
+   $\log_{10}(\kappa C_1)$
 
@@
    which gives that
-   \begin{equation}
-      \log_{10}(F_X)=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
-                    +2(\gamma-1)\log_{10}(d_L),
-   \end{equation}
-   where $d_L$ is the luminosity distance same as which in the SNe Ia,Eq.15
-   so the $\chi^2$ function for the QSO data can be defined as
+   \begin{eqnarray}
+      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
+                    \\ &+2(\gamma-1)\log_{10}(d_L),
+   \end{eqnarray}
+   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
+   So the $\chi^2$ function for the QSO data can be defined as
    \begin{equation}
@@
       \centering
-      \begin{tabular}{lllll}
+      \begin{tabular}{llll}
          \hline\hline
@@
 
+   We use the Markov chain Monte Carlo (MCMC) method based 
+   on the opening package \texttt{emcee} to give a global constraints
+   to the free parameters $\Omega_{2,0}$ and $\log_{10}(\kappa C_1)$ in 
+   Model 1 and $n$ in Model 2.
+   Besides, we also add the parameter $H_0$ or $h$ to give the constraints
+   to the dark matter particle mass $M_x$.
+
+\subsection{Model 1: mimicking the ΛCDM model}
+
+   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
+   $\log_{10}(\kappa C_1)\to-\infty$, therefore the constraints
+   could only give the upper limit of what, and give the lower limit
+   of $M_x$, respectively.
+
+   \begin{figure}[htbp]
+      \centering
+   \end{figure}
+
 \section{Conclusions}

### 2024-12-22 CMB/test.py

@@ -80,7 +80,7 @@ def plot(log_kC1, O20, H0):
 
 import multiprocessing as mp
 import emcee
-import corner
+from getdist import plots, MCSamples
 import scipy
 
 def r(z, paras):
@@ -132,26 +132,27 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 3000, progress = True)
 
-    labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]', '$r_{*}h$']
+    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]', r'r_{\star}h']
     flat_samples = sampler.get_chain(discard=500, flat=True)
-    figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='k')
-    plt.tight_layout()
-    plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='k')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['k'], title_limit=1)
     plt.show()
 
-    H0 = np.median(flat_samples[:,2])
-    H0_list = np.array([H0]*len(flat_samples))
-    Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
-    combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
-    labels_ = [r'$\Omega_{2,0}$', r'$\log_{10}(M_x$/GeV)']
[…]

### 2024-12-22 OHD/result.py

@@ -2,7 +2,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import emcee
-import corner
+from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
@@ -77,16 +77,15 @@ def main():
         sampler.run_mcmc(pos, 2000, progress = True)
 
     # MCMC result plot
-    labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['b'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='b')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/ohd_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['b'], title_limit=1)
+    g.export('./article/pictures/ohd_1.pdf')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -94,11 +93,10 @@ def main():
     # Plot Mx vs O20 corner plot
     Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
[…]

### 2024-12-22 QSO/result1.py

@@ -2,7 +2,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import emcee
-import corner
+from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
@@ -74,27 +74,25 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 2500, progress=True)
 
-    labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
     flat_samples = sampler.get_chain(discard=400, flat=True)
-    figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['k'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/qso_dm_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['k'], title_limit=1)
+    g.export('./article/pictures/qso_dm_1.pdf')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
[…]

### 2024-12-22 QSO/result2.py

@@ -2,7 +2,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import emcee
-import corner
+from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
@@ -78,27 +78,25 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 2500, progress=True)
 
-    labels = [r'$\Omega_{2,0}$',r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$','$H_0$[km/s/Mpc]',r'$\beta$',r'$\gamma$',r'$\delta$']
+    labels = [r'\Omega_{2,0}',r'\log_{10}(\kappa C_1/Gyr{}^{-1})','H_0[km/s/Mpc]',r'\beta',r'\gamma',r'\delta']
     flat_samples = sampler.get_chain(discard=400, flat=True)
-    figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['k'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/qso_fx_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['k'], title_limit=1)
+    g.export('./article/pictures/qso_fx_1.pdf')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
[…]

### 2024-12-22 SNe/result2.py

@@ -1,7 +1,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import emcee
-import corner
+from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
@@ -75,16 +75,15 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 2000, progress=True)
 
-    labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['g'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/sne_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['g'], title_limit=1)
+    g.export('./article/pictures/sne_1.pdf')
     plt.show()
 
     H0 = np.median(flat_samples[:,2])
@@ -92,11 +91,10 @@ def main():
     # Plot Mx vs O20 corner plot
[…]

### 2024-12-22 wIDM/BAO.py

@@ -3,7 +3,7 @@ import scipy
 import matplotlib.pyplot as plt
 import multiprocessing as mp
 import emcee
-import corner
+from getdist import plots, MCSamples
 
 import sys
 import os
@@ -38,23 +38,21 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 5000, progress = True)
 
-    labels = [r'$\Omega_{2,0}$', '$n$', '$H_0$[km/s/Mpc]', '$r_dh$[Mpc]']
-    flat_samples = sampler.get_chain(discard=100, flat=True)
-    figure = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
-    plt.tight_layout()
+    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
+    flat_samples = sampler.get_chain(discard=200, flat=True)
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['r'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='r')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/bao_widm_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['r'], title_limit=1)
+    g.export('./article/pictures/bao_widm_1.pdf')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
-    labels_ = [r'$\Omega_{2,0}$', '$w_{IDM}$']
[…]

### 2024-12-22 wIDM/SNe.py

@@ -3,7 +3,7 @@ import scipy
 import matplotlib.pyplot as plt
 import multiprocessing as mp
 import emcee
-import corner
+from getdist import plots, MCSamples
 
 import sys
 import os
@@ -38,25 +38,23 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 2000, progress = True)
 
-    labels = [r'$\Omega_{2,0}$', '$n$', '$H_0$[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
     flat_samples = sampler.get_chain(discard=100, flat=True)
-    figure = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['g'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/sne_widm_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['g'], title_limit=1)
+    g.export('./article/pictures/sne_widm_1.pdf')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
-    labels_ = [r'$\Omega_{2,0}$', '$w_{IDM}$']
[…]

### 2024-12-22 wIDM/methods2.py

@@ -3,7 +3,7 @@ import scipy
 import matplotlib.pyplot as plt
 import multiprocessing as mp
 import emcee
-import corner
+from getdist import plots, MCSamples
 
 import sys
 import os
@@ -39,23 +39,21 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 2000, progress = True)
 
-    labels = [r'$\Omega_{2,0}$', '$n$', '$H_0$[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
     flat_samples = sampler.get_chain(discard=100, flat=True)
-    figure = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
-    plt.tight_layout()
+    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['c'], title_limit=1)
     plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='c')
-    plt.tight_layout()
-    plt.savefig('./article/pictures/ohd_sne_widm_1.eps')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
+    g.triangle_plot(samples_2, filled=True, contour_colors=['c'], title_limit=1)
+    g.export('./article/pictures/ohd_sne_widm_1.pdf')
     plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
-    labels_ = [r'$\Omega_{2,0}$', '$w_{IDM}$']
[…]

### 2024-12-26 article/article.tex
pictures from eps to pdf qso use the newly params

@@
 \documentclass[twocolumn]{aastex631}
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
+\usepackage{subfigure}
 \graphicspath{{./pictures/}}
@@
    (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
-   the BAO data from SDSS and DESI 2024, and the reduced CMB parameters
-   from Planck 2018.
+   the BAO data from SDSS and DESI 2024.
 
@@
    \begin{equation}
-      \widetilde{\chi}_{\text{SNe}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
+      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
    \end{equation}
-   where $A=\Delta^{\text{T}}C^{-1}\Delta,B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
+   where $B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
    Apparently these two functions give the same constraints in $\Omega_{2,0}$ and
-   $\log_{10}(\kappa C_1)$
+   $\log_{10}(\kappa C_1)$.
 
@@
 
-\subsection{Reduced CMB parameters}
-
-   We used the reduced CMB parameters $\{l_A,R,z_{*}\}$ from Planck 2018
-   to constrains the model. The reduced CMB parameters are
-   \begin{equation}
-      l_A=\frac{\pi r(z_{*})}{r_s(z_{*})}
-   \end{equation}
-   which refer to acoustic scale, and the shift parameter is given as
-   \begin{equation}
-      R=H_0\sqrt{\Omega_{m0}}r(z_{*})\sim H_0\sqrt{\Omega_{2,0}}r(z_{*}),
-   \end{equation}
-   where $r(z_{*})$ and $r_s(z_{*})$ are defined as
-   \begin{eqnarray}
-      r(z_{*})=\int_0^{z_{*}}\frac{z'\mathrm{d}z'}{H(z')},\\
-      r_s(z_{*})=\int_{z_{*}}^{\infty}\frac{c_s\mathrm{d}z'}{H(z')}.
-   \end{eqnarray}
-   As the same as what we do in BAO data, we choose the cross parameter
-   $r_s(z_{*})h$ and give the $z_{*}\simeq1090$ to constrain the model.
-
 \section{Constraint results}
@@
 
+   The prior range set for free parameters are given at Table \ref{tab:4}
+
+   \begin{table}[htbp]
+      \caption{Parameters and priors used in analysis}
+      \centering
+      \begin{tabular}{lll}
+         \hline\hline
+         parameter & initial & prior \\
+         \hline
+         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
+         $n$ & --- & $\mathcal{U}[-10,10]$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
+         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
+         \hline
+         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
+         \hline
+         $\beta$ & $-11$ & $\mathcal{U}[-15,-5]$ \\
+         $\gamma$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
+         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
+         \hline
+      \end{tabular}
+      \label{tab:4}
+   \end{table}
+
 \subsection{Model 1: mimicking the ΛCDM model}
@@
    could only give the upper limit of what, and give the lower limit
-   of $M_x$, respectively.
+   of $M_x$ according to Eq.(\ref{eq:9}), respectively.
 
@@
       \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_2.pdf}
+      }
+      \caption{The constraint result from the observational
+      $H(z)$ data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_2.pdf}
+      }
+      \caption{The constraint result from the supernovae
+      Ia data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{bao_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{bao_2.pdf}
+      }
+      \caption{The constraint result from the BAO data}
    \end{figure}

### 2024-12-26 BAO/result.py

@@ -104,25 +104,31 @@ def main():
         sampler.run_mcmc(pos, 2000, progress = True)
 
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
+    names = ['O20', 'log_kC1', 'H0', 'rdh']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['r'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['r'], title_limit=1)
+    g.export('./article/pictures/bao.pdf')
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
+    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['r'])
     g.export('./article/pictures/bao_1.pdf')
-    plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
     Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
     combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
     labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['r'], title_limit=1)
+    names_ = ['O20', 'Mx']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
+    g = plots.get_single_plotter(ratio=1)    
+    g.settings.axes_fontsize = 18
[…]

### 2024-12-26 CMB/test.py

@@ -133,8 +133,9 @@ def main():
         sampler.run_mcmc(pos, 3000, progress = True)
 
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]', r'r_{\star}h']
+    names = ['O20', 'log_kC1', 'H0', 'rsh']
     flat_samples = sampler.get_chain(discard=500, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['k'], title_limit=1)
     plt.show()

### 2024-12-26 OHD/result.py

@@ -78,15 +78,18 @@ def main():
 
     # MCMC result plot
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
+    names = ['O20', 'log_kC1', 'H0']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['b'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['b'], title_limit=1)
+    g.export('./article/pictures/ohd.pdf')
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
+    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['b'])
     g.export('./article/pictures/ohd_1.pdf')
-    plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
@@ -94,10 +97,13 @@ def main():
     Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
     combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
     labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['b'], title_limit=1)
+    names_ = ['O20', 'Mx']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
+    g = plots.get_single_plotter(ratio=1)    
+    g.settings.axes_fontsize = 18
[…]

### 2024-12-26 QSO/result1.py

@@ -72,10 +72,10 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2500, progress=True)
+        sampler.run_mcmc(pos, 3000, progress=True)
 
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
-    flat_samples = sampler.get_chain(discard=400, flat=True)
+    flat_samples = sampler.get_chain(discard=500, flat=True)
     samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['k'], title_limit=1)

### 2024-12-26 QSO/result2.py

@@ -13,6 +13,9 @@ from solution import solution
 from solution import const_c
 from cross_section import cross_section
 
+import astropy.units as u
+transform = u.Mpc.to(u.m)
+
 H0 = 70.0
 O20 = 0.3
 log_kC1 = -5.0
@@ -25,7 +28,7 @@ e_logFUV = data[:,2]
 logFX = data[:,3]
 e_logFX = data[:,4]
 
-def logFX_z(log_kC1, O20, H0, beta, gamma):
+def logFX_z(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1):
     t0 = 1 / H0
     t_values = solution(log_kC1, O20, H0).t
     z_values = solution(log_kC1, O20, H0).y[0, :]
@@ -39,24 +42,27 @@ def logFX_z(log_kC1, O20, H0, beta, gamma):
         dl_value = const_c * (1 + z_value) * (t0 - t_values[idx] + int_value)
         dl_values.append(dl_value)
 
-    dl = np.array(dl_values)
+    dl = np.array(dl_values) * transform
+    beta = beta0 + beta1 * (1 + z)
+    gamma = gamma0 + gamma1 * (1 + z)
     return beta+(gamma-1)*np.log10(4*np.pi)+gamma*logFUV+2*(gamma-1)*np.log10(dl)
 
-def chi_square(log_kC1, O20, H0, beta, gamma, delta):
-    delta_fx = logFX_z(log_kC1, O20, H0, beta, gamma) - logFX
+def chi_square(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta):
+    delta_fx = logFX_z(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1) - logFX
+    gamma = gamma0 + gamma1 * (1 + z)
     sigma_2 = e_logFX**2 + gamma**2*e_logFUV**2 + delta**2
     chi2 = np.sum(delta_fx**2/sigma_2)
     extra = np.sum(np.log(2*np.pi*sigma_2))
     return chi2 + extra
 
 def lnlike(paras):
-    O20, log_kC1, H0, beta, gamma, delta = paras
-    chi2 = chi_square(log_kC1, O20, H0, beta, gamma, delta)
+    O20, log_kC1, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    chi2 = chi_square(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta)
     return -0.5 * chi2
 
 def lnprior(paras):
[…]

### 2024-12-26 SNe/result2.py

@@ -76,15 +76,18 @@ def main():
         sampler.run_mcmc(pos, 2000, progress=True)
 
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
+    names = ['O20', 'log_kC1', 'H0']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['g'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['g'], title_limit=1)
+    g.export('./article/pictures/sne.pdf')
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
+    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['g'])
     g.export('./article/pictures/sne_1.pdf')
-    plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
@@ -92,10 +95,13 @@ def main():
     Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
     combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
     labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['g'], title_limit=1)
+    names_ = ['O20', 'Mx']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
+    g = plots.get_single_plotter(ratio=1)    
+    g.settings.axes_fontsize = 18
[…]

### 2024-12-26 multimethods/methods2.py

@@ -56,15 +56,18 @@ def main():
         sampler.run_mcmc(pos, 2000, progress = True)
 
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
+    names = ['O20', 'log_kC1', 'H0']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['c'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['c'], title_limit=1)
+    g.export('./article/pictures/ohd_sne.pdf')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['c'])
     g.export('./article/pictures/ohd_sne_1.pdf')
-    plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
@@ -72,10 +75,13 @@ def main():
     Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
     combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
     labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['b'], title_limit=1)
+    names_ = ['O20', 'Mx']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
+    g = plots.get_single_plotter(ratio=1)    
[…]

### 2024-12-26 multimethods/methods3.py

@@ -61,25 +61,31 @@ def main():
         sampler.run_mcmc(pos, 2000, progress = True)
 
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
+    names = ['O20', 'log_kC1', 'H0', 'rdh']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['m'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['m'], title_limit=1)
+    g.export('./article/pictures/ohd_sne_bao.pdf')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['m'])
     g.export('./article/pictures/ohd_sne_bao_1.pdf')
-    plt.show()
 
     H0 = np.median(flat_samples[:,2])
     H0_list = np.array([H0]*len(flat_samples))
     Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
     combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
     labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['m'], title_limit=1)
+    names_ = ['O20', 'Mx']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
+    g = plots.get_single_plotter(ratio=1)    
[…]

### 2024-12-27 article/article.tex
solution singularity?

@@
    \begin{equation}
-      L_X=\beta+\gamma\log L_{UV},
+      \log_{10}(L_X)=\beta+\gamma\log_{10}(L_{UV}),
    \end{equation}
@@
    where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
-   So the $\chi^2$ function for the QSO data can be defined as
+   Here we use the parameters defined in \cite{li2024redshiftevolutionxrayuv}, which
+   gives\begin{equation}
+      \beta=\beta_0+\beta_1(1+z),\gamma=\gamma_0+\gamma_1(1+z),
+   \end{equation}
+   so the $\chi^2$ function for the QSO data can be defined as
    \begin{equation}
-      \chi_{\text{QSO}}^2=\sum_i^{2421}\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
-      -\ln(2\pi s_i^2),
+      \chi_{\text{QSO}}^2=\sum_i^{2421}\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
+      -\ln(2\pi s_i^2)\right],
    \end{equation}
@@
 
-   However, the Eq.(\ref{eq:8}) just have a stiff point when $z\to\infty$, so the IDM
+   However, the Eq.(\ref{eq:8}) just have a singularity when $z\to\infty$, so the IDM
    model can not give a constraint to the $r_{\text{d}}$ and we just try to use the cross
@@
          $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
-         $n$ & --- & $\mathcal{U}[-10,10]$ \\
+         $n$ & 0 & $\mathcal{U}[-10,10]$ \\
          $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
@@
          \hline
+         $\beta_0$ & 6 & $\mathcal{U}[-15,15]$ \\
+         $\beta_1$ & 1 & $\mathcal{U}[-10,10]$ \\
+         $\gamma_0$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
+         $\gamma_1$ & 0 & $\mathcal{U}[-1.0,1.0]$ \\         
+         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
+         \hline
          $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
-         \hline
-         $\beta$ & $-11$ & $\mathcal{U}[-15,-5]$ \\
-         $\gamma$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
-         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
          \hline
@@
       \subfigure{
+         \includegraphics[width=0.22\textwidth]{qso_fx_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{qso_fx_2.pdf}
+      }
+      \caption{The constraint result from the quasar data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
          \includegraphics[width=0.22\textwidth]{bao_1.pdf}

### 2024-12-27 BAO/result.py

@@ -106,7 +106,7 @@ def main():
     labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
     names = ['O20', 'log_kC1', 'H0', 'rdh']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None),'H0':(60, 80)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['r'], title_limit=1)
     g.export('./article/pictures/bao.pdf')

### 2024-12-27 wIDM/caculus.py

@@ -54,8 +54,8 @@ def chi_square_SNe(O20, n, H0):
     return chi2
 
 ### QSO
-file_path_QSO = "./QSO/data/table3.dat"
-data = np.loadtxt(file_path_QSO, skiprows=1, usecols=(3,11,12))
+file_path_QSO = "./QSO/data/dm.dat"
+data = np.loadtxt(file_path_QSO)
 z_qso = data[:,0]
 DM = data[:,1]
 e_DM = data[:,2]

### 2025-02-11 article/article.tex
theoretical solution?

@@
 
-   However, the Eq.(\ref{eq:8}) just have a singularity when $z\to\infty$, so the IDM
-   model can not give a constraint to the $r_{\text{d}}$ and we just try to use the cross
+   However, the Eq.(\ref{eq:8}) just have a singularity when $t\to 0$ as $z\to\infty$,
+   so the IDM model cannot give a constraint to the $r_{\text{d}}$ and we just try to use the cross
    parameter $r_{\text{d}}h$ to give the constraints.
@@
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{qso_fx_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{qso_fx_2.pdf}
-      }
-      \caption{The constraint result from the quasar data}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
          \includegraphics[width=0.22\textwidth]{bao_1.pdf}

### 2025-02-11 SNe/result1.py

@@ -1,5 +1,5 @@
 import numpy as np
-import matplotlib.pyplot as plt
+from getdist import plots, MCSamples
 import emcee
 import corner
 import scipy
@@ -78,27 +78,33 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 2000, progress=True)
 
-    labels = [r'$\Omega_{2,0}$', r'$\log_{10}(\kappa C_1/$Gyr${}^{-1})$', '$H_0$[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
+    names = ['O20', 'log_kC1', 'H0']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    figure1 = corner.corner(flat_samples, levels=(0.6826,0.9544), labels=labels, plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
-    plt.show()
-    figure2 = corner.corner(flat_samples[:,0:2], levels=(0.6826,0.9544), labels=labels[0:2], plot_datapoints=False, plot_density=False, fill_contours=True,
-                            title_fmt='.4f', show_titles=True, title_kwargs={"fontsize": 14}, smooth=1, smooth1d=4, bins=50, hist_bin_factor=4, color='g')
-    plt.tight_layout()
-    plt.show()
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None), 'H0':(60, 80)})
+    g = plots.get_subplot_plotter()
+    g.triangle_plot(samples, filled=True, contour_colors=['g'], title_limit=1)
+    # g.export('./article/pictures/sne.pdf')
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
[…]

### 2025-02-11 multimethods/methods1.py

@@ -1,0 +1,82 @@
+import numpy as np
+import emcee
+from getdist import plots, MCSamples
+import multiprocessing as mp
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+from cross_section import cross_section
+
+H0 = 70.0
+O20 = 0.3
+log_kC1 = -5.0
+
+import QSO.result2
+def chi_square_QSO(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta):
+    return QSO.result2.chi_square(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta)
+
+import SNe.result1
+def chi_square_SNe(log_kC1, O20, H0):
+    return SNe.result1.chi_square(log_kC1, O20, H0)
+
+def lnlike(paras):
+    O20, log_kC1, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    chi2 = chi_square_SNe(log_kC1, O20, H0) + chi_square_QSO(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    O20, log_kC1, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    if -10<log_kC1<0 and 0<O20<1 and 60<H0<80 and 0<gamma0<1 and -1<gamma1<1 and -15<beta0<15 and -10<beta1<10 and 0<delta<1:
+        return 0.0
+    return -np.inf
+
+def lnprob(paras):
+    lp = lnprior(paras)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(paras)
+
+def main():
+    nll = lambda *args: -lnlike(*args)
+    initial = np.array([0.3, -5, 70, 0.6, 0, 6, 1, 0.2])
+    # soln = scipy.optimize.minimize(nll, initial)
+    # pos = soln.x + 1e-4 * np.random.randn(50, 6)
+    pos = initial + 1e-4 * np.random.randn(50, 8)
+    nwalkers, ndim = pos.shape
+
+    with mp.Pool() as pool:
+        sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
+        sampler.run_mcmc(pos, 2000, progress = True)
+
[…]

### 2025-02-11 wIDM/BAO.py

@@ -39,20 +39,26 @@ def main():
         sampler.run_mcmc(pos, 5000, progress = True)
 
     labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
+    names = ['O20', 'n', 'H0', 'rdh']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['r'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['r'], title_limit=1)
+    g.export('./article/pictures/bao_widm.pdf')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2])
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    g.plot_2d(samples_2, 'O20', 'n', filled=True, colors=['r'])
     g.export('./article/pictures/bao_widm_1.pdf')
-    plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
     labels_ = [r'\Omega_{2,0}', 'w_{IDM}']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['r'], title_limit=1)
+    names_ = ['O20', 'wIDM']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_)
+    g = plots.get_single_plotter(ratio=1)    
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    g.plot_2d(samples_, 'O20', 'wIDM', filled=True, colors=['r'])
     g.export('./article/pictures/bao_widm_2.pdf')
-    plt.show()

### 2025-02-11 wIDM/OHD.py

@@ -29,7 +29,7 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.28, 0, 70]) # expected best values
+    initial = np.array([0.2, 0, 70]) # expected best values
     soln = scipy.optimize.minimize(nll, initial)
     pos = soln.x + 1e-4 * np.random.randn(50, 3)
     nwalkers, ndim = pos.shape
@@ -39,23 +39,29 @@ def main():
         sampler.run_mcmc(pos, 5000, progress = True)
 
     labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
+    names = ['O20', 'n', 'H0']   
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['b'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['b'], title_limit=1)
+    g.export('./article/pictures/ohd_widm.pdf')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2])
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    g.plot_2d(samples_2, 'O20', 'n', filled=True, colors=['b'])
     g.export('./article/pictures/ohd_widm_1.pdf')
-    plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
     labels_ = [r'\Omega_{2,0}', 'w_{IDM}']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['b'], title_limit=1)
+    names_ = ['O20', 'wIDM']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_)
+    g = plots.get_single_plotter(ratio=1)    
[…]

### 2025-02-11 wIDM/QSO.py

@@ -11,13 +11,13 @@ sys.path.append(os.path.join(os.path.dirname(__file__), '.'))
 from caculus import chi_square_QSO
 
 def lnlike(paras):
-    O20, n, H0 = paras
-    chi2 = chi_square_QSO(O20, n, H0)
+    O20, n, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    chi2 = chi_square_QSO(O20, n, H0, gamma0, gamma1, beta0, beta1, delta)
     return -0.5 * chi2
 
 def lnprior(paras):
-    O20, n, H0 = paras
-    if 0 < O20 < 1 and -10 < n < 10 and 50 < H0 < 100:
+    O20, n, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    if 0 < O20 < 1 and -10 < n < 10 and 50 < H0 < 100 and 0<gamma0<1 and -1<gamma1<1 and -15<beta0<15 and -10<beta1<10 and 0<delta<1:
         return 0.0
     return -np.inf
 
@@ -29,17 +29,17 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.3, 0, 70])
+    initial = np.array([0.3, 0, 70, 0.6, 0, 6, 1, 0.2])
     # soln = scipy.optimize.minimize(nll, initial)
     # pos = soln.x + 1e-4 * np.random.randn(50, 3)
-    pos = initial + 1e-4 * np.random.randn(50, 3)
+    pos = initial + 1e-4 * np.random.randn(50, 8)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 5000, progress = True)
 
-    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
+    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', r'\gamma_0',r'\gamma_1',r'\beta_0',r'\beta_1',r'\delta']
     flat_samples = sampler.get_chain(discard=400, flat=True)
     samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
     g = plots.get_subplot_plotter()
@@ -54,7 +54,7 @@ def main():
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
[…]

### 2025-02-11 wIDM/caculus.py

@@ -54,22 +54,35 @@ def chi_square_SNe(O20, n, H0):
     return chi2
 
 ### QSO
-file_path_QSO = "./QSO/data/dm.dat"
-data = np.loadtxt(file_path_QSO)
+file_path_QSO = "./QSO/data/table3.dat"
+data = np.loadtxt(file_path_QSO, skiprows=1, usecols=(3,4,5,6,7))
 z_qso = data[:,0]
-DM = data[:,1]
-e_DM = data[:,2]
+logFUV = data[:,1]
+e_logFUV = data[:,2]
+logFX = data[:,3]
+e_logFX = data[:,4]
 
-def chi_square_QSO(O20, n, H0):
+import astropy.units as u
+transform = u.Mpc.to(u.m)
+
+def logFX_z(O20, n, H0, gamma0, gamma1, beta0, beta1):
     dl = []
     for z in z_qso:
         int_value = scipy.integrate.quad(H_ad, 0, z, args=(O20, n, H0))[0]
         dl.append(const_c*(1 + z)*int_value)
-    dl = np.array(dl)
-    muth = 5 * np.log10(dl) + 25
-    delta_DM = muth - DM
-    chi2 = np.sum(delta_DM**2/e_DM**2)
-    return chi2
+    dl = np.array(dl) * transform
+
+    beta = beta0 + beta1 * (1 + z_qso)
+    gamma = gamma0 + gamma1 * (1 + z_qso)
+    return beta+(gamma-1)*np.log10(4*np.pi)+gamma*logFUV+2*(gamma-1)*np.log10(dl)
+
+def chi_square_QSO(O20, n, H0, gamma0, gamma1, beta0, beta1, delta):
+    delta_fx = logFX_z(O20, n, H0, gamma0, gamma1, beta0, beta1) - logFX
+    gamma = gamma0 + gamma1 * (1 + z_qso)
+    sigma_2 = e_logFX**2 + gamma**2*e_logFUV**2 + delta**2
+    chi2 = np.sum(delta_fx**2/sigma_2)
+    extra = np.sum(np.log(2*np.pi*sigma_2))
+    return chi2 + extra
 
 ### BAO
 file_path_BAO = "./BAO/BAO.csv"

### 2025-02-11 wIDM/methods2.py

@@ -30,7 +30,7 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.28, 0, 70]) # expected best values
+    initial = np.array([0.3, 0, 70]) # expected best values
     soln = scipy.optimize.minimize(nll, initial)
     pos = soln.x + 1e-4 * np.random.randn(50, 3)
     nwalkers, ndim = pos.shape
@@ -40,20 +40,26 @@ def main():
         sampler.run_mcmc(pos, 2000, progress = True)
 
     labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
+    names = ['O20', 'n', 'H0']
     flat_samples = sampler.get_chain(discard=100, flat=True)
-    samples = MCSamples(samples=flat_samples, names=labels, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['c'], title_limit=1)
-    plt.show()
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=labels[0:2], labels=labels[0:2])
-    g.triangle_plot(samples_2, filled=True, contour_colors=['c'], title_limit=1)
+    g.export('./article/pictures/ohd_sne_widm.pdf')
+    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2])
+    g = plots.get_single_plotter(ratio=1)
+    g.settings.axes_fontsize = 18
+    g.settings.axes_labelsize = 24
+    g.plot_2d(samples_2, 'O20', 'n', filled=True, colors=['c'])
     g.export('./article/pictures/ohd_sne_widm_1.pdf')
-    plt.show()
 
     wIDM = -1 - flat_samples[:,1]/3
     combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
     labels_ = [r'\Omega_{2,0}', 'w_{IDM}']
-    samples_ = MCSamples(samples=combined_samples, names=labels_, labels=labels_)
-    g.triangle_plot(samples_, filled=True, contour_colors=['c'], title_limit=1)
+    names_ = ['O20', 'wIDM']
+    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_)
+    g = plots.get_single_plotter(ratio=1)    
[…]

### 2025-02-22 article/article.tex
appendix and figure added

@@
    Refering to Appendix B in \cite{refId0}, only one of these two is of interest
-   because it provides a "$\propto a^{-3}$" dependence of the scale factor,
+   because it provides a ``$\propto a^{-3}$'' dependence of the scale factor,
    which is \begin{equation}
@@
    \begin{equation}
-      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},
+      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},\label{eq:12}
    \end{equation}
@@
    \begin{equation}
-      r_{\text{d}}=\int_{z_{\text{drag}}}^{\infty}\frac{c_s\text{d}z'}{H(z')}.
+      r_{\text{d}}=\int_{z_{\text{drag}}}^{\infty}\frac{c_s(z')\text{d}z'}{H(z')},
+   \end{equation}
+   where $c_s$ is the sound speed prior to recombination, which is given as
+   \begin{equation}
+      c_s(z)=\frac{c}{\sqrt{3\left(1+\frac{3\rho_{\mathrm{b}}(z)}{4\rho_{\gamma}(z)}\right)}}\simeq
+      \frac{c}{\sqrt{3\left(1+\frac{3\rho_{\mathrm{b}0}}{4\rho_{\gamma0}}\frac{1}{1+z}\right)}}.
    \end{equation}
 
-   However, the Eq.(\ref{eq:8}) just have a singularity when $t\to 0$ as $z\to\infty$,
-   so the IDM model cannot give a constraint to the $r_{\text{d}}$ and we just try to use the cross
+   However, the solution of Eq.(\ref{eq:8}) gives an upper limit of redshift $z_{\max}$
+   (see Appendix), so the IDM model cannot give a constraint to the $r_{\text{d}}$ and we just try to use the cross
    parameter $r_{\text{d}}h$ to give the constraints.
@@
 
+   We use the 99\% and 1\% quantiles to determine the upper and lower
+   limits of the parameters, and the results are shown in Table \ref{tab:5}.
+
    \begin{figure}[htbp]
@@
       \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_qso_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_qso_2.pdf}
+      }
+      \caption{The constraint result from the SNe Ia + QSO data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
          \includegraphics[width=0.22\textwidth]{bao_1.pdf}
@@
 
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
+      }
+      \caption{The constraint result from the OHD + SNe Ia data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
+      }
+      \caption{The constraint result from the OHD + SNe Ia + BAO data}
+   \end{figure}
+
+   \begin{table*}[htbp]
+      \caption{The constraint results of Model 1}
+      \centering
+      \begin{tabular}{lcccccc}
+         \hline\hline
+         Model 1 & OHD & SNe Ia & SNe Ia + QSO & BAO &
+          OHD + SNe Ia & OHD + SNe Ia + BAO \\
+         \hline
+         $\Omega_{2,0}$ & $0.321_{-0.067}^{+0.055}$ & $0.360_{-0.020}^{+0.020}$
+          & $0.359_{-0.020}^{+0.020}$ & $0.301_{-0.013}^{+0.013}$
+          & $0.330_{-0.016}^{+0.016}$ & $0.3131_{-0.0099}^{+0.0099}$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & < & < & < & < & < & < \\
+         $\log_{10}(M_x/$GeV) & > & > & > & > & > & > \\
+         \hline
+      \end{tabular}
+      \label{tab:5}
+   \end{table*}
+
+\subsection{Model 2: mimicking the wCDM model}
+
+   The constraint results of Model 2 are shown in Table \ref{tab:6}.
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_widm_2.pdf}
+      }
+      \caption{The constraint result from the observational
+      $H(z)$ data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_widm_2.pdf}
+      }
+      \caption{The constraint result from the supernovae
+      Ia data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_qso_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{sne_qso_widm_2.pdf}
+      }
+      \caption{The constraint result from the SNe Ia + QSO data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{bao_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{bao_widm_2.pdf}
+      }
+      \caption{The constraint result from the BAO data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_2.pdf}
+      }
+      \caption{The constraint result from the OHD + SNe Ia data}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_widm_2.pdf}
+      }
+      \caption{The constraint result from the OHD + SNe Ia + BAO data}
+   \end{figure}
+
+   \begin{table*}[htbp]
+      \caption{The constraint results of Model 2}
+      \centering
+      \begin{tabular}{lcccccc}
+         \hline\hline
+         Model 2 & OHD & SNe Ia & SNe Ia + QSO & BAO &
+          OHD + SNe Ia & OHD + SNe Ia + BAO \\
+         \hline
+         $\Omega_{2,0}$ & $0.295_{-0.077}^{+0.077}$ & $0.216_{-0.078}^{+0.096}$
+          & $0.208_{-0.087}^{+0.12}$ & $0.296_{-0.014}^{+0.014}$
+          & $0.202_{-0.049}^{+0.060}$ & $0.291_{-0.013}^{+0.013}$ \\
+         $n$ & $1.4_{-2.8}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
+          & $-0.85_{-0.49}^{+0.42}$ & $-0.40_{-0.29}^{+0.29}$
+          & $-0.83_{-0.27}^{+0.24}$ & $-0.41_{-0.13}^{+0.13}$ \\
+         $w_{\text{IDM}}$ & $-1.5_{-0.9}^{+0.5}$ & $-0.73_{-0.15}^{+0.10}$
+          & $-0.72_{-0.16}^{+0.14}$ & $-0.87_{-0.10}^{+0.10}$
+          & $-0.72_{-0.09}^{+0.09}$ & $-0.86_{-0.04}^{+0.04}$ \\
+         \hline
+      \end{tabular}
+      \label{tab:6}
+   \end{table*}
+
 \section{Conclusions}
+
+\appendix
+
+\section{The theoretical solution of model 1}
+
+   Apply the Eq.(\ref{eq:12}) to Eq.(\ref{eq:8}), we can get a simple nonlinear
+   second-order differential equation for the redshift $z(t)$, which can
+   be written as \begin{equation}
+      2H_0^2\Omega_{1,0}(1+z)^2z'z''+\kappa C_1z'{}^4-5H_0^2\Omega_{1,0}(1+z)z'{}^3
+      +3H_0^4\Omega_{1,0}^2(1+z)^3z'-H_0^4\Omega_{1,0}^2\kappa C_1[(z+1)^4-1]
+      =H_0^4\Omega_{1,0}^2\kappa C_1,
+   \end{equation}
+   where the prime denotes the derivative with respect to $t$.
+   The equation can be simplified as
+   \begin{equation}
+      2H_0^2\Omega_{1,0}y^2y'y''+\kappa C_1y'{}^4-5H_0^2\Omega_{1,0}yy'{}^3
+      +3H_0^4\Omega_{1,0}^2y^3y'-H_0^4\Omega_{1,0}^2\kappa C_1y^4=0,
+   \end{equation}
+   where $y=z+1$, now it is a homogeneous function and we can give the
+   general solution as $y=\exp{f}$ with $f$ a function of $t$, the equation
+   now is \begin{equation}
+      2H_0^2\Omega_{1,0}f'f''+\kappa C_1f'{}^4-3H_0^2\Omega_{1,0}f'{}^3
+      +3H_0^4\Omega_{1,0}^2f'-H_0^4\Omega_{1,0}^2\kappa C_1=0.
+   \end{equation}
+   We use $g=f'$, which also gives $g(t)=y'/y=-H(t)$, then the equation can be written as
+   \begin{equation}
+      2H_0^2\Omega_{1,0}gg'+\kappa C_1g^4-3H_0^2\Omega_{1,0}g^3
+      +3H_0^4\Omega_{1,0}^2g-H_0^4\Omega_{1,0}^2\kappa C_1=0.
+   \end{equation}
+   It can be theoretically solved and the solution is like
+   \begin{equation}
+      g(t)=\mathcal{G}\left(-\frac{t}{2H_0^2\Omega_{1,0}}+\mathrm{Const}\right),
+   \end{equation}
+   where $\mathcal{G}$ is the inverse function of
+   \begin{equation}
+      \mathcal{F}(x)=\frac{3H_0\sqrt{\Omega_{1,0}}\mathrm{arctanh}\frac{x}{H_0\sqrt{\Omega_{1,0}}}
+      -\kappa C_1\log(x^2-H_0^2\Omega_{1,0})+\kappa C_1\ln(\kappa C_1x^2-3H_0^2\Omega_{1,0}x
+      +H_0^2\Omega_{1,0}\kappa C_1)}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}\kappa C_1^2},
+   \end{equation}
+   in this term, $\mathrm{arctanh}(x)\doteq \frac{1}{2}\log[(x+1)/(x-1)]$ when $x<-1$,
+   and the Const is determined by the initial condition $g(t_0)=-H_0$.
+
+   The function has a limit when $x\to-\infty$,
+   \begin{equation}
+      \lim_{x\to-\infty}\mathcal{F}(x)\equiv \mathcal{F}(-\infty)=
+      \frac{\kappa C_1\ln\kappa C_1}{H_0^2\Omega_{1,0}(-4\kappa C_1^2+9H_0^2\Omega_{1,0})},
+   \end{equation}
+   which means that the IDM model can only give a solution to the lower limit $t_{\min}$,
+   and the redshift $z_{\max}$ can be calculated as
+   \begin{equation}
+      z_{\max}=\exp\left[\int_{-\infty}^{-H_0}\left(\mathcal{F}(-\infty)
+      -\mathcal{F}(x)\right)\mathrm{d}x+\frac{t_0-t_{\min}}{2H_0\Omega_{1,0}}\right]-1,
+   \end{equation}
+   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
+   \begin{figure}[htbp]
+      \centering
+      \includegraphics[width=0.7\textwidth]{zmax.pdf}
+      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
+   \end{figure}
 

### 2025-02-22 solution.py

@@ -49,3 +49,44 @@ def solution(log_kC1, O20, H0, n=100000):
     z = scipy.integrate.solve_ivp(function, t_span=tspan, y0=zt0, t_eval=tn, method='RK45', args=(kC1, O10, H0))
     # z.y[0,:] = z(t), z.y[1,:] = z'(t)
     return z
+
+# theoretical solution
+
+def original_function(x, log_kC1, O10, H0):
+    kC1 = 10**log_kC1 * transfer
+    # p1 = 3 * H0 * np.sqrt(O10) * np.arctanh(x/H0/np.sqrt(O10))
+    p1 = 3 * H0 * np.sqrt(O10) * 1/2*np.log(np.abs(1+x/H0/np.sqrt(O10))/(1-x/H0/np.sqrt(O10)))
+    p2 = kC1 * np.log(x**2 - H0**2*O10)
+    p3 = kC1 * np.log(kC1*x**2 - 3*H0**2*O10*x + H0**2*O10*kC1)
+    p4 = 9*H0**4*O10**2 - 4*H0**2*O10*kC1**2
+    return (p1 - p2 + p3) / p4
+
+def constant_f(log_kC1, O10, H0):
+    p = 1/(2*H0**3*O10)
+    return original_function(-H0, log_kC1, O10, H0) + p
+
+def inverse_function(t, log_kC1, O10, H0):
+    varible = -t/(2*H0**2*O10) + constant_f(log_kC1, O10, H0)
+
+    def equation(x):
+        return original_function(x, log_kC1, O10, H0) - varible
+    
+    y = scipy.optimize.root_scalar(equation, x0=-H0, method='newton').root
+    return y
+
+def t_lim(log_kC1, O10, H0):
+    kC1 = 10**log_kC1 * transfer
+    limit = kC1*np.log(kC1)/(H0**2*O10*(-4*kC1**2 + 9*H0**2*O10))
+    return (constant_f(log_kC1, O10, H0) - limit)*(2*H0**2*O10)
+
+def z_lim(log_kC1, O10, H0):
+    kC1 = 10**log_kC1 * transfer
+    limit = kC1*np.log(kC1)/(H0**2*O10*(-4*kC1**2 + 9*H0**2*O10))
+    
+    def func(x):
+        return original_function(x, log_kC1, O10, H0) - limit
+
+    integral = scipy.integrate.quad(func, -np.inf, -H0)
[…]

### 2025-02-22 wIDM/BAO.py

@@ -41,7 +41,7 @@ def main():
     labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
     names = ['O20', 'n', 'H0', 'rdh']
     flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'H0':(60, 80)})
     g = plots.get_subplot_plotter()
     g.triangle_plot(samples, filled=True, contour_colors=['r'], title_limit=1)
     g.export('./article/pictures/bao_widm.pdf')

### 2025-02-22 wIDM/methods1.py

@@ -1,0 +1,68 @@
+import numpy as np
+import scipy
+import matplotlib.pyplot as plt
+import multiprocessing as mp
+import emcee
+from getdist import plots, MCSamples
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '.'))
+from caculus import chi_square_QSO
+from caculus import chi_square_SNe
+
+
+def lnlike(paras):
+    O20, n, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    chi2 = chi_square_QSO(O20, n, H0, gamma0, gamma1, beta0, beta1, delta) + chi_square_SNe(O20, n, H0)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    O20, n, H0, gamma0, gamma1, beta0, beta1, delta = paras
+    if 0 < O20 < 1 and -10 < n < 10 and 50 < H0 < 100 and 0<gamma0<1 and -1<gamma1<1 and -15<beta0<15 and -10<beta1<10 and 0<delta<1:
+        return 0.0
+    return -np.inf
+
+
+def lnprob(paras):
+    lp = lnprior(paras)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(paras)
+
+def main():
+    nll = lambda *args: -lnlike(*args)
+    initial = np.array([0.3, 0, 70, 0.6, 0, 6, 1, 0.2])
+    # soln = scipy.optimize.minimize(nll, initial)
+    # pos = soln.x + 1e-4 * np.random.randn(50, 3)
+    pos = initial + 1e-4 * np.random.randn(50, 8)
+    nwalkers, ndim = pos.shape
+
+    with mp.Pool() as pool:
+        sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
+        sampler.run_mcmc(pos, 2000, progress = True)
+
+    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', r'\gamma_0',r'\gamma_1',r'\beta_0',r'\beta_1',r'\delta']
+    names = ['O20', 'n', 'H0', 'gamma0', 'gamma1', 'beta0', 'beta1', 'delta']
+    flat_samples = sampler.get_chain(discard=100, flat=True)
+    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
+    g = plots.get_subplot_plotter()
[…]

### 2025-03-05 article/article.tex
transfer the t0 and zmax

@@
 
-   However, the solution of Eq.(\ref{eq:8}) gives an upper limit of redshift $z_{\max}$
-   (see Appendix), so the IDM model cannot give a constraint to the $r_{\text{d}}$ and we just try to use the cross
+   However, the solution of Eq.(\ref{eq:8}) only gives an upper limit of redshift $z_{\max}$
+   (see Appendix), and we just try to use the cross
    parameter $r_{\text{d}}h$ to give the constraints.
@@
 
+   We would find that the SNe Ia and QSO combined result is most
+   similar to SNe Ia result, what may refer that the QSO cannot
+   give an effective constraint.
+
    \begin{figure}[htbp]
@@
           & $0.359_{-0.020}^{+0.020}$ & $0.301_{-0.013}^{+0.013}$
-          & $0.330_{-0.016}^{+0.016}$ & $0.3131_{-0.0099}^{+0.0099}$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & < & < & < & < & < & < \\
-         $\log_{10}(M_x/$GeV) & > & > & > & > & > & > \\
+          & $0.330_{-0.016}^{+0.016}$ & $0.313_{-0.010}^{+0.010}$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-1.81$ & $<-2.30$ & $<-2.35$
+          & $<-2.66$ & $<-2.78$ & $<-3.21$ \\
+         $\log_{10}(M_x/$GeV) & $>-10.09$ & $>-9.62$ & $>-9.60$
+          & $>-9.25$ & $>-9.15$ & $>-8.70$ \\
          \hline
@@
 
+   The results from three dataset are different
+
    \begin{table*}[htbp]
@@
    \begin{equation}
-      g(t)=\mathcal{G}\left(-\frac{t}{2H_0^2\Omega_{1,0}}+\mathrm{Const}\right),
+      g(t)=\mathcal{G}\left(-\frac{t}{2H_0^2\Omega_{1,0}}+Const\right),
    \end{equation}
@@
       \mathcal{F}(x)=\frac{3H_0\sqrt{\Omega_{1,0}}\mathrm{arctanh}\frac{x}{H_0\sqrt{\Omega_{1,0}}}
-      -\kappa C_1\log(x^2-H_0^2\Omega_{1,0})+\kappa C_1\ln(\kappa C_1x^2-3H_0^2\Omega_{1,0}x
-      +H_0^2\Omega_{1,0}\kappa C_1)}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}\kappa C_1^2},
+      -\kappa C_1\log(x^2-H_0^2\Omega_{1,0})+\kappa C_1\log(\kappa C_1x^2-3H_0^2\Omega_{1,0}x
+      +H_0^2\Omega_{1,0}\kappa C_1)}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
    \end{equation}
-   in this term, $\mathrm{arctanh}(x)\doteq \frac{1}{2}\log[(x+1)/(x-1)]$ when $x<-1$,
-   and the Const is determined by the initial condition $g(t_0)=-H_0$.
+   In this term, $\displaystyle\mathrm{arctanh}(x)\doteq \frac{1}{2}\log\left(\frac{x+1}{x-1}\right)$
+   when $x<-1$, and the $Const$ is determined by the boundary condition $g(0)\to -\infty$, which is
 
-   The function has a limit when $x\to-\infty$,
    \begin{equation}
-      \lim_{x\to-\infty}\mathcal{F}(x)\equiv \mathcal{F}(-\infty)=
-      \frac{\kappa C_1\ln\kappa C_1}{H_0^2\Omega_{1,0}(-4\kappa C_1^2+9H_0^2\Omega_{1,0})},
+      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
+      \frac{\kappa C_1\ln\kappa C_1}{H_0^2\Omega_{1,0}[-4(\kappa C_1)^2+9H_0^2\Omega_{1,0}]}.
    \end{equation}
-   which means that the IDM model can only give a solution to the lower limit $t_{\min}$,
+   The initial time of today $t_0$ can be easily given as
+   \begin{equation}
+      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
+   \end{equation}
    and the redshift $z_{\max}$ can be calculated as
    \begin{equation}
-      z_{\max}=\exp\left[\int_{-\infty}^{-H_0}\left(\mathcal{F}(-\infty)
-      -\mathcal{F}(x)\right)\mathrm{d}x+\frac{t_0-t_{\min}}{2H_0\Omega_{1,0}}\right]-1,
+      z_{\max}=\exp\left[\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
+      -\mathcal{F}(x)]\mathrm{d}x+\frac{t_0}{2H_0\Omega_{1,0}}\right]-1,
    \end{equation}

### 2025-03-05 BAO/fixed.py

@@ -1,0 +1,140 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import emcee
+from getdist import plots, MCSamples
+import scipy
+import multiprocessing as mp
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+from solution import solution, z_max
+from solution import const_c
+from cross_section import cross_section
+
+# Prior values
+H0 = 70.0
+O20 = 0.3
+log_kC1 = -8.0
+rd = 150
+
+# Read data from csv file
+file_path = "BAO.csv"
+pandata = np.loadtxt(file_path, delimiter=',', skiprows=1, usecols=(3, 4, 5, 6, 7, 8, 9))
+z_eff = pandata[:, 0]
+D_M_obs = pandata[:, 1]
+D_M_err = pandata[:, 2]
+D_H_obs = pandata[:, 3]
+D_H_err = pandata[:, 4]
+D_V_obs = pandata[:, 5]
+D_V_err = pandata[:, 6]
+
+# Reduce the number of equation solutions
+class BAO:
+    def __init__(self, log_kC1, O20, H0, rd):
+        self.log_kC1 = log_kC1
+        self.O20 = O20
+        self.H0 = H0
+        self.rd = rd
+        self.z_list = np.array(solution(log_kC1, O20, H0).y[0,:])
+        self.zprime_list = np.array(solution(log_kC1, O20, H0).y[1,:])
+
+    def D_M(self, z):
+        idx = np.searchsorted(self.z_list, z)
+        if idx >= len(self.z_list):
+            idx = len(self.z_list) - 1
+        intrange = self.z_list[:idx]
+        integrand = -(1 + intrange) / self.zprime_list[:idx]
+        intvalue = np.trapz(integrand, intrange)
+        return intvalue * const_c
+
+    def D_H(self, z):
+        idx = np.searchsorted(self.z_list, z)
+        if idx >= len(self.z_list):
+            idx = len(self.z_list) - 1
+        z1 = self.zprime_list[idx]
+        Hz = -z1 / (1 + z)
+        return const_c / Hz
+
+    def D_V(self, z):
+        DM = self.D_M(z)
+        DH = self.D_H(z)
+        return (z * DM**2 * DH)**(1/3)
+
[…]

### 2025-03-05 solution.py

@@ -15,6 +15,44 @@ time_s = time_gyr.to(u.s)
 # Unit conversion (1/H0 to Gyr)
 transfer = (distance_km / time_s).value
 
+# theoretical solution
+
+def original_function(x, log_kC1, O10, H0):
+    kC1 = 10**log_kC1 * transfer
+    # p1 = 3 * H0 * np.sqrt(O10) * np.arctanh(x/H0/np.sqrt(O10))
+    p1 = 3 * H0 * np.sqrt(O10) * 1/2*np.log(np.abs(1+x/H0/np.sqrt(O10))/(1-x/H0/np.sqrt(O10)))
+    p2 = kC1 * np.log(x**2 - H0**2*O10)
+    p3 = kC1 * np.log(kC1*x**2 - 3*H0**2*O10*x + H0**2*O10*kC1)
+    p4 = 9*H0**4*O10**2 - 4*H0**2*O10*kC1**2
+    return (p1 - p2 + p3) / p4
+
+def constant_f(log_kC1, O10, H0):
+    kC1 = 10**log_kC1 * transfer
+    return kC1*np.log(kC1)/(H0**2*O10*(-4*kC1**2 + 9*H0**2*O10))
+
+def inverse_function(t, log_kC1, O10, H0):
+    varible = -t/(2*H0**2*O10) + constant_f(log_kC1, O10, H0)
+
+    def equation(x):
+        return original_function(x, log_kC1, O10, H0) - varible
+    
+    y = scipy.optimize.root_scalar(equation, x0=-H0, method='newton').root
+    return y
+
+def t_0(log_kC1, O10, H0):
+    p = original_function(-H0, log_kC1, O10, H0)
+    return (constant_f(log_kC1, O10, H0) - p) * 2 * H0**2 * O10
+
+def z_max(log_kC1, O10, H0):
+    def func(x):
+        return original_function(x, log_kC1, O10, H0) - constant_f(log_kC1, O10, H0)
+
+    integral = scipy.integrate.quad(func, -np.inf, -H0)
+    square = -t_0(log_kC1, O10, H0) / (2*H0*O10)
+    p = 2*H0**2*O10 * (integral[0] + square)
+    return np.exp(-p) - 1
+
+# numerical solution
 # Reconstruct z as a vector function z = [dz0, dz1, dz2]
 def function(t, z, kC1, O10, H0):
[…]

### 2025-03-17 article/article.tex
add introduction in the article

@@
 
-   \title{Self-interacting dark matter model without dark energy in cosmology}
+   \title{Constraint result to the self-interacting dark matter model without dark energy
+   in cosmology}
 
@@
 \section{Introduction}
+
+   The standard Λ-Cold Dark Matter (ΛCDM) model has been remarkably 
+   successful in explaining a wide range of cosmological observations, 
+   from the Cosmic Microwave Background (CMB) anisotropies to 
+   large-scale structure formation. However, there are also many 
+   alternative models that have been proposed to explain the
+   accelerated expansion of the Universe, such as the dynamical
+   dark energy models and the modified gravity models.
+
+   It has been shown that dark matter self-interaction could distribute 
+   to the accelerated expansion without dark energy component. According
+   to the Boltzmann formalism, the disequilibrium between dark matter particle
+   creation and annihilation processes would creat an effective source term 
+   making negative pressure just like the dark energy. \cite{refId0}
+   investigated the analytical solutions for the simple interacting dark matter (IDM) 
+   model, and find that the effective annihilation term is much smaller than the
+   results given by the general methods. The gravitational matter creation
+   model is mathematically equivalent to one case of the IDM models.
+
+   In this paper, we use the newly revised data from $H(z)$, supernovae Ia, 
+   quasars and baryon acoustic oscillation by using the Markov chain Monte
+   Carlo (MCMC) method. The result gives that the lower limit of the interacting
+   dark matter particle mass is about 1 eV.
 
@@
    \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
-   \cite{Borghi_2022};\cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia 
+   \cite{Borghi_2022};\cite{Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
    (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
@@
          \hline\hline
-         $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
+         $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & 
+         $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
          \hline
@@
    \begin{equation}
-      z_{\max}=\exp\left[\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
-      -\mathcal{F}(x)]\mathrm{d}x+\frac{t_0}{2H_0\Omega_{1,0}}\right]-1,
+      z_{\max}=\exp\left[2H_0^2\Omega_{1,0}\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
+      -\mathcal{F}(x)]\mathrm{d}x+H_0t_0\right]-1,
    \end{equation}

### 2025-04-07 article/article.tex
update data caculation

@@
 
-   The standard Λ-Cold Dark Matter (ΛCDM) model has been remarkably 
-   successful in explaining a wide range of cosmological observations, 
-   from the Cosmic Microwave Background (CMB) anisotropies to 
-   large-scale structure formation. However, there are also many 
-   alternative models that have been proposed to explain the
-   accelerated expansion of the Universe, such as the dynamical
+   The standard Λ-Cold Dark Matter (ΛCDM) model has been successful in 
+   explaining the accelerated expansion of the Universe (\cite{Riess_1998}; \cite{Perlmutter_1999}), 
+   from the cosmic microwave background (CMB) anisotropies (\cite{Bennett_1996}) to 
+   the measurement of baryon acoustic oscillations (BAO; \cite{Eisenstein_2005}). However, there are also many 
+   alternative models that have been proposed to explain, such as the dynamical
    dark energy models and the modified gravity models.
@@
    creation and annihilation processes would creat an effective source term 
-   making negative pressure just like the dark energy. \cite{refId0}
+   making negative pressure just like the dark energy. \cite{Basilakos_2009}
    investigated the analytical solutions for the simple interacting dark matter (IDM) 
@@
 
-   \cite{refId0} identified two functional forms for which
+   \cite{Basilakos_2009} identified two functional forms for which
    the previous Boltzmann equation can be solved analytically.
-   Refering to Appendix B in \cite{refId0}, only one of these two is of interest
+   Refering to Appendix B in \cite{Basilakos_2009}, only one of these two is of interest
    because it provides a ``$\propto a^{-3}$'' dependence of the scale factor,
@@
    \end{equation}
-   where $Z(t)=\int_{t_0}^ta^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$(\cite{refId0}).
+   where $Z(t)=\int_{t_0}^ta^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$ (\cite{Basilakos_2009}).
    Using the usual unit-less $\Omega$-like parameterization, we obtain that
@@
    where $\Omega_{2,0}=8\pi G\mathcal{D}/3H_0^2$ and 
-   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.(\cite{refId0})
+   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.(\cite{Basilakos_2009})
 
@@
 
-   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
+   To constrain the relevant IDM models (\cite{Basilakos_2009}), we use the newly revised
    observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001}; 
-   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Zhang_2014};
-   \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
-   \cite{Borghi_2022};\cite{Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
-   (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
+   \cite{Daniel.Stern_2010}; \cite{M.Moresco_2012}; \cite{Zhang_2014};
+   \cite{Moresco_2016}; \cite{10.1093/mnras/stx301}; \cite{10.1093/mnrasl/slv037}; 
+   \cite{Borghi_2022}; \cite{Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
+   (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
    the BAO data from SDSS and DESI 2024.
@@
    \end{equation}
-   where $c_s$ is the sound speed prior to recombination, which is given as
-   \begin{equation}
-      c_s(z)=\frac{c}{\sqrt{3\left(1+\frac{3\rho_{\mathrm{b}}(z)}{4\rho_{\gamma}(z)}\right)}}\simeq
-      \frac{c}{\sqrt{3\left(1+\frac{3\rho_{\mathrm{b}0}}{4\rho_{\gamma0}}\frac{1}{1+z}\right)}}.
-   \end{equation}
+   where $c_s$ is the sound speed prior to recombination.
 
@@
 
-   We use the 99\% and 1\% quantiles to determine the upper and lower
+   We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
    limits of the parameters, and the results are shown in Table \ref{tab:5}.
@@
    similar to SNe Ia result, what may refer that the QSO cannot
-   give an effective constraint.
+   give an effective constraint. It may be due to the data quality
+   at the high redshift.
 
@@
           & $0.330_{-0.016}^{+0.016}$ & $0.313_{-0.010}^{+0.010}$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-1.81$ & $<-2.30$ & $<-2.35$
-          & $<-2.66$ & $<-2.78$ & $<-3.21$ \\
-         $\log_{10}(M_x/$GeV) & $>-10.09$ & $>-9.62$ & $>-9.60$
-          & $>-9.25$ & $>-9.15$ & $>-8.70$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.17$ & $<-2.51$ & $<-2.57$
+          & $<-3.10$ & $<-2.88$ & $<-3.39$ \\
+         $\log_{10}(M_x/$GeV) & $>-9.77$ & $>-9.42$ & $>-9.40$
+          & $>-8.84$ & $>-9.03$ & $>-8.52$ \\
          \hline
@@
       Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
-      \frac{\kappa C_1\ln\kappa C_1}{H_0^2\Omega_{1,0}[-4(\kappa C_1)^2+9H_0^2\Omega_{1,0}]}.
+      \frac{\kappa C_1\ln\kappa C_1}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
    \end{equation}

### 2025-04-07 BAO/fixed.py

@@ -1,140 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import emcee
-from getdist import plots, MCSamples
-import scipy
-import multiprocessing as mp
-
-import sys
-import os
-sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from solution import solution, z_max
-from solution import const_c
-from cross_section import cross_section
-
-# Prior values
-H0 = 70.0
-O20 = 0.3
-log_kC1 = -8.0
-rd = 150
-
-# Read data from csv file
-file_path = "BAO.csv"
-pandata = np.loadtxt(file_path, delimiter=',', skiprows=1, usecols=(3, 4, 5, 6, 7, 8, 9))
-z_eff = pandata[:, 0]
-D_M_obs = pandata[:, 1]
-D_M_err = pandata[:, 2]
-D_H_obs = pandata[:, 3]
-D_H_err = pandata[:, 4]
-D_V_obs = pandata[:, 5]
-D_V_err = pandata[:, 6]
-
-# Reduce the number of equation solutions
-class BAO:
-    def __init__(self, log_kC1, O20, H0, rd):
-        self.log_kC1 = log_kC1
-        self.O20 = O20
-        self.H0 = H0
-        self.rd = rd
-        self.z_list = np.array(solution(log_kC1, O20, H0).y[0,:])
-        self.zprime_list = np.array(solution(log_kC1, O20, H0).y[1,:])
-
-    def D_M(self, z):
-        idx = np.searchsorted(self.z_list, z)
-        if idx >= len(self.z_list):
-            idx = len(self.z_list) - 1
-        intrange = self.z_list[:idx]
-        integrand = -(1 + intrange) / self.zprime_list[:idx]
-        intvalue = np.trapz(integrand, intrange)
-        return intvalue * const_c
-
-    def D_H(self, z):
-        idx = np.searchsorted(self.z_list, z)
-        if idx >= len(self.z_list):
-            idx = len(self.z_list) - 1
-        z1 = self.zprime_list[idx]
-        Hz = -z1 / (1 + z)
-        return const_c / Hz
-
-    def D_V(self, z):
-        DM = self.D_M(z)
-        DH = self.D_H(z)
-        return (z * DM**2 * DH)**(1/3)
-
[…]

### 2025-04-07 BAO/result.py

@@ -45,7 +45,7 @@ class BAO:
             idx = len(self.z_list) - 1
         intrange = self.z_list[:idx]
         integrand = -(1 + intrange) / self.zprime_list[:idx]
-        intvalue = np.trapz(integrand, intrange)
+        intvalue = np.trapezoid(integrand, intrange)
         return intvalue * const_c
 
     def D_H(self, z):

### 2025-04-07 QSO/result1.py

@@ -33,7 +33,7 @@ def DM_z(log_kC1, O20, H0):
         idx = np.searchsorted(z_values, z_value)
         if idx >= len(z_values):  
             idx = len(z_values) - 1
-        int_value = -np.trapz(z_values[:idx], t_values[:idx])
+        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
         dl_value = const_c * (1 + z_value) * (t0 - t_values[idx] + int_value)
         dl_values.append(dl_value)
 

### 2025-04-07 QSO/result2.py

@@ -38,7 +38,7 @@ def logFX_z(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1):
         idx = np.searchsorted(z_values, z_value)
         if idx >= len(z_values):  
             idx = len(z_values) - 1
-        int_value = -np.trapz(z_values[:idx], t_values[:idx])
+        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
         dl_value = const_c * (1 + z_value) * (t0 - t_values[idx] + int_value)
         dl_values.append(dl_value)
 

### 2025-04-07 SNe/result2.py

@@ -37,7 +37,7 @@ def chi_square(log_kC1, O20, H0):
         idx = np.searchsorted(z_values, z_hz_value)
         if idx >= len(z_values):  
             idx = len(z_values) - 1
-        int_value = -np.trapz(z_values[:idx], t_values[:idx])
+        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
         dl_value = const_c * (1 + z_hz_value) * (t0 - t_values[idx] + int_value)
         dl_values.append(dl_value)
 

### 2025-04-07 multimethods/methods1.py

@@ -41,7 +41,6 @@ def main():
     nll = lambda *args: -lnlike(*args)
     initial = np.array([0.3, -5, 70, 0.6, 0, 6, 1, 0.2])
     # soln = scipy.optimize.minimize(nll, initial)
-    # pos = soln.x + 1e-4 * np.random.randn(50, 6)
     pos = initial + 1e-4 * np.random.randn(50, 8)
     nwalkers, ndim = pos.shape
 

### 2025-04-07 pdf_cdf.py

@@ -34,8 +34,8 @@ def main():
     H0_OHD_list = np.array([H0_OHD]*len(flat_samples_OHD))
     Mx_OHD = np.log10(cross_section(flat_samples_OHD[:,0], H0_OHD_list)) - flat_samples_OHD[:,1]
 
-    upper_limit['OHD'] = np.percentile(flat_samples_OHD[:,1], 99)
-    lower_limit['OHD'] = np.percentile(Mx_OHD, 1)
+    upper_limit['OHD'] = np.percentile(flat_samples_OHD[:,1], 97.7)
+    lower_limit['OHD'] = np.percentile(Mx_OHD, 2.3)
 
     ## SNe
     nll = lambda *args: -SNe.result2.lnlike(*args)
@@ -52,8 +52,8 @@ def main():
     H0_SNe_list = np.array([H0_SNe]*len(flat_samples_SNe))
     Mx_SNe = np.log10(cross_section(flat_samples_SNe[:,0], H0_SNe_list)) - flat_samples_SNe[:,1]
 
-    upper_limit['SNe'] = np.percentile(flat_samples_SNe[:,1], 99)
-    lower_limit['SNe'] = np.percentile(Mx_SNe, 1)
+    upper_limit['SNe'] = np.percentile(flat_samples_SNe[:,1], 97.7)
+    lower_limit['SNe'] = np.percentile(Mx_SNe, 2.3)
 
     ## OHD+SNe
     nll = lambda *args: -methods2.lnlike(*args)
@@ -70,8 +70,8 @@ def main():
     H0_m2_list = np.array([H0_m2]*len(flat_samples_m2))
     Mx_m2 = np.log10(cross_section(flat_samples_m2[:,0], H0_m2_list)) - flat_samples_m2[:,1]
 
-    upper_limit['OHD+SNe'] = np.percentile(flat_samples_m2[:,1], 99)
-    lower_limit['OHD+SNe'] = np.percentile(Mx_m2, 1)
+    upper_limit['OHD+SNe'] = np.percentile(flat_samples_m2[:,1], 97.7)
+    lower_limit['OHD+SNe'] = np.percentile(Mx_m2, 2.3)
 
     ## SNe+QSO
     nll = lambda *args: -methods1.lnlike(*args)
@@ -88,8 +88,8 @@ def main():
     H0_m1_list = np.array([H0_m1]*len(flat_samples_m1))
[…]

### 2025-04-09 article/article.tex
seperate the data caculating and figure plotting

@@
    The standard Λ-Cold Dark Matter (ΛCDM) model has been successful in 
-   explaining the accelerated expansion of the Universe (\cite{Riess_1998}; \cite{Perlmutter_1999}), 
+   explaining the accelerated expansion of the Universe (\cite{Riess_1998,Perlmutter_1999}), 
    from the cosmic microwave background (CMB) anisotropies (\cite{Bennett_1996}) to 
-   the measurement of baryon acoustic oscillations (BAO; \cite{Eisenstein_2005}). However, there are also many 
-   alternative models that have been proposed to explain, such as the dynamical
-   dark energy models and the modified gravity models.
+   the measurement of baryon acoustic oscillations (BAO; \cite{Eisenstein_2005}). 
+   However, there are also many alternative models that have been proposed to describe 
+   the phenomenon, such as the canonical ``quintessence" scalar field theories 
+   (\cite{PhysRevD.37.3406, WETTERICH1988668,PhysRevLett.80.1582}),
+   non-canonical ``k-essence" theories (\cite{PhysRevLett.85.4438, PhysRevD.63.103510})
+   and the modified gravity models (see, e.g., \cite{CLIFTON20121} for a review).
 
-   It has been shown that dark matter self-interaction could distribute 
-   to the accelerated expansion without dark energy component. According
-   to the Boltzmann formalism, the disequilibrium between dark matter particle
+   It has been shown that dark matter self-interaction could contribute 
+   to the accelerated expansion without dark energy component (\cite{PhysRevD.64.063501, Balakin_2003}). 
+   According to the Boltzmann formalism, the disequilibrium between dark matter particle
    creation and annihilation processes would creat an effective source term 
@@
    model, and find that the effective annihilation term is much smaller than the
-   results given by the general methods. The gravitational matter creation
-   model is mathematically equivalent to one case of the IDM models.
+   results given by the general methods. The gravitational matter creation model (\cite{Lima_2008})
+   is mathematically equivalent to one case of the IDM models (\cite{Basilakos_2009}).
 
@@
    We assume that the total density of the cosmic fluid obeys
-   the collisional Boltzmann equation
+   the collisional Boltzmann equation (\cite{Kolb:1990vq})
    \begin{equation}
@@
    \end{equation}
-   where $\mathcal{D}=C_2-C-1$. The conditions in which the current 
+   where $\mathcal{D}=C_2-C_1$. The conditions in which the current 
    model acts as a quintessence cosmology are given by $\mathcal{D}>0,
    C_1>0,$ and $w_{\text{IDM}}=-1-n/3$. This solution is mathematically
-   equivalent to that of the gravitational matter creation model of().
+   equivalent to that of the gravitational matter creation model of \cite{Lima_2008}.
    The Hubble flow is now given by
@@
    To constrain the relevant IDM models (\cite{Basilakos_2009}), we use the newly revised
-   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001}; 
-   \cite{Daniel.Stern_2010}; \cite{M.Moresco_2012}; \cite{Zhang_2014};
-   \cite{Moresco_2016}; \cite{10.1093/mnras/stx301}; \cite{10.1093/mnrasl/slv037}; 
-   \cite{Borghi_2022}; \cite{Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
+   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001, Daniel.Stern_2010, 
+   M.Moresco_2012, Zhang_2014, Moresco_2016, 10.1093/mnras/stx301, 10.1093/mnrasl/slv037, 
+   Borghi_2022, Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
    (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
-   the BAO data from SDSS and DESI 2024.
+   the BAO data from SDSS (\cite{PhysRevD.103.083533}) and DESI 2024 
+   (\cite{desicollaboration2024desi2024vicosmological}).
 
@@
    \begin{table}[htbp]
-      \caption{The OHD dataset}
       \centering
@@
       \end{tabular}
+      \caption{The OHD dataset from different paper.}
       \label{tab:1}
@@
 
-   SNe Ia have long been used as "standard candles" to give a direct
+   SNe Ia have long been used as ``standard candles" to give a direct
    measurement of their luminosity distance, and provides strong constraints
    on cosmological parameters. We use the latest Pantheon+ data set of 1701 
-   SNe Ia samples(\cite{Scolnic_2022}), which covers the redshift range [0, 2.26].
+   SNe Ia samples (\cite{Scolnic_2022}), which covers the redshift range [0, 2.26].
 
-   We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
-   host distances(\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
+   We use the fiducial SNe Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
+   host distances (\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
    give the $\chi^2$ as 
@@
    where $B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
-   Apparently these two functions give the same constraints in $\Omega_{2,0}$ and
+   Apparently, these two functions give the same constraints in $\Omega_{2,0}$ and
    $\log_{10}(\kappa C_1)$.
@@
 
-   The Baryon acoustic oscillation method (BAO) provides a key cosmological probe
+   The Baryon acoustic oscillation (BAO) method provides a key cosmological probe
    sensitive to the cosmic expansion history with well-controlled systematics.
-   We use two BAO data sets from the SDSS(\cite{PhysRevD.103.083533}) and DESI 2024(\cite{desicollaboration2024desi2024vicosmological}),
+   We use two BAO datasets from the SDSS (\cite{PhysRevD.103.083533}) and DESI 2024 (\cite{desicollaboration2024desi2024vicosmological}),
    which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
@@
    \begin{table}[htbp]
-      \caption{The BAO-only dataset from SDSS}
       \centering
@@
       \end{tabular}
+      \caption{The BAO-only dataset from SDSS. The $\sigma$ of asymmetric 
+      uncertainties would be calculated on average.}
       \label{tab:2}
@@
    \begin{table}[htbp]
-      \caption{The BAO dataset from DESI 2024}
       \centering
@@
       \end{tabular}
+      \caption{The BAO dataset from DESI 2024.}
       \label{tab:3}
@@
    to the dark matter particle mass $M_x$.
-
    The prior range set for free parameters are given at Table \ref{tab:4}
@@
    \begin{table}[htbp]
-      \caption{Parameters and priors used in analysis}
       \centering
@@
       \end{tabular}
+      \caption{Parameters and priors used in analysis. 
+      All of the priors are flat in the ranges given. 
+      The $\log_{10}(\kappa C_1)$ does not have a predicted value, 
+      and the initial value of each chain is selected randomly uniformly
+      within the prior range.}
       \label{tab:4}
    \end{table}
+
+   For the BAO dataset, we use $h \simeq 0.7$ as the default value to give constraints.
 
@@
    The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
-   $\log_{10}(\kappa C_1)\to-\infty$, therefore the constraints
+   $\log_{10}(\kappa C_1)\to-\infty$, thus the constraints
    could only give the upper limit of what, and give the lower limit
@@
    We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
-   limits of the parameters, and the results are shown in Table \ref{tab:5}.
+   limits of the parameters. The  constraint results are shown in 
+   Figure \ref{fig:1}-\ref{fig:6} and summarized in Table \ref{tab:5}.
 
@@
       \caption{The constraint result from the observational
-      $H(z)$ data}
+      $H(z)$ data.}
+      \label{fig:1}
    \end{figure}
@@
       \caption{The constraint result from the supernovae
-      Ia data}
+      Ia data.}
    \end{figure}
@@
       }
-      \caption{The constraint result from the SNe Ia + QSO data}
+      \caption{The constraint result from the SNe Ia + QSO data.}
    \end{figure}
 
-   We would find that the SNe Ia and QSO combined result is most
+   We could find that the combined result of SNe Ia and QSO is most
    similar to SNe Ia result, what may refer that the QSO cannot
    give an effective constraint. It may be due to the data quality
-   at the high redshift.
+   at the high redshift, while the effective redshift of QSO as tracers in BAO
+   is about 1.5, within the SNe Ia range.
 
@@
       }
-      \caption{The constraint result from the BAO data}
+      \caption{The constraint result from the BAO data.}
    \end{figure}
@@
       }
-      \caption{The constraint result from the OHD + SNe Ia data}
+      \caption{The constraint result from the OHD + SNe Ia data.}
    \end{figure}
@@
       }
-      \caption{The constraint result from the OHD + SNe Ia + BAO data}
+      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
+      \label{fig:6}
    \end{figure}
@@
    \begin{table*}[htbp]
-      \caption{The constraint results of Model 1}
       \centering
@@
       \end{tabular}
+      \caption{The constraint results of Model 1.}
       \label{tab:5}
@@
       \caption{The constraint result from the observational
-      $H(z)$ data}
+      $H(z)$ data.}
    \end{figure}
@@
       }
-      \caption{The constraint result from the SNe Ia + QSO data}
+      \caption{The constraint result from the SNe Ia + QSO data.}
    \end{figure}
@@
       }
-      \caption{The constraint result from the OHD + SNe Ia + BAO data}
+      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
    \end{figure}
@@
    \begin{table*}[htbp]
-      \caption{The constraint results of Model 2}
       \centering
@@
       \end{tabular}
+      \caption{The constraint results of Model 2.}
       \label{tab:6}

### 2025-04-09 OHD/result.py

@@ -1,8 +1,6 @@
 # Import packages
 import numpy as np
-import matplotlib.pyplot as plt
 import emcee
-from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
@@ -10,7 +8,6 @@ import sys
 import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
 from solution import solution
-from cross_section import cross_section
 
 # Prior values
 H0 = 70.0
@@ -52,7 +49,7 @@ def lnlike(paras):
 # lnprior function (prior probability function)
 def lnprior(paras):
     O20, log_kC1, H0 = paras
-    if 0 < O20 < 0.7 and -10 < log_kC1 < 0 and 60 < H0 < 80:
+    if 0 < O20 < 1.0 and -10 < log_kC1 < 0 and 60 < H0 < 80:
         return 0.0
     return -np.inf
 
@@ -74,36 +71,9 @@ def main():
     # Multithreaded MCMC
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
-
-    # MCMC result plot
-    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
-    names = ['O20', 'log_kC1', 'H0']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['b'], title_limit=1)
-    g.export('./article/pictures/ohd.pdf')
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
-    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['b'])
-    g.export('./article/pictures/ohd_1.pdf')
-
-    H0 = np.median(flat_samples[:,2])
-    H0_list = np.array([H0]*len(flat_samples))
[…]

### 2025-04-09 QSO/#result1.py

@@ -1,0 +1,107 @@
+# use dm
+import numpy as np
+import matplotlib.pyplot as plt
+import emcee
+from getdist import plots, MCSamples
+import scipy
+import multiprocessing as mp
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+from solution import solution
+from solution import const_c
+from cross_section import cross_section
+
+H0 = 70.0
+O20 = 0.3
+log_kC1 = -5.0
+
+file_path = "./QSO/data/dm.dat"
+data = np.loadtxt(file_path)
+z = data[:,0]
+DM = data[:,1]
+e_DM = data[:,2]
+
+def DM_z(log_kC1, O20, H0):
+    t0 = 1 / H0
+    t_values = solution(log_kC1, O20, H0).t
+    z_values = solution(log_kC1, O20, H0).y[0, :]
+    dl_values = []
+
+    for z_value in z:
+        idx = np.searchsorted(z_values, z_value)
+        if idx >= len(z_values):  
+            idx = len(z_values) - 1
+        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
+        dl_value = const_c * (1 + z_value) * (t0 - t_values[idx] + int_value)
+        dl_values.append(dl_value)
+
+    dl = np.array(dl_values)
+    muth = 5 * np.log10(dl) + 25
+    return muth
+
+def chi_square(log_kC1, O20, H0):
+    delta_DM = DM_z(log_kC1, O20, H0) - DM
+    chi2 = np.sum(delta_DM**2/e_DM**2)
+    return chi2
+
+def lnlike(paras):
+    O20, log_kC1, H0 = paras
+    chi2 = chi_square(log_kC1, O20, H0)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    O20, log_kC1, H0 = paras
+    if 0 < O20 < 1 and -10 < log_kC1 < 0 and 60 < H0 < 80:
+        return 0.0
+    return -np.inf
+
+def lnprob(paras):
+    lp = lnprior(paras)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(paras)
+
+def main():
+    nll = lambda *args: -lnlike(*args)
+    initial = np.array([0.35, -4, 70])
+    # soln = scipy.optimize.minimize(nll, initial)
[…]

### 2025-04-09 QSO/result1.py

@@ -1,107 +1,0 @@
-# use dm
-import numpy as np
-import matplotlib.pyplot as plt
-import emcee
-from getdist import plots, MCSamples
-import scipy
-import multiprocessing as mp
-
-import sys
-import os
-sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from solution import solution
-from solution import const_c
-from cross_section import cross_section
-
-H0 = 70.0
-O20 = 0.3
-log_kC1 = -5.0
-
-file_path = "./QSO/data/dm.dat"
-data = np.loadtxt(file_path)
-z = data[:,0]
-DM = data[:,1]
-e_DM = data[:,2]
-
-def DM_z(log_kC1, O20, H0):
-    t0 = 1 / H0
-    t_values = solution(log_kC1, O20, H0).t
-    z_values = solution(log_kC1, O20, H0).y[0, :]
-    dl_values = []
-
-    for z_value in z:
-        idx = np.searchsorted(z_values, z_value)
-        if idx >= len(z_values):  
-            idx = len(z_values) - 1
-        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
-        dl_value = const_c * (1 + z_value) * (t0 - t_values[idx] + int_value)
-        dl_values.append(dl_value)
-
-    dl = np.array(dl_values)
-    muth = 5 * np.log10(dl) + 25
-    return muth
-
-def chi_square(log_kC1, O20, H0):
-    delta_DM = DM_z(log_kC1, O20, H0) - DM
-    chi2 = np.sum(delta_DM**2/e_DM**2)
-    return chi2
-
-def lnlike(paras):
-    O20, log_kC1, H0 = paras
-    chi2 = chi_square(log_kC1, O20, H0)
-    return -0.5 * chi2
-
-def lnprior(paras):
-    O20, log_kC1, H0 = paras
-    if 0 < O20 < 1 and -10 < log_kC1 < 0 and 60 < H0 < 80:
-        return 0.0
-    return -np.inf
-
-def lnprob(paras):
-    lp = lnprior(paras)
-    if not np.isfinite(lp):
-        return -np.inf
-    return lp + lnlike(paras)
-
-def main():
-    nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.35, -4, 70])
-    # soln = scipy.optimize.minimize(nll, initial)
[…]

### 2025-04-09 SNe/result1.py

@@ -1,111 +1,0 @@
-import numpy as np
-from getdist import plots, MCSamples
-import emcee
-import corner
-import scipy
-import multiprocessing as mp
-
-import sys
-import os
-sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from solution import solution
-from solution import const_c
-from cross_section import cross_section
-
-H0 = 70.0
-O20 = 0.3
-log_kC1 = -5.0
-
-# pantheon+
-file_path = "./SNe/Pantheon+ data/Pantheon+SH0ES.dat"
-pandata = np.loadtxt(file_path, skiprows=1, usecols=(2, 10))
-z_hd = pandata[:, 0]
-mu = pandata[:, 1]
-
-file_path_cov = './SNe/Pantheon+ data/Pantheon+SH0ES_cov.dat'
-cov = np.loadtxt(file_path_cov, skiprows=1)
-cov_matrix = cov.reshape((1701, 1701))
-cov_matrix_inv = np.linalg.inv(cov_matrix)
-
-def chi_square(log_kC1, O20, H0):
-    t0 = 1 / H0
-    t_values = solution(log_kC1, O20, H0).t
-    z_values = solution(log_kC1, O20, H0).y[0, :]
-    dl_values = []
-
-    for z_hz_value in z_hd:
-        idx = np.searchsorted(z_values, z_hz_value)
-        if idx >= len(z_values):  
-            idx = len(z_values) - 1
-        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
-        dl_value = const_c * (1 + z_hz_value) * (t0 - t_values[idx] + int_value)
-        dl_values.append(dl_value)
-
-    dl = np.array(dl_values)
-    muth = 5 * np.log10(dl) + 25
-    delta_mu = muth - mu
-    A = np.dot(delta_mu, np.dot(cov_matrix_inv, delta_mu))
-    B = np.sum(np.dot(cov_matrix_inv, delta_mu))
-    C = np.sum(cov_matrix_inv)
-    chi2 = A - B**2/C + np.log(C/(2*np.pi))
-    return chi2
-
-def lnlike(paras):
-    O20, log_kC1, H0 = paras
-    chi2 = chi_square(log_kC1, O20, H0)
-    return -0.5 * chi2
-
-def lnprior(paras):
-    O20, log_kC1, H0 = paras
-    if 0 < O20 < 0.5 and -10 < log_kC1 < 0 and 60 < H0 < 80:
[…]

### 2025-04-09 SNe/result2.py

@@ -1,7 +1,5 @@
 import numpy as np
-import matplotlib.pyplot as plt
 import emcee
-from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
@@ -10,7 +8,6 @@ import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
 from solution import solution
 from solution import const_c
-from cross_section import cross_section
 
 H0 = 70.0
 O20 = 0.3
@@ -44,7 +41,7 @@ def chi_square(log_kC1, O20, H0):
     dl = np.array(dl_values)
     muth = 5 * np.log10(dl) + 25
     delta_mu = muth - mu
-    chi2 = np.dot(delta_mu, np.dot(cov_matrix_inv, delta_mu))
+    chi2 = delta_mu @ cov_matrix_inv @ delta_mu.T
     return chi2
 
 def lnlike(paras):
@@ -54,7 +51,7 @@ def lnlike(paras):
 
 def lnprior(paras):
     O20, log_kC1, H0 = paras
-    if 0 < O20 < 0.5 and -10 < log_kC1 < 0 and 60 < H0 < 80:
+    if 0 < O20 < 1.0 and -10 < log_kC1 < 0 and 60 < H0 < 80:
         return 0.0
     return -np.inf
 
@@ -73,35 +70,9 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress=True)
-
-    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
-    names = ['O20', 'log_kC1', 'H0']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['g'], title_limit=1)
-    g.export('./article/pictures/sne.pdf')
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
[…]

### 2025-04-09 multimethods/methods1.py

@@ -1,12 +1,10 @@
 import numpy as np
 import emcee
-from getdist import plots, MCSamples
 import multiprocessing as mp
 
 import sys
 import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from cross_section import cross_section
 
 H0 = 70.0
 O20 = 0.3
@@ -16,9 +14,9 @@ import QSO.result2
 def chi_square_QSO(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta):
     return QSO.result2.chi_square(log_kC1, O20, H0, gamma0, gamma1, beta0, beta1, delta)
 
-import SNe.result1
+import SNe.result2
 def chi_square_SNe(log_kC1, O20, H0):
-    return SNe.result1.chi_square(log_kC1, O20, H0)
+    return SNe.result2.chi_square(log_kC1, O20, H0)
 
 def lnlike(paras):
     O20, log_kC1, H0, gamma0, gamma1, beta0, beta1, delta = paras
@@ -40,41 +38,14 @@ def lnprob(paras):
 def main():
     nll = lambda *args: -lnlike(*args)
     initial = np.array([0.3, -5, 70, 0.6, 0, 6, 1, 0.2])
-    # soln = scipy.optimize.minimize(nll, initial)
     pos = initial + 1e-4 * np.random.randn(50, 8)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
-
-    labels = [r'\Omega_{2,0}',r'\log_{10}(\kappa C_1/Gyr{}^{-1})','H_0[km/s/Mpc]',r'\gamma_0',r'\gamma_1',r'\beta_0',r'\beta_1',r'\delta']
-    names = ['O20','log_kC1','H0','gamma0','gamma1','beta0','beta1','delta']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None), 'H0':(60,80)})
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['b'], title_limit=1)
-    g.export('./article/pictures/sne_qso.pdf')
[…]

### 2025-04-09 multimethods/methods2.py

@@ -1,14 +1,11 @@
 import numpy as np
-import matplotlib.pyplot as plt
 import emcee
-from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
 import sys
 import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from cross_section import cross_section
 
 # Prior values
 H0 = 70.0
@@ -53,35 +50,9 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
-
-    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]']
-    names = ['O20', 'log_kC1', 'H0']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['c'], title_limit=1)
-    g.export('./article/pictures/ohd_sne.pdf')
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['c'])
-    g.export('./article/pictures/ohd_sne_1.pdf')
-
-    H0 = np.median(flat_samples[:,2])
-    H0_list = np.array([H0]*len(flat_samples))
-    # Plot Mx vs O20 corner plot
-    Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
-    combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
-    labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    names_ = ['O20', 'Mx']
-    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
-    g = plots.get_single_plotter(ratio=1)    
[…]

### 2025-04-09 multimethods/methods3.py

@@ -1,14 +1,11 @@
 import numpy as np
-import matplotlib.pyplot as plt
 import emcee
-from getdist import plots, MCSamples
 import scipy
 import multiprocessing as mp
 
 import sys
 import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from cross_section import cross_section
 
 H0 = 70.0
 O20 = 0.3
@@ -58,35 +55,10 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
-
-    labels = [r'\Omega_{2,0}', r'\log_{10}(\kappa C_1/Gyr{}^{-1})', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
-    names = ['O20', 'log_kC1', 'H0', 'rdh']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'log_kC1':(-10, None)})
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['m'], title_limit=1)
-    g.export('./article/pictures/ohd_sne_bao.pdf')
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2], ranges={'log_kC1':(-10, None)})
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_2, 'O20', 'log_kC1', filled=True, colors=['m'])
-    g.export('./article/pictures/ohd_sne_bao_1.pdf')
-
-    H0 = np.median(flat_samples[:,2])
-    H0_list = np.array([H0]*len(flat_samples))
-    Mx = np.log10(cross_section(flat_samples[:,0], H0_list)) - flat_samples[:,1]
-    combined_samples = np.vstack((flat_samples[:, 0], Mx)).T
-    labels_ = [r'\Omega_{2,0}', r'\log_{10}(M_x/GeV)']
-    names_ = ['O20', 'Mx']
-    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_, ranges={'Mx':(None, -2)})
-    g = plots.get_single_plotter(ratio=1)    
[…]

### 2025-04-09 pdf_cdf.py

@@ -1,35 +1,15 @@
-import scipy
 import numpy as np
 import matplotlib.pyplot as plt
-import multiprocessing as mp
-import emcee
 import seaborn as sns
 import pandas as pd
-
-import OHD.result
-import SNe.result2
-import BAO.result
-import multimethods.methods1 as methods1
-import multimethods.methods2 as methods2
-import multimethods.methods3 as methods3
 
 from cross_section import cross_section
 
 def main():
     upper_limit = {}
     lower_limit = {}
-    ## OHD
-    initial = np.array([0.3, -5, 70])
-    nll = lambda *args: -OHD.result.lnlike(*args)
-    soln = scipy.optimize.minimize(nll, initial)
-    pos = soln.x + 1e-4 * np.random.randn(50, 3)
-    nwalkers, ndim = pos.shape
 
-    with mp.Pool() as pool:
-        sampler_OHD = emcee.EnsembleSampler(nwalkers, ndim, OHD.result.lnprob, pool=pool)
-        sampler_OHD.run_mcmc(pos, 2000, progress = True)
-
-    flat_samples_OHD = sampler_OHD.get_chain(discard=200, flat=True)
+    flat_samples_OHD = np.loadtxt('./OHD/output.dat')
     H0_OHD = np.median(flat_samples_OHD[:,2])
     H0_OHD_list = np.array([H0_OHD]*len(flat_samples_OHD))
     Mx_OHD = np.log10(cross_section(flat_samples_OHD[:,0], H0_OHD_list)) - flat_samples_OHD[:,1]
@@ -37,17 +17,7 @@ def main():
     upper_limit['OHD'] = np.percentile(flat_samples_OHD[:,1], 97.7)
     lower_limit['OHD'] = np.percentile(Mx_OHD, 2.3)
 
-    ## SNe
-    nll = lambda *args: -SNe.result2.lnlike(*args)
-    soln = scipy.optimize.minimize(nll, initial)
-    pos = soln.x + 1e-4 * np.random.randn(50, 3)
-    nwalkers, ndim = pos.shape
-
-    with mp.Pool() as pool:
-        sampler_SNe = emcee.EnsembleSampler(nwalkers, ndim, SNe.result2.lnprob, pool=pool)
[…]

### 2025-04-14 article/article.tex
update to desi dr2

@@
 
-   \author{Yixuan Zhu}\affiliation{Department of Astronomy, Beijing Normal University.
-   Beijing 100875.
-   PR China}
+   \author{Yixuan Zhu}\affiliation{Department of Astronomy, Beijing Normal University,
+   Beijing 100875, China}
 
@@
    (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
-   the BAO data from SDSS (\cite{PhysRevD.103.083533}) and DESI 2024 
-   (\cite{desicollaboration2024desi2024vicosmological}).
+   the BAO data from SDSS-IV (\cite{PhysRevD.103.083533}) and DESI DR2 
+   (\cite{desicollaboration2025desidr2resultsii}).
 
@@
    \begin{equation}
-      \chi_{\text{OHD}}^2=\sum_i^{33}\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
+      \chi_{\text{OHD}}^2=\sum_i\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
    \end{equation}
@@
       \centering
-      \begin{tabular}{llll}
+      \begin{tabular}{ccl}
          \hline\hline
@@
          \hline     
-         0.07 & 69$\pm$19.6 & \cite{Zhang_2014} \\
-         0.09 & 69$\pm$12 & \cite{PhysRevD.71.123001} \\
-         0.12 & 68.6$\pm$26.2 & \cite{Zhang_2014} \\
-         0.17 & 83$\pm$8 & \cite{PhysRevD.71.123001} \\
-         0.179 & 75$\pm$4 & \cite{M.Moresco_2012} \\
-         0.199 & 75$\pm$5 & \cite{M.Moresco_2012} \\
-         0.2 & 72.9$\pm$29.6 & \cite{Zhang_2014} \\
-         0.27 & 77$\pm$14 & \cite{PhysRevD.71.123001} \\
-         0.28 & 88.8$\pm$36.6 & \cite{Zhang_2014} \\
-         0.352 & 83$\pm$14 & \cite{M.Moresco_2012} \\
-         0.3802 & 83$\pm$13.5 & \cite{Moresco_2016}  \\
-         0.4 & 95$\pm$17 & \cite{PhysRevD.71.123001} \\
-         0.4004 & 77$\pm$10.2 & \cite{Moresco_2016} \\
-         0.4247 & 87.1$\pm$11.2 & \cite{Moresco_2016} \\
-         0.4497 & 92.8$\pm$12.9 & \cite{Moresco_2016} \\
-         0.47 & 89$\pm$34 & \cite{10.1093/mnras/stx301} \\
-         0.4783 & 80.9$\pm$9 & \cite{Moresco_2016} \\
-         0.48 & 97$\pm$62 & \cite{Daniel.Stern_2010} \\
-         0.593 & 104$\pm$13 & \cite{M.Moresco_2012} \\
-         0.68 & 92$\pm$8 & \cite{M.Moresco_2012} \\
-         0.75 & 98.8$\pm$33.6 & \cite{Borghi_2022} \\
-         0.781 & 105$\pm$12 & \cite{M.Moresco_2012} \\
-         0.8 & 113.1$\pm$15.1 & \cite{Jiao_2023} \\
-         0.875 & 125$\pm$17 & \cite{M.Moresco_2012} \\
-         0.88 & 90$\pm$40 & \cite{Daniel.Stern_2010} \\
-         0.9 & 117$\pm$23 & \cite{PhysRevD.71.123001} \\
-         1.037 & 154$\pm$20 & \cite{M.Moresco_2012} \\
-         1.3 & 168$\pm$17 & \cite{PhysRevD.71.123001} \\
-         1.363 & 160$\pm$33.6 & \cite{10.1093/mnrasl/slv037} \\
-         1.43 & 177$\pm$18 & \cite{PhysRevD.71.123001} \\
-         1.53 & 140$\pm$14 & \cite{PhysRevD.71.123001} \\
-         1.75 & 202$\pm$40 & \cite{PhysRevD.71.123001} \\
-         1.965 & 186.5$\pm$50.4 & \cite{10.1093/mnrasl/slv037} \\
+         0.07 & $69 \pm 19.6$ & \cite{Zhang_2014} \\
+         0.09 & $69 \pm 12$ & \cite{PhysRevD.71.123001} \\
+         0.12 & $68.6 \pm 26.2$ & \cite{Zhang_2014} \\
+         0.17 & $83 \pm 8$ & \cite{PhysRevD.71.123001} \\
+         0.179 & $75 \pm 4$ & \cite{M.Moresco_2012} \\
+         0.199 & $75 \pm 5$ & \cite{M.Moresco_2012} \\
+         0.2 & $72.9 \pm 29.6$ & \cite{Zhang_2014} \\
+         0.27 & $77 \pm 14$ & \cite{PhysRevD.71.123001} \\
+         0.28 & $88.8 \pm 36.6$ & \cite{Zhang_2014} \\
+         0.352 & $83 \pm 14$ & \cite{M.Moresco_2012} \\
+         0.3802 & $83 \pm 13.5$ & \cite{Moresco_2016}  \\
+         0.4 & $95 \pm 17$ & \cite{PhysRevD.71.123001} \\
+         0.4004 & $77 \pm 10.2$ & \cite{Moresco_2016} \\
+         0.4247 & $87.1 \pm 11.2$ & \cite{Moresco_2016} \\
+         0.4497 & $92.8 \pm 12.9$ & \cite{Moresco_2016} \\
+         0.47 & $89 \pm 34$ & \cite{10.1093/mnras/stx301} \\
+         0.4783 & $80.9 \pm 9$ & \cite{Moresco_2016} \\
+         0.48 & $97 \pm 62$ & \cite{Daniel.Stern_2010} \\
+         0.593 & $104 \pm 13$ & \cite{M.Moresco_2012} \\
+         0.68 & $92 \pm 8$ & \cite{M.Moresco_2012} \\
+         0.75 & $98.8 \pm 33.6$ & \cite{Borghi_2022} \\
+         0.781 & $105 \pm 12$ & \cite{M.Moresco_2012} \\
+         0.8 & $113.1 \pm 15.1$ & \cite{Jiao_2023} \\
+         0.875 & $125 \pm 17$ & \cite{M.Moresco_2012} \\
+         0.88 & $90 \pm 40$ & \cite{Daniel.Stern_2010} \\
+         0.9 & $117 \pm 23$ & \cite{PhysRevD.71.123001} \\
+         1.037 & $154 \pm 20$ & \cite{M.Moresco_2012} \\
+         1.3 & $168 \pm 17$ & \cite{PhysRevD.71.123001} \\
+         1.363 & $160 \pm 33.6$ & \cite{10.1093/mnrasl/slv037} \\
+         1.43 & $177 \pm 18$ & \cite{PhysRevD.71.123001} \\
+         1.53 & $140 \pm 14$ & \cite{PhysRevD.71.123001} \\
+         1.75 & $202 \pm 40$ & \cite{PhysRevD.71.123001} \\
+         1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
          \hline    
       \end{tabular}
-      \caption{The OHD dataset from different paper.}
+      \caption{The OHD dataset from different reference.}
       \label{tab:1}
@@
    \begin{equation}
-      \chi_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
+      \chi_{\text{SNe}}^2=\Delta C^{-1} \Delta^{\text{T}},
    \end{equation}
@@
    \begin{equation}
-      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
+      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{\mathcal{C}}+\ln\left(\frac{\mathcal{C}}{2\pi}\right),
    \end{equation}
-   where $B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
-   Apparently, these two functions give the same constraints in $\Omega_{2,0}$ and
-   $\log_{10}(\kappa C_1)$.
+   where $B$ is the sum of $\Delta C^{-1}$ and $\mathcal{C}$ is the sum of $C^{-1}$.
 
@@
    \begin{equation}
-      \chi_{\text{QSO}}^2=\sum_i^{2421}\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
+      \chi_{\text{QSO}}^2=\sum_i\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
       -\ln(2\pi s_i^2)\right],
@@
    sensitive to the cosmic expansion history with well-controlled systematics.
-   We use two BAO datasets from the SDSS (\cite{PhysRevD.103.083533}) and DESI 2024 (\cite{desicollaboration2024desi2024vicosmological}),
+   We use two BAO datasets from the SDSS-IV (\cite{PhysRevD.103.083533}) and 
+   DESI DR2 (\cite{desicollaboration2025desidr2resultsii}),
    which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
@@
 
-   However, the solution of Eq.(\ref{eq:8}) only gives an upper limit of redshift $z_{\max}$
-   (see Appendix), and we just try to use the cross
-   parameter $r_{\text{d}}h$ to give the constraints.
+   However, the solution of Eq.(\ref{eq:8}) only gives an upper 
+   limit of redshift $z_{\max}$ (see Appendix), and the cross 
+   parameter $r_{\text{d}}h$ is used to give the constraints.
 
-   \begin{table}[htbp]
+   \begin{table*}[htbp]
       \centering
-      \begin{tabular}{llll}
+      \begin{tabular}{lcccc}
          \hline\hline
-         $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & 
-         $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
+         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
+         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
          \hline
-         0.15 & & & 4.47$\pm$0.17 \\
-         0.38 & 10.23$\pm$0.17 & 25$\pm$0.76 & \\
-         0.51 & 13.36$\pm$0.21 & 22.33$\pm$0.58 & \\
-         0.7 & 17.86$\pm$0.33 & 19.33$\pm$0.53 & \\
-         0.85 & & & $18.33_{-0.62}^{+0.57}$ \\
-         1.48 & 30.69$\pm$0.8 & 13.26$\pm$0.55 & \\
-         2.33 & 37.6$\pm$1.9 & 8.93$\pm$0.28 & \\
-         2.33 & 37.3$\pm$1.7 & 9.08$\pm$0.34 & \\
+         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
+         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
+         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
+         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
+         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
+         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
+         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
+         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
          \hline
       \end{tabular}
-      \caption{The BAO-only dataset from SDSS. The $\sigma$ of asymmetric 
-      uncertainties would be calculated on average.}
+      \caption{The BAO+RSD measurements dataset from SDSS-IV.}
       \label{tab:2}
-   \end{table}
+   \end{table*}
 
-   \begin{table}[htbp]
+   \begin{table*}[htbp]
       \centering
-      \begin{tabular}{llll}
+      \begin{tabular}{lcccc}
          \hline\hline
-         $z_{\text{eff}}$ & $D_{\text{M}}/r_{\text{d}}$ & 
-         $D_{\text{H}}/r_{\text{d}}$ & $D_{\text{V}}/r_{\text{d}}$ \\
+         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
+         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
          \hline
-         0.295 & & & 7.93$\pm$0.15 \\
-         0.51 & 13.62$\pm$0.25 & 20.98$\pm$0.61 & \\
-         0.706 & 16.85$\pm$0.32 & 20.08$\pm$0.6 & \\
-         0.93 & 21.71$\pm$0.28 & 17.88$\pm$0.35 & \\
-         1.317 & 27.79$\pm$0.69 & 13.82$\pm$0.42 & \\
-         1.491 & & & 26.07$\pm$0.67 \\
-         2.33 & 39.71$\pm$0.94 & 8.52$\pm$0.17 & \\
+         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
+         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
+         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
+         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
+         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
+         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
+         Lya & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
+         \hline
+         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
+         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
          \hline
       \end{tabular}
-      \caption{The BAO dataset from DESI 2024.}
+      \caption{The BAO dataset from DESI DR2.}
       \label{tab:3}
-   \end{table}
+   \end{table*}
 
@@
 
-   For the BAO dataset, we use $h \simeq 0.7$ as the default value to give constraints.
+   For the dataset which cannot give a constraint to $H_0$, 
+   we use $h \simeq 0.7$ as the default value to calculate the 
+   dark matter particle mass $M_x$
 
@@
    limits of the parameters. The  constraint results are shown in 
-   Figure \ref{fig:1}-\ref{fig:6} and summarized in Table \ref{tab:5}.
+   Figure \ref{fig:1}-\ref{fig:5} and summarized in Table \ref{tab:5}.
 
@@
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_1.pdf}
+         \includegraphics[width=0.22\textwidth]{compare_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_2.pdf}
+         \includegraphics[width=0.22\textwidth]{compare_2.pdf}
       }
-      \caption{The constraint result from the supernovae
-      Ia data.}
+      \caption{The constraint result from the supernovae Ia data
+      compared with the SNe Ia+QSO data.}
    \end{figure}
+
+   We could find that the combined result of SNe Ia and QSO is quite
+   similar to SNe Ia result, what may refer that the QSO cannot
+   give an effective constraint. It may be due to the data quality
+   at the high redshift, while the effective redshift of QSO as tracers in BAO
+   is about 1.5, respectively, within the SNe Ia range.
 
@@
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_qso_1.pdf}
+         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_qso_2.pdf}
+         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
       }
-      \caption{The constraint result from the SNe Ia + QSO data.}
+      \caption{The constraint result from the OHD + SNe Ia data.}
    \end{figure}
-
-   We could find that the combined result of SNe Ia and QSO is most
-   similar to SNe Ia result, what may refer that the QSO cannot
-   give an effective constraint. It may be due to the data quality
-   at the high redshift, while the effective redshift of QSO as tracers in BAO
-   is about 1.5, within the SNe Ia range.
 
@@
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
-      }
-      \caption{The constraint result from the OHD + SNe Ia data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
          \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
@@
       \caption{The constraint result from the OHD + SNe Ia + BAO data.}
-      \label{fig:6}
+      \label{fig:5}
    \end{figure}
@@
          \hline\hline
-         Model 1 & OHD & SNe Ia & SNe Ia + QSO & BAO &
-          OHD + SNe Ia & OHD + SNe Ia + BAO \\
+         Model 1 & OHD & SNe Ia & SNe Ia + QSO 
+         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
          \hline
-         $\Omega_{2,0}$ & $0.321_{-0.067}^{+0.055}$ & $0.360_{-0.020}^{+0.020}$
-          & $0.359_{-0.020}^{+0.020}$ & $0.301_{-0.013}^{+0.013}$
-          & $0.330_{-0.016}^{+0.016}$ & $0.313_{-0.010}^{+0.010}$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.17$ & $<-2.51$ & $<-2.57$
-          & $<-3.10$ & $<-2.88$ & $<-3.39$ \\
-         $\log_{10}(M_x/$GeV) & $>-9.77$ & $>-9.42$ & $>-9.40$
-          & $>-8.84$ & $>-9.03$ & $>-8.52$ \\
+         $\Omega_{2,0}$ & $0.324_{-0.066}^{+0.056}$ & $0.380_{-0.020}^{+0.020}$
+          & $0.378_{-0.020}^{+0.020}$ & $0.375_{-0.019}^{+0.019}$
+          & $0.298_{-0.007}^{+0.007}$ & $0.308_{-0.007}^{+0.005}$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.08$ & $<-2.73$ & $<-2.75$
+         & $<-2.91$ & $<-3.38$  & $<-3.71$ \\
+         $\log_{10}(M_x/$GeV) & $>-9.85$ & $>-9.26$ & $>-9.23$
+         & $>-9.13$ & $>-8.56$ & $>-8.26$ \\
          \hline
@@
    \end{table*}
+
+   \begin{figure}[htbp]
+      \centering
+      \includegraphics[width=0.45\textwidth]{pdf_1.pdf}
+      \caption{The probability density of $\Omega_{2,0}$ from different
+      datasets.}
+      \label{fig:6}
+   \end{figure}
 
@@
       \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_2.pdf}
+      }
+      \caption{The constraint result from the OHD + SNe Ia data.}
+   \end{figure}
+
+   \begin{figure}[htbp]
+      \centering
+      \subfigure{
          \includegraphics[width=0.22\textwidth]{bao_widm_1.pdf}
@@
       \caption{The constraint result from the BAO data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_2.pdf}
-      }
-      \caption{The constraint result from the OHD + SNe Ia data.}
    \end{figure}
@@
          \hline\hline
-         Model 2 & OHD & SNe Ia & SNe Ia + QSO & BAO &
-          OHD + SNe Ia & OHD + SNe Ia + BAO \\
+         Model 2 & OHD & SNe Ia & SNe Ia + QSO 
+         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
          \hline
-         $\Omega_{2,0}$ & $0.295_{-0.077}^{+0.077}$ & $0.216_{-0.078}^{+0.096}$
-          & $0.208_{-0.087}^{+0.12}$ & $0.296_{-0.014}^{+0.014}$
-          & $0.202_{-0.049}^{+0.060}$ & $0.291_{-0.013}^{+0.013}$ \\
-         $n$ & $1.4_{-2.8}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
-          & $-0.85_{-0.49}^{+0.42}$ & $-0.40_{-0.29}^{+0.29}$
-          & $-0.83_{-0.27}^{+0.24}$ & $-0.41_{-0.13}^{+0.13}$ \\
-         $w_{\text{IDM}}$ & $-1.5_{-0.9}^{+0.5}$ & $-0.73_{-0.15}^{+0.10}$
-          & $-0.72_{-0.16}^{+0.14}$ & $-0.87_{-0.10}^{+0.10}$
-          & $-0.72_{-0.09}^{+0.09}$ & $-0.86_{-0.04}^{+0.04}$ \\
+         $\Omega_{2,0}$ & $0.299_{-0.074}^{+0.074}$ & $0.216_{-0.078}^{+0.096}$
+          & $0.208_{-0.087}^{+0.12}$ & $0.202_{-0.049}^{+0.060}$ 
+          & $0.296_{-0.014}^{+0.014}$ & $0.291_{-0.013}^{+0.013}$ \\
+         $n$ & $1.5_{-2.9}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
+          & $-0.85_{-0.49}^{+0.42}$ & $-0.83_{-0.27}^{+0.24}$
+          & $-0.40_{-0.29}^{+0.29}$ & $-0.41_{-0.13}^{+0.13}$ \\
+         $w_{\text{IDM}}$ & $-1.5_{-0.5}^{+1.0}$ & $-0.73_{-0.10}^{+0.15}$
+          & $-0.72_{-0.14}^{+0.16}$ & $-0.72_{-0.08}^{+0.09}$
+          & $-0.87_{-0.10}^{+0.10}$ & $-0.86_{-0.04}^{+0.04}$ \\
          \hline

### 2025-04-14 BAO/result.py

@@ -16,15 +16,15 @@ log_kC1 = -5.0
 rdh = 100
 
 # Read data from csv file
-file_path = "./BAO/BAO.csv"
-pandata = np.loadtxt(file_path, delimiter=',', skiprows=1, usecols=(3, 4, 5, 6, 7, 8, 9))
-z_eff = pandata[:, 0]
-D_M_obs = pandata[:, 1]
-D_M_err = pandata[:, 2]
-D_H_obs = pandata[:, 3]
-D_H_err = pandata[:, 4]
-D_V_obs = pandata[:, 5]
-D_V_err = pandata[:, 6]
+data1 = np.loadtxt('./BAO/sdss.dat', skiprows=1)
+data2 = np.loadtxt('./BAO/desi.dat', skiprows=1)
+z_eff = np.concatenate((data1[:, 0], data2[:, 0]))
+D_V_obs = np.concatenate((data1[:, 1], data2[:, 1]))
+D_V_err = np.concatenate((data1[:, 2], data2[:, 2]))
+D_M_obs = np.concatenate((data1[:, 3], data2[:, 3]))
+D_M_err = np.concatenate((data1[:, 4], data2[:, 4]))
+D_H_obs = np.concatenate((data1[:, 5], data2[:, 5]))
+D_H_err = np.concatenate((data1[:, 6], data2[:, 6]))
 
 # Reduce the number of equation solutions
 class BAO:

### 2025-04-14 OHD/result.py

@@ -15,8 +15,8 @@ O20 = 0.3
 log_kC1 = -5.0
     
 # Read data from csv file
-file_path = "./OHD/OHD.csv"
-pandata = np.loadtxt(file_path, delimiter=',', skiprows=1, usecols=(0, 1, 2))
+file_path = "./OHD/OHD.dat"
+pandata = np.loadtxt(file_path, skiprows=1)
 z_hz = pandata[:, 0]
 H_z = pandata[:, 1]
 err_H = pandata[:, 2]

### 2025-04-14 SNe/#result1.py

@@ -44,10 +44,7 @@ def chi_square(log_kC1, O20, H0):
     dl = np.array(dl_values)
     muth = 5 * np.log10(dl) + 25
     delta_mu = muth - mu
-    A = np.dot(delta_mu, np.dot(cov_matrix_inv, delta_mu))
-    B = np.sum(np.dot(cov_matrix_inv, delta_mu))
-    C = np.sum(cov_matrix_inv)
-    chi2 = A - B**2/C + np.log(C/(2*np.pi))
+    chi2 = delta_mu @ cov_matrix_inv @ delta_mu.T
     return chi2
 
 def lnlike(paras):

### 2025-04-14 multimethods/methods3.py

@@ -47,10 +47,8 @@ def lnprob(paras):
     return lp + lnlike(paras)
 
 def main():
-    nll = lambda *args: -lnlike(*args)
     initial = np.array([0.3, -5, 70, 100]) # expected best values
-    soln = scipy.optimize.minimize(nll, initial)
-    pos = soln.x + 1e-4 * np.random.randn(50, 4)
+    pos = initial + 1e-4 * np.random.randn(50, 4)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:

### 2025-04-16 article/article.tex
use the times roman format for some figures

@@
          QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
-         Lya & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
+         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
          \hline
@@
       }
-      \caption{The constraint result from the OHD + SNe Ia data.}
+      \caption{The constraint result from the SNe Ia + OHD data.}
    \end{figure}
@@
       }
-      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
+      \caption{The constraint result from the BAO + SNe Ia + OHD data.}
       \label{fig:5}
@@
          Model 1 & OHD & SNe Ia & SNe Ia + QSO 
-         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
+         & SNe Ia + OHD & BAO & BAO + SNe Ia + OHD \\
          \hline
@@
    \end{figure}
+
+   Fig \ref{fig:6} shows the difference between classical dataset ($H(z)$, SNe Ia)
+   and newly released BAO dataset. The BAO dataset gives a strict constraint to
+   $\Omega_{2,0} \simeq 0.3$, lower than the SNe Ia dataset about $3\sigma$, which
+   gives a higher value $\Omega_{2,0} \simeq 0.4$. The constraint result to Pantheon+
+   SNe Ia dataset in $\Lambda$CDM model is $\Omega_M \simeq 0.33$ (\cite{Borghi_2022}),
 
@@
    \end{equation}
-   It can be theoretically solved and the solution is like
+   It can be theoretically solved and the solution has a form like
    \begin{equation}

### 2025-05-14 article/article.tex
change the figure shows

@@
 
-   \title{Constraint result to the self-interacting dark matter model without dark energy
-   in cosmology}
+   \title{Constraint result to the self-interacting dark matter particle mass from the
+   observational data}
 
@@
 
-   In this paper, we use the newly revised data from $H(z)$, supernovae Ia, 
-   quasars and baryon acoustic oscillation by using the Markov chain Monte
+   In this paper, we use the newly revised data from $H(z)$, supernovae Ia 
+   and baryon acoustic oscillation by using the Markov chain Monte
    Carlo (MCMC) method. The result gives that the lower limit of the interacting
-   dark matter particle mass is about 1 eV.
+   dark matter particle mass is about 10 eV.
 
@@
    Borghi_2022, Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
-   (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
-   the BAO data from SDSS-IV (\cite{PhysRevD.103.083533}) and DESI DR2 
+   (\cite{Scolnic_2022}), the BAO data from SDSS-IV (\cite{PhysRevD.103.083533}) and DESI DR2 
    (\cite{desicollaboration2025desidr2resultsii}).
@@
 
-   \begin{table}[htbp]
+   \begin{table}
       \centering
@@
 
-\subsection{Quasar}
-
-   The quasar gives a higher redshift than SNe Ia.
-   We use the QSO dataset from \cite{Lusso_2020}, which gives
-   2421 samples with the ultraviolet (UV) and X-ray luminosity.
-   The redshift is up to $\simeq7.5$.
-
-   The $L_X-L_{UV}$ relation of quasar is usually written as
-   \begin{equation}
-      \log_{10}(L_X)=\beta+\gamma\log_{10}(L_{UV}),
-   \end{equation}
-   which gives that
-   \begin{eqnarray}
-      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
-                    \\ &+2(\gamma-1)\log_{10}(d_L),
-   \end{eqnarray}
-   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
-   Here we use the parameters defined in \cite{li2024redshiftevolutionxrayuv}, which
-   gives\begin{equation}
-      \beta=\beta_0+\beta_1(1+z),\gamma=\gamma_0+\gamma_1(1+z),
-   \end{equation}
-   so the $\chi^2$ function for the QSO data can be defined as
-   \begin{equation}
-      \chi_{\text{QSO}}^2=\sum_i\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
-      -\ln(2\pi s_i^2)\right],
-   \end{equation}
-   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
-   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
-   $\delta_i$ reprensent the instrinsic dispersion.
-
 \subsection{Baryon acoustic oscillation}
@@
 
-   \begin{table*}[htbp]
+   \begin{table*}
       \centering
@@
          $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
-         \hline
-         $\beta_0$ & 6 & $\mathcal{U}[-15,15]$ \\
-         $\beta_1$ & 1 & $\mathcal{U}[-10,10]$ \\
-         $\gamma_0$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
-         $\gamma_1$ & 0 & $\mathcal{U}[-1.0,1.0]$ \\         
-         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
          \hline
@@
    limits of the parameters. The  constraint results are shown in 
-   Figure \ref{fig:1}-\ref{fig:5} and summarized in Table \ref{tab:5}.
+   Figure \ref{fig:1} and summarized in Table \ref{tab:5}.
 
-   \begin{figure}[htbp]
+   \begin{figure*}
       \centering
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_1.pdf}
+         \includegraphics[width=0.3\textwidth]{sne_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_2.pdf}
-      }
-      \caption{The constraint result from the observational
-      $H(z)$ data.}
-      \label{fig:1}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{compare_1.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_sne_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{compare_2.pdf}
+         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.3\textwidth]{sne_2.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.3\textwidth]{bao_sne_2.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_2.pdf}
       }
       \caption{The constraint result from the supernovae Ia data
-      compared with the SNe Ia+QSO data.}
-   \end{figure}
+      (left), the BAO + SNe Ia data (middle) and the BAO + SNe Ia + OHD data (right).}
+      \label{fig:1}
+   \end{figure*}
 
-   We could find that the combined result of SNe Ia and QSO is quite
-   similar to SNe Ia result, what may refer that the QSO cannot
-   give an effective constraint. It may be due to the data quality
-   at the high redshift, while the effective redshift of QSO as tracers in BAO
-   is about 1.5, respectively, within the SNe Ia range.
-
-   \begin{figure}[htbp]
+   \begin{table*}
       \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
-      }
-      \caption{The constraint result from the SNe Ia + OHD data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{bao_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{bao_2.pdf}
-      }
-      \caption{The constraint result from the BAO data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
-      }
-      \caption{The constraint result from the BAO + SNe Ia + OHD data.}
-      \label{fig:5}
-   \end{figure}
-
-   \begin{table*}[htbp]
-      \centering
-      \begin{tabular}{lcccccc}
+      \begin{tabular}{lccc}
          \hline\hline
-         Model 1 & OHD & SNe Ia & SNe Ia + QSO 
-         & SNe Ia + OHD & BAO & BAO + SNe Ia + OHD \\
+         Model 1 & SNe Ia & BAO + SNe Ia & BAO + SNe Ia + OHD \\
          \hline
-         $\Omega_{2,0}$ & $0.324_{-0.066}^{+0.056}$ & $0.380_{-0.020}^{+0.020}$
-          & $0.378_{-0.020}^{+0.020}$ & $0.375_{-0.019}^{+0.019}$
-          & $0.298_{-0.007}^{+0.007}$ & $0.308_{-0.007}^{+0.005}$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.08$ & $<-2.73$ & $<-2.75$
-         & $<-2.91$ & $<-3.38$  & $<-3.71$ \\
-         $\log_{10}(M_x/$GeV) & $>-9.85$ & $>-9.26$ & $>-9.23$
-         & $>-9.13$ & $>-8.56$ & $>-8.26$ \\
+         $\Omega_{2,0}$ & $0.380_{-0.020}^{+0.020}$
+          & $0.3078_{-0.0067}^{+0.0053}$ & $0.3079_{-0.0067}^{+0.0051}$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.73$ 
+         & $<-3.70$  & $<-3.71$ \\
+         $\log_{10}(M_x/$GeV) & $>-9.26$
+         & $>-8.24$ & $>-8.26$ \\
          \hline
@@
 
-   \begin{figure}[htbp]
-      \centering
-      \includegraphics[width=0.45\textwidth]{pdf_1.pdf}
-      \caption{The probability density of $\Omega_{2,0}$ from different
-      datasets.}
-      \label{fig:6}
-   \end{figure}
+   The SNe Ia dataset gives a value $\Omega_{2,0} \simeq 0.38$. The constraint result to Pantheon+
+   SNe Ia dataset in the flat $\Lambda$CDM model is $\Omega_{m} \simeq 0.33$ (\cite{Borghi_2022}),
 
-   Fig \ref{fig:6} shows the difference between classical dataset ($H(z)$, SNe Ia)
-   and newly released BAO dataset. The BAO dataset gives a strict constraint to
-   $\Omega_{2,0} \simeq 0.3$, lower than the SNe Ia dataset about $3\sigma$, which
-   gives a higher value $\Omega_{2,0} \simeq 0.4$. The constraint result to Pantheon+
-   SNe Ia dataset in $\Lambda$CDM model is $\Omega_M \simeq 0.33$ (\cite{Borghi_2022}),
+   We use the most combined dataset of OHD + SNe Ia + BAO to give a stringent lower limit
+   of $\log_{10}(M_x/$GeV) $\simeq -8.26$ at $2\sigma$ level, similar to the 
+   sub-MeV mass of the interacting dark matter.
 
@@
 
-   \begin{figure}[htbp]
+   \begin{figure*}
       \centering
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_widm_1.pdf}
+         \includegraphics[width=0.3\textwidth]{sne_widm_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_widm_2.pdf}
-      }
-      \caption{The constraint result from the observational
-      $H(z)$ data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_widm_1.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_sne_widm_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_widm_2.pdf}
-      }
-      \caption{The constraint result from the supernovae
-      Ia data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_qso_widm_1.pdf}
+         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_widm_1.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{sne_qso_widm_2.pdf}
-      }
-      \caption{The constraint result from the SNe Ia + QSO data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_1.pdf}
+         \includegraphics[width=0.3\textwidth]{sne_widm_2.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_2.pdf}
-      }
-      \caption{The constraint result from the OHD + SNe Ia data.}
-   \end{figure}
-
-   \begin{figure}[htbp]
-      \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{bao_widm_1.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_sne_widm_2.pdf}
       }
       \subfigure{
-         \includegraphics[width=0.22\textwidth]{bao_widm_2.pdf}
+         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_widm_2.pdf}
       }
-      \caption{The constraint result from the BAO data.}
-   \end{figure}
+      \caption{The constraint result from the supernovae Ia data
+      (left), the BAO + SNe Ia data (middle) and the BAO + SNe Ia + OHD data (right).}
+   \end{figure*}
 
-   \begin{figure}[htbp]
+   \begin{table*}
       \centering
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_widm_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_widm_2.pdf}
-      }
-      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
-   \end{figure}
-
-   The results from three dataset are different
-
-   \begin{table*}[htbp]
-      \centering
-      \begin{tabular}{lcccccc}
+      \begin{tabular}{lccc}
          \hline\hline
-         Model 2 & OHD & SNe Ia & SNe Ia + QSO 
-         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
+         Model 2 & SNe Ia & SNe Ia + BAO
+          & OHD + SNe Ia + BAO \\
          \hline
-         $\Omega_{2,0}$ & $0.299_{-0.074}^{+0.074}$ & $0.216_{-0.078}^{+0.096}$
-          & $0.208_{-0.087}^{+0.12}$ & $0.202_{-0.049}^{+0.060}$ 
-          & $0.296_{-0.014}^{+0.014}$ & $0.291_{-0.013}^{+0.013}$ \\
-         $n$ & $1.5_{-2.9}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
-          & $-0.85_{-0.49}^{+0.42}$ & $-0.83_{-0.27}^{+0.24}$
-          & $-0.40_{-0.29}^{+0.29}$ & $-0.41_{-0.13}^{+0.13}$ \\
-         $w_{\text{IDM}}$ & $-1.5_{-0.5}^{+1.0}$ & $-0.73_{-0.10}^{+0.15}$
-          & $-0.72_{-0.14}^{+0.16}$ & $-0.72_{-0.08}^{+0.09}$
-          & $-0.87_{-0.10}^{+0.10}$ & $-0.86_{-0.04}^{+0.04}$ \\
+         $\Omega_{2,0}$ & $0.215_{-0.073}^{+0.10}$
+          & $0.2940_{-0.0076}^{+0.0076}$ & $0.2945_{-0.0075}^{+0.0075}$ \\
+         $n$ & $-0.82_{-0.45}^{+0.29}$
+          & $-0.43_{-0.10}^{+0.10}$ & $-0.42_{-0.11}^{+0.11}$ \\
+         $w_{\text{IDM}}$ & $-0.73_{-0.10}^{+0.15}$
+          & $-0.86_{-0.03}^{+0.03}$ & $-0.86_{-0.04}^{+0.04}$ \\
          \hline
@@
    and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
-   \begin{figure}[htbp]
+   \begin{figure}
       \centering

### 2025-05-14 SNe/#result1.py

@@ -1,108 +1,0 @@
-import numpy as np
-from getdist import plots, MCSamples
-import emcee
-import corner
-import scipy
-import multiprocessing as mp
-
-import sys
-import os
-sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
-from solution import solution
-from solution import const_c
-from cross_section import cross_section
-
-H0 = 70.0
-O20 = 0.3
-log_kC1 = -5.0
-
-# pantheon+
-file_path = "./SNe/Pantheon+ data/Pantheon+SH0ES.dat"
-pandata = np.loadtxt(file_path, skiprows=1, usecols=(2, 10))
-z_hd = pandata[:, 0]
-mu = pandata[:, 1]
-
-file_path_cov = './SNe/Pantheon+ data/Pantheon+SH0ES_cov.dat'
-cov = np.loadtxt(file_path_cov, skiprows=1)
-cov_matrix = cov.reshape((1701, 1701))
-cov_matrix_inv = np.linalg.inv(cov_matrix)
-
-def chi_square(log_kC1, O20, H0):
-    t0 = 1 / H0
-    t_values = solution(log_kC1, O20, H0).t
-    z_values = solution(log_kC1, O20, H0).y[0, :]
-    dl_values = []
-
-    for z_hz_value in z_hd:
-        idx = np.searchsorted(z_values, z_hz_value)
-        if idx >= len(z_values):  
-            idx = len(z_values) - 1
-        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
-        dl_value = const_c * (1 + z_hz_value) * (t0 - t_values[idx] + int_value)
-        dl_values.append(dl_value)
-
-    dl = np.array(dl_values)
-    muth = 5 * np.log10(dl) + 25
-    delta_mu = muth - mu
-    chi2 = delta_mu @ cov_matrix_inv @ delta_mu.T
-    return chi2
-
-def lnlike(paras):
-    O20, log_kC1, H0 = paras
-    chi2 = chi_square(log_kC1, O20, H0)
-    return -0.5 * chi2
-
-def lnprior(paras):
-    O20, log_kC1, H0 = paras
-    if 0 < O20 < 0.5 and -10 < log_kC1 < 0 and 60 < H0 < 80:
-        return 0.0
-    return -np.inf
-
-def lnprob(paras):
-    lp = lnprior(paras)
-    if not np.isfinite(lp):
-        return -np.inf
[…]

### 2025-05-14 SNe/DESY5 data/SN_only_cosmosis_likelihood.py

@@ -1,0 +1,196 @@
+"""
+The likelihood module for the DES-SN5YR sample
+This likelihood analytically marginalize over M (SN absolute brightness).
+M is fully degenerate with H0. Do not try to measure H0 with SN data
+"""
+
+from cosmosis.gaussian_likelihood import GaussianLikelihood
+from cosmosis.datablock import names
+import os
+import numpy as np
+import pandas as pd 
+
+# Default is to use DES-SN5YR
+# default_data_file = os.path.join(os.path.split(__file__)[0], "DESONLY/hubble_diagram.txt")
+# default_covmat_file = os.path.join(os.path.split(__file__)[0], "DESONLY/covsys_000.txt")
+
+default_data_file = os.path.join(os.path.split(__file__)[0], "4_DISTANCES_COVMAT/DES-SN5YR_HD.csv")
+default_covmat_file = os.path.join(os.path.split(__file__)[0], "4_DISTANCES_COVMAT/STAT+SYS.txt.gz")
+
+def cov_log_likelihood(mu_model, mu, inv_cov):
+    """ 
+    Computes modified likelihood computation to marginalize offset M 
+    from https://arxiv.org/abs/astro-ph/0104009v1, see Equation A9-12 
+    """
+    delta = np.array([mu_model - mu])
+    deltaT = np.transpose(delta)
+    chit2 = np.sum(delta @ inv_cov @ deltaT)
+    B = np.sum(delta @ inv_cov)
+    C = np.sum(inv_cov)
+    chi2 = chit2 - (B**2 / C) + np.log(C / (2 * np.pi))
+    return -0.5*chi2
+
+class DESY5SNLikelihood(GaussianLikelihood):
+    x_section = names.distances
+    x_name = "z"
+    y_section = names.distances
+    y_name = "D_A"
+    like_name = "desy5sn"
+
+    def build_data(self):
+        """
+        Run once at the start to load in the data vectors.
+
+        Returns x, y where x is the independent variable (redshift in this case)
+        and y is the Gaussian-distribured measured variable (magnitude in this case).
+
+        """
+        filename = self.options.get_string("data_file", default=default_data_file)
+        print("Loading DES Y5 SN data from {}".format(filename))
+        data = pd.read_csv(filename, delim_whitespace=True, comment='#')
+        self.origlen = len(data)
+        # The only columns that we actually need here are the redshift,
+        # distance modulus and distance modulus error
+
[…]

### 2025-05-14 SNe/result1.py

@@ -1,0 +1,88 @@
+import numpy as np
+from getdist import plots, MCSamples
+import emcee
+import corner
+import scipy
+import multiprocessing as mp
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+from solution import solution
+from solution import const_c
+from cross_section import cross_section
+
+H0 = 70.0
+O20 = 0.3
+log_kC1 = -5.0
+
+# desy5
+data = np.loadtxt('./SNe/DESY5 data/DES-SN5YR_HD.csv', delimiter=',', skiprows=1, usecols=(2,4,5,6))
+z_cmb = data[:,0]
+z_hel = data[:,1]
+mu = data[:,2]
+mu_err = data[:,3]
+
+cov_list = np.loadtxt('./SNe/DESY5 data/covsys_000.txt', skiprows=1)
+cov_matrix = cov_list.reshape((1829, 1829))
+mu_err_martix = np.diag(mu_err**2)
+cov_matrix += mu_err_martix
+cov_inv = np.linalg.inv(cov_matrix)
+
+def chi_square(log_kC1, O20, H0):
+    t0 = 1 / H0
+    t_values = solution(log_kC1, O20, H0).t
+    z_values = solution(log_kC1, O20, H0).y[0, :]
+    dl_values = []
+
+    for z_value in z_cmb:
+        idx = np.searchsorted(z_values, z_value)
+        if idx >= len(z_values):  
+            idx = len(z_values) - 1
+        int_value = -np.trapezoid(z_values[:idx], t_values[:idx])
+        dl_value = const_c * (t0 - t_values[idx] + int_value)
+        dl_values.append(dl_value)
+
+    dl = np.array(dl_values * (1 + z_hel))
+    muth = 5 * np.log10(dl) + 25
+    delta = muth - mu
+    deltaT = np.transpose(delta)
+    chit2 = np.sum(delta @ cov_inv @ deltaT)
+    B = np.sum(delta @ cov_inv)
+    C = np.sum(cov_inv)
+    chi2 = chit2 - (B**2 / C) + np.log(C / (2 * np.pi))
+    return chi2
+
+def lnlike(paras):
+    O20, log_kC1, H0 = paras
+    chi2 = chi_square(log_kC1, O20, H0)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    O20, log_kC1, H0 = paras
[…]

### 2025-05-14 multimethods/methods2.py

@@ -12,10 +12,10 @@ H0 = 70.0
 O20 = 0.3
 log_kC1 = -5.0
 
-### OHD
-import OHD.result 
-def chi_square_OHD(log_kC1, O20, H0):
-    return OHD.result.chi_square(log_kC1, O20, H0)
+### BAO
+import BAO.result
+def chi_square_BAO(log_kC1, O20, H0, rdh):
+    return BAO.result.chi_square(log_kC1, O20, H0, rdh)
 
 ### SNe Ia
 import SNe.result2
@@ -25,13 +25,13 @@ def chi_square_SNe(log_kC1, O20, H0):
 ### MCMC
 
 def lnlike(paras):
-    O20, log_kC1, H0 = paras
-    chi2 = chi_square_OHD(log_kC1, O20, H0) + chi_square_SNe(log_kC1, O20, H0)
+    O20, log_kC1, H0, rdh = paras
+    chi2 = chi_square_BAO(log_kC1, O20, H0, rdh) + chi_square_SNe(log_kC1, O20, H0)
     return -0.5 * chi2
 
 def lnprior(paras):
-    O20, log_kC1, H0 = paras
-    if 0 < O20 < 0.5 and -10 < log_kC1 < 0 and 60 < H0 < 80 :
+    O20, log_kC1, H0, rdh = paras
+    if 0 < O20 < 0.5 and -10 < log_kC1 < 0 and 60 < H0 < 80 and 50 < rdh < 150:
         return 0.0
     return -np.inf
 
@@ -42,10 +42,8 @@ def lnprob(paras):
     return lp + lnlike(paras)
 
 def main():
-    nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.3, -5, 70]) # expected best values
-    soln = scipy.optimize.minimize(nll, initial)
-    pos = soln.x + 1e-4 * np.random.randn(50, 3)
+    initial = np.array([0.3, -5, 70, 100]) # expected best values
+    pos = initial + 1e-4 * np.random.randn(50, 4)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:

### 2025-05-14 multimethods/methods2_desy.py

@@ -1,0 +1,57 @@
+import numpy as np
+import emcee
+import scipy
+import multiprocessing as mp
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '..'))
+
+# Prior values
+H0 = 70.0
+O20 = 0.3
+log_kC1 = -5.0
+
+### BAO
+import BAO.result
+def chi_square_BAO(log_kC1, O20, H0, rdh):
+    return BAO.result.chi_square(log_kC1, O20, H0, rdh)
+
+### SNe Ia
+import SNe.result1
+def chi_square_SNe(log_kC1, O20, H0):
+    return SNe.result1.chi_square(log_kC1, O20, H0)
+
+### MCMC
+
+def lnlike(paras):
+    O20, log_kC1, H0, rdh = paras
+    chi2 = chi_square_BAO(log_kC1, O20, H0, rdh) + chi_square_SNe(log_kC1, O20, H0)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    O20, log_kC1, H0, rdh = paras
+    if 0 < O20 < 0.5 and -10 < log_kC1 < 0 and 60 < H0 < 80 and 50 < rdh < 150:
+        return 0.0
+    return -np.inf
+
+def lnprob(paras):
+    lp = lnprior(paras)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(paras)
+
+def main():
+    initial = np.array([0.3, -5, 70, 100]) # expected best values
+    pos = initial + 1e-4 * np.random.randn(50, 4)
+    nwalkers, ndim = pos.shape
+
+    with mp.Pool() as pool:
+        sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
+        sampler.run_mcmc(pos, 5000, progress = True)
+    flat_samples = sampler.get_chain(discard=500, flat=True)
+    np.savetxt('./multimethods/output2_desy.dat', flat_samples)
+
+if __name__ == '__main__':
+    mp.freeze_support()
+    main()

### 2025-05-14 wIDM/BAO.py

@@ -38,27 +38,5 @@ def main():
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
         sampler.run_mcmc(pos, 5000, progress = True)
 
-    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
-    names = ['O20', 'n', 'H0', 'rdh']
-    flat_samples = sampler.get_chain(discard=200, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels, ranges={'H0':(60, 80)})
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['r'], title_limit=1)
-    g.export('./article/pictures/bao_widm.pdf')
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2])
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_2, 'O20', 'n', filled=True, colors=['r'])
-    g.export('./article/pictures/bao_widm_1.pdf')
-
-    wIDM = -1 - flat_samples[:,1]/3
-    combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
-    labels_ = [r'\Omega_{2,0}', 'w_{IDM}']
-    names_ = ['O20', 'wIDM']
-    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_)
-    g = plots.get_single_plotter(ratio=1)    
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_, 'O20', 'wIDM', filled=True, colors=['r'])
-    g.export('./article/pictures/bao_widm_2.pdf')
+    flat_samples = sampler.get_chain(discard=500, flat=True)
+    np.savetxt('./wIDM/output/bao.dat', flat_samples)

### 2025-05-14 wIDM/SNe.py

@@ -36,32 +36,10 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
+        sampler.run_mcmc(pos, 5000, progress = True)
 
-    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
-    names = ['O20', 'n', 'H0']
-    flat_samples = sampler.get_chain(discard=100, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['g'], title_limit=1)
-    g.export('./article/pictures/sne_widm.pdf')
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2])
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_2, 'O20', 'n', filled=True, colors=['g'])
-    g.export('./article/pictures/sne_widm_1.pdf')
-
-    wIDM = -1 - flat_samples[:,1]/3
-    combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
-    labels_ = [r'\Omega_{2,0}', 'w_{IDM}']
-    names_ = ['O20', 'wIDM']
-    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_)
-    g = plots.get_single_plotter(ratio=1)    
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_, 'O20', 'wIDM', filled=True, colors=['g'])
-    g.export('./article/pictures/sne_widm_2.pdf')
+    flat_samples = sampler.get_chain(discard=500, flat=True)
+    np.savetxt('./wIDM/output/sne.dat', flat_samples)  
 
 if __name__ == "__main__":
     mp.freeze_support()

### 2025-05-14 wIDM/caculus.py

@@ -17,8 +17,8 @@ def H_ad(z, O20, n, H0):
     return 1/H(z, O20, n, H0)
 
 ### OHD
-file_path = "./OHD/OHD.csv"
-pandata = np.loadtxt(file_path, delimiter=',', skiprows=1, usecols=(0, 1, 2))
+file_path = "./OHD/OHD.dat"
+pandata = np.loadtxt(file_path, skiprows=1)
 z_hz = pandata[:, 0]
 H_z = pandata[:, 1]
 err_H = pandata[:, 2]
@@ -50,7 +50,10 @@ def chi_square_SNe(O20, n, H0):
     dl = np.array(dl)
     muth = 5 * np.log10(dl) + 25
     delta_mu = muth - mu
-    chi2 = np.dot(delta_mu, np.dot(cov_matrix_inv, delta_mu))
+    A = delta_mu @ cov_matrix_inv @ delta_mu.T
+    B = np.sum(delta_mu @ cov_matrix_inv)
+    C = np.sum(cov_matrix_inv)
+    chi2 = A - B**2 / C + np.log(C / (2 * np.pi))
     return chi2
 
 ### QSO
@@ -85,15 +88,15 @@ def chi_square_QSO(O20, n, H0, gamma0, gamma1, beta0, beta1, delta):
     return chi2 + extra
 
 ### BAO
-file_path_BAO = "./BAO/BAO.csv"
-pandata_BAO = np.loadtxt(file_path_BAO, delimiter=',', skiprows=1, usecols=(3, 4, 5, 6, 7, 8, 9))
-z_eff = pandata_BAO[:, 0]
-D_M_obs = pandata_BAO[:, 1]
-D_M_err = pandata_BAO[:, 2]
-D_H_obs = pandata_BAO[:, 3]
-D_H_err = pandata_BAO[:, 4]
-D_V_obs = pandata_BAO[:, 5]
-D_V_err = pandata_BAO[:, 6]
+data1 = np.loadtxt('./BAO/sdss.dat', skiprows=1)
+data2 = np.loadtxt('./BAO/desi.dat', skiprows=1)
+z_eff = np.concatenate((data1[:, 0], data2[:, 0]))
+D_V_obs = np.concatenate((data1[:, 1], data2[:, 1]))
+D_V_err = np.concatenate((data1[:, 2], data2[:, 2]))
+D_M_obs = np.concatenate((data1[:, 3], data2[:, 3]))
[…]

### 2025-05-14 wIDM/methods2.py

@@ -8,17 +8,17 @@ from getdist import plots, MCSamples
 import sys
 import os
 sys.path.append(os.path.join(os.path.dirname(__file__), '.'))
-from caculus import chi_square_OHD
+from caculus import chi_square_BAO
 from caculus import chi_square_SNe
 
 def lnlike(paras):
-    O20, n, H0 = paras
-    chi2 = chi_square_OHD(O20, n, H0) + chi_square_SNe(O20, n, H0)
+    O20, n, H0, rdh = paras
+    chi2 = chi_square_BAO(O20, n, H0, rdh) + chi_square_SNe(O20, n, H0)
     return -0.5 * chi2
 
 def lnprior(paras):
-    O20, n, H0 = paras
-    if 0 < O20 < 1 and -10 < n < 10 and 50 < H0 < 100:
+    O20, n, H0, rdh = paras
+    if 0 < O20 < 1 and -10 < n < 10 and 50 < H0 < 100 and 50 < rdh < 150:
         return 0.0
     return -np.inf
 
@@ -30,36 +30,14 @@ def lnprob(paras):
 
 def main():
     nll = lambda *args: -lnlike(*args)
-    initial = np.array([0.3, 0, 70]) # expected best values
+    initial = np.array([0.3, 0, 70, 100]) # expected best values
     soln = scipy.optimize.minimize(nll, initial)
-    pos = soln.x + 1e-4 * np.random.randn(50, 3)
+    pos = soln.x + 1e-4 * np.random.randn(50, 4)
     nwalkers, ndim = pos.shape
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
+        sampler.run_mcmc(pos, 5000, progress = True)
 
-    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]']
-    names = ['O20', 'n', 'H0']
-    flat_samples = sampler.get_chain(discard=100, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['c'], title_limit=1)
-    g.export('./article/pictures/ohd_sne_widm.pdf')
[…]

### 2025-05-14 wIDM/methods3.py

@@ -38,29 +38,7 @@ def main():
 
     with mp.Pool() as pool:
         sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
-        sampler.run_mcmc(pos, 2000, progress = True)
+        sampler.run_mcmc(pos, 5000, progress = True)
 
-    labels = [r'\Omega_{2,0}', 'n', 'H_0[km/s/Mpc]', 'r_dh[Mpc]']
-    names = ['O20', 'n', 'H0', 'rdh']
-    flat_samples = sampler.get_chain(discard=100, flat=True)
-    samples = MCSamples(samples=flat_samples, names=names, labels=labels)
-    g = plots.get_subplot_plotter()
-    g.triangle_plot(samples, filled=True, contour_colors=['m'], title_limit=1)
-    g.export('./article/pictures/ohd_sne_bao_widm.pdf')
-    samples_2 = MCSamples(samples=flat_samples[:,0:2], names=names[0:2], labels=labels[0:2])
-    g = plots.get_single_plotter(ratio=1)
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_2, 'O20', 'n', filled=True, colors=['m'])
-    g.export('./article/pictures/ohd_sne_bao_widm_1.pdf')
-
-    wIDM = -1 - flat_samples[:,1]/3
-    combined_samples = np.vstack((flat_samples[:,0], wIDM)).T
-    labels_ = [r'\Omega_{2,0}', 'w_{IDM}']
-    names_ = ['O20', 'wIDM']
-    samples_ = MCSamples(samples=combined_samples, names=names_, labels=labels_)
-    g = plots.get_single_plotter(ratio=1)    
-    g.settings.axes_fontsize = 18
-    g.settings.axes_labelsize = 24
-    g.plot_2d(samples_, 'O20', 'wIDM', filled=True, colors=['m'])
-    g.export('./article/pictures/ohd_sne_bao_widm_2.pdf')
+    flat_samples = sampler.get_chain(discard=500, flat=True)
+    np.savetxt('./wIDM/output/m3.dat', flat_samples)

### 2025-06-02 article/article.tex
add cross-section figure contrast

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:1}
 
@@
    and baryon acoustic oscillation by using the Markov chain Monte
-   Carlo (MCMC) method. The result gives that the lower limit of the interacting
-   dark matter particle mass is about 10 eV.
+   Carlo (MCMC) method. The constraint result gives an upper limit for the 
+   linear ratio between the dark matter annihilation cross section $\langle\sigma v\rangle$
+   and the dark matter particle mass $M_{\chi}$ about $9\times10^{-15} \;\text{cm}^{3}\text{s}^{-1}\text{GeV}^{-1}$.
 
-\section{The basic equations in the IDM model}
+   The paper is arranged as follows: In Sec.\ref{sec:2}, we review the basic equations in the IDM model,
+   in Sec.\ref{sec:3}, we introduce the observational datasets used in this analysis, in Sec.\ref{sec:4}, 
+   we give the constraint results of the IDM model and compare our results with 
+   other relevant dark matter constraints, and finally we conclude in Sec.\ref{sec:5}.
+
+\section{The basic equations in the IDM model}\label{sec:2}
 
@@
       \dot{\rho}+3H\rho+\kappa\rho^2-2\Psi=0,
+      \label{eq:1}
    \end{equation}
@@
    \begin{equation}
-      \kappa=\frac{\langle\sigma u\rangle}{M_x},\label{eq:2}
+      \kappa=\frac{\langle\sigma v\rangle}{M_{\chi}},
+      \label{eq:2}
    \end{equation}
-   where $\sigma$ is the cross-section for annihilation, $u$ is
-   the mean particle velocity, and $M_x$ is the mass of the DM
+   where $\sigma$ is the cross section for annihilation, $v$ is
+   the mean particle velocity, and $M_{\chi}$ is the mass of the DM
    particle.
@@
       P=\frac{\kappa\rho^2-\Psi}{3H}.
+      \label{eq:3}
    \end{equation}
@@
    Refering to Appendix B in \cite{Basilakos_2009}, only one of these two is of interest
-   because it provides a ``$\propto a^{-3}$'' dependence of the scale factor,
+   because it provides a ``$\propto\alpha^{-3}$'' dependence of the scale factor,
    which is \begin{equation}
-      \Psi(a)=aH(a)R(a)=C_1(n+3)a^nH(a)+\kappa C_1^2a^{2m}.
+      \Psi(\alpha)=\alpha H(\alpha)R(\alpha)=C_1(n+3)\alpha^nH(\alpha)+\kappa C_1^2 \alpha^{2m}.
+      \label{eq:4}
    \end{equation}
@@
    \begin{equation}
-      \rho(a)=C_1a^n+\frac{a^{-3}F(a)}{C_2-\int_1^{a}x^{-3}f(x)F(x)\mathrm{d}x},\label{eq:5}
+      \rho(\alpha)=C_1 \alpha^n+\frac{\alpha^{-3}F(\alpha)}{C_2-\int_1^{\alpha}x^{-3}f(x)F(x)\mathrm{d}x},
+      \label{eq:5}
    \end{equation}
-   where $f(a)=-\kappa/[aH(a)],$ and the kernal function $F(a)$ has
+   where $f(\alpha)=-\kappa/[\alpha H(\alpha)],$ and the kernal function $F(\alpha)$ has
    the form \begin{equation}
-      F(a)=\exp\left[-2\kappa C_1\int_1^{a}\frac{x^{n-1}}{H(x)}\mathrm{d}x\right].
+      F(\alpha)=\exp\left[-2\kappa C_1\int_1^{\alpha}\frac{x^{n-1}}{H(x)}\mathrm{d}x\right].
+      \label{eq:6}
    \end{equation}
@@
    \begin{equation}
-      \rho(a)=C_1+a^{-3}\frac{e^{-2\kappa C_1(t-t_0)}}{C_2-\kappa Z(t)},
+      \rho(\alpha)=C_1+\alpha^{-3}\frac{e^{-2\kappa C_1(t-t_0)}}{C_2+\kappa Z(t)},
+      \label{eq:7}
    \end{equation}
-   where $Z(t)=\int_{t_0}^ta^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$ (\cite{Basilakos_2009}).
+   where $Z(t)=\int_{t_0}^t \alpha^{-3}e^{-2\kappa C_1(t'-t_0)}\mathrm{d}t'$ (\cite{Basilakos_2009}).
    Using the usual unit-less $\Omega$-like parameterization, we obtain that
    \begin{equation}
-      \left(\frac{H}{H_0}\right)^2=\Omega_{1,0}+\frac{\Omega_{1,0}\Omega_{2,0}a^{-3}e^{-2\kappa C_1(t-t_0)}}
-      {\Omega_{1,0}+\kappa C_1\Omega_{2,0}Z(t)},\label{eq:8}
+      \left(\frac{H}{H_0}\right)^2=\Omega_{1,0}+\frac{\Omega_{1,0}\Omega_{2,0}\alpha^{-3}e^{-2\kappa C_1(t-t_0)}}
+      {\Omega_{1,0}+\kappa C_1\Omega_{2,0}Z(t)},
+      \label{eq:8}
    \end{equation}
@@
    \begin{equation}
-      M_x=\frac{3.325\times10^{-12}}{\kappa C_1}
-      \frac{\langle\sigma u\rangle}{10^{-23}}h^2(1-\Omega_{2,0})\,\text{GeV},\label{eq:9}
+      M_{\chi}=\frac{3.325\times10^{-12}}{\kappa C_1}
+      \frac{\langle\sigma v\rangle}{10^{-23}}h^2(1-\Omega_{2,0})\,\text{GeV},
+      \label{eq:9}
    \end{equation}
@@
 
-   If $\kappa=0$, the global density evolution can be written as
+   If $n\neq0$, the global density evolution is Eq.(\ref{eq:5}), and the 
+   usual unit-less $\Omega$-like can be written as
    \begin{equation}
-      \rho(a)=\mathcal{D}a^{-3}+C_1a^{n},
+      \left(\frac{H}{H_0}\right)^2 = \Omega_{1,0} \alpha^n + 
+      \frac{\Omega_{1,0} \Omega_{2,0} \alpha^{-3}F(\alpha)}
+      {\Omega_{1,0} + \kappa C_1 \Omega_{2,0} \int_1^\alpha 
+      \frac{F(x)}{x^4 H(x)} \mathrm{d}x},
+      \label{eq:10}
    \end{equation}
-   where $\mathcal{D}=C_2-C_1$. The conditions in which the current 
-   model acts as a quintessence cosmology are given by $\mathcal{D}>0,
-   C_1>0,$ and $w_{\text{IDM}}=-1-n/3$. This solution is mathematically
-   equivalent to that of the gravitational matter creation model of \cite{Lima_2008}.
-   The Hubble flow is now given by
+   where $\Omega_{1,0}$ and $\Omega_{2,0}$ are the same defined as Eq.(\ref{eq:8}), and 
+   $F(\alpha)$ is given by Eq.(\ref{eq:6}).
+
+   Considering the limit of $\kappa \to0$, the global density evolution can be
+   simplified as
    \begin{equation}
-      \left(\frac{H}{H_0}\right)^2=\Omega_{2,0}a^{-3}+\Omega_{1,0}a^{n},
+      \rho(\alpha)=C_1 a^{n}+\frac{1}{C_2} a^{-3},
+      \label{eq:11}
    \end{equation}
-   where $\Omega_{2,0}=8\pi G\mathcal{D}/3H_0^2$ and 
-   $\Omega_{1,0}=8\pi GC_1/3H_0^2$, respectively.(\cite{Basilakos_2009})
+   and Eq.(\ref{eq:10}) becomes
+   \begin{equation}
+      \left(\frac{H}{H_0}\right)^2=\Omega_{1,0}\alpha^{n}+\Omega_{2,0}\alpha^{-3}.
+      \label{eq:12}
+   \end{equation}
+   The conditions $n>2$ indicates that the IDM model has an inflection point (\cite{Basilakos_2009}),
+   and we define $w_{\text{IDM}}=-1-n/3$ as the equation of state (EoS) of the IDM model.
+   This solution is mathematically equivalent to that of the gravitational matter 
+   creation model of \cite{Lima_2008}.
 
-\section{Dataset}
+\section{Dataset}\label{sec:3}
 
@@
    \begin{equation}
-      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},\label{eq:12}
+      H(z)=-\frac{1}{1+z}\frac{\mathrm{d}z}{\mathrm{d}t},
+      \label{eq:13}
    \end{equation}
@@
       \chi_{\text{OHD}}^2=\sum_i\frac{(H_{\text{th}}-H_{\text{data}})^2}{\sigma_i^2}.
+      \label{eq:14}
    \end{equation}
@@
          1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
-         \hline    
+         \hline\hline    
       \end{tabular}
@@
       \chi_{\text{SNe}}^2=\Delta C^{-1} \Delta^{\text{T}},
+      \label{eq:15}
    \end{equation}
@@
    \begin{equation}
-      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.\label{eq:15}
+      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.
+      \label{eq:16}
    \end{equation}
@@
       \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{\mathcal{C}}+\ln\left(\frac{\mathcal{C}}{2\pi}\right),
+      \label{eq:17}
    \end{equation}
@@
    DESI DR2 (\cite{desicollaboration2025desidr2resultsii}),
-   which are given at Table \ref{tab:2} and Table \ref{tab:3}, respectively.
+   which are given at Table \ref{tab:2} respectively.
    The redshift is up to 2.33 both in the SDSS and the DESI 2024 dataset.
@@
       \chi_{\text{BAO}}^2=\sum_i\frac{(D_{\text{th}}/r_{\text{d}}-D_{\text{data}}/r_{\text{d}})^2}{\sigma_i^2},
+      \label{eq:18}
    \end{equation}
@@
       D_{\text{V}}(z)&=&\left[zD_{\text{M}}^2(z)D_{\text{H}}(z)\right]^{1/3},
+      \label{eq:19-21}
    \end{eqnarray}
@@
       r_{\text{d}}=\int_{z_{\text{drag}}}^{\infty}\frac{c_s(z')\text{d}z'}{H(z')},
+      \label{eq:22}
    \end{equation}
@@
       \centering
-      \begin{tabular}{lcccc}
+      \begin{tabular}{l|l|cccc}
          \hline\hline
-         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
+         Dataset & Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
          $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
          \hline
-         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
-         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
-         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
-         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
-         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
-         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
-         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
-         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
+         \textbf{SDSS-IV} & MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
+                      & BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
+                      & BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
+                      & eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
+                      & eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
+                      & eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
+                      & Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
+                      & Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
+         \hline\hline
+         \textbf{DESI DR2} & BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
+                           & LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
+                           & LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
+                           & LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
+                           & ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
+                           & QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
+                           & Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
          \hline
+                           & LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
+                           & ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
+         \hline\hline
       \end{tabular}
-      \caption{The BAO+RSD measurements dataset from SDSS-IV.}
+      \caption{The BAO+RSD measurements dataset from SDSS-IV and DESI DR2.}
       \label{tab:2}
@@
 
-   \begin{table*}
-      \centering
-      \begin{tabular}{lcccc}
-         \hline\hline
-         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
-         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
-         \hline
-         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
-         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
-         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
-         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
-         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
-         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
-         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
-         \hline
-         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
-         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
-         \hline
-      \end{tabular}
-      \caption{The BAO dataset from DESI DR2.}
-      \label{tab:3}
-   \end{table*}
-
-\section{Constraint results}
+\section{Constraint results}\label{sec:4}
 
@@
    Besides, we also add the parameter $H_0$ or $h$ to give the constraints
-   to the dark matter particle mass $M_x$.
-   The prior range set for free parameters are given at Table \ref{tab:4}
+   to the dark matter particle mass $M_{\chi}$.
+   The prior range set for free parameters are given at Table \ref{tab:3}
 
@@
          $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
-         $n$ & 0 & $\mathcal{U}[-10,10]$ \\
+         $n$ & 0 & $\mathcal{U}[-5,5]$ \\
          $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
@@
       within the prior range.}
-      \label{tab:4}
+      \label{tab:3}
    \end{table}
@@
    we use $h \simeq 0.7$ as the default value to calculate the 
-   dark matter particle mass $M_x$
+   annihilation parameter $\kappa$ and dark matter particle mass $M_{\chi}$.
 
@@
    could only give the upper limit of what, and give the lower limit
-   of $M_x$ according to Eq.(\ref{eq:9}), respectively.
+   of $M_{\chi}$ according to Eq.(\ref{eq:9}), respectively. We 
+   assume the dark matter annihilation cross section in IDM model
+   a constant that $\langle\sigma v\rangle \simeq 10^{-23}\text{cm}^{3}\text{s}^{-1}$.
 
-   We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
-   limits of the parameters. The  constraint results are shown in 
-   Figure \ref{fig:1} and summarized in Table \ref{tab:5}.
+   We use the 95\% and 5\% quantiles to determine the upper and lower
+   bounds of the parameters. The  constraint results are shown in 
+   Figure \ref{fig:1} and summarized in Table \ref{tab:4}.
 
@@
       \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_sne_1.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_1.pdf}
       }
@@
       \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_sne_2.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_2.pdf}
       }
@@
       \caption{The constraint result from the supernovae Ia data
-      (left), the BAO + SNe Ia data (middle) and the BAO + SNe Ia + OHD data (right).}
+      (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
       \label{fig:1}
@@
          \hline\hline
-         Model 1 & SNe Ia & BAO + SNe Ia & BAO + SNe Ia + OHD \\
+         Model 1 & SNe Ia & BAO & BAO + SNe Ia + OHD \\
          \hline
          $\Omega_{2,0}$ & $0.380_{-0.020}^{+0.020}$
-          & $0.3078_{-0.0067}^{+0.0053}$ & $0.3079_{-0.0067}^{+0.0051}$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.73$ 
-         & $<-3.70$  & $<-3.71$ \\
-         $\log_{10}(M_x/$GeV) & $>-9.26$
-         & $>-8.24$ & $>-8.26$ \\
+          & $0.2980_{-0.0070}^{+0.0070}$ & $0.3079_{-0.0067}^{+0.0051}$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-3.05$ 
+         & $<-3.66$  & $<-3.99$ \\
+         $\log_{10}(M_{\chi}/$GeV) & $>-8.94$
+         & $>-8.28$ & $>-7.97$ \\
          \hline
@@
       \caption{The constraint results of Model 1.}
-      \label{tab:5}
+      \label{tab:4}
    \end{table*}
@@
 
-   We use the most combined dataset of OHD + SNe Ia + BAO to give a stringent lower limit
-   of $\log_{10}(M_x/$GeV) $\simeq -8.26$ at $2\sigma$ level, similar to the 
-   sub-MeV mass of the interacting dark matter.
-
 \subsection{Model 2: mimicking the wCDM model}
 
-   The constraint results of Model 2 are shown in Table \ref{tab:6}.
+   The constraint results of Model 2 are shown in Table \ref{tab:5}.
 
@@
       \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_sne_widm_1.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_widm_1.pdf}
       }
@@
       \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_sne_widm_2.pdf}
+         \includegraphics[width=0.3\textwidth]{bao_widm_2.pdf}
       }
@@
       \caption{The constraint result from the supernovae Ia data
-      (left), the BAO + SNe Ia data (middle) and the BAO + SNe Ia + OHD data (right).}
+      (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
    \end{figure*}
@@
          \hline\hline
-         Model 2 & SNe Ia & SNe Ia + BAO
-          & OHD + SNe Ia + BAO \\
+         Model 2 & SNe Ia & BAO & BAO + SNe Ia + OHD \\
          \hline
          $\Omega_{2,0}$ & $0.215_{-0.073}^{+0.10}$
-          & $0.2940_{-0.0076}^{+0.0076}$ & $0.2945_{-0.0075}^{+0.0075}$ \\
+          & $0.2952_{-0.0073}^{+0.0073}$ & $0.2945_{-0.0075}^{+0.0075}$ \\
          $n$ & $-0.82_{-0.45}^{+0.29}$
-          & $-0.43_{-0.10}^{+0.10}$ & $-0.42_{-0.11}^{+0.11}$ \\
+          & $-0.29_{-0.18}^{+0.15}$ & $-0.42_{-0.11}^{+0.11}$ \\
          $w_{\text{IDM}}$ & $-0.73_{-0.10}^{+0.15}$
-          & $-0.86_{-0.03}^{+0.03}$ & $-0.86_{-0.04}^{+0.04}$ \\
+          & $-0.90_{-0.05}^{+0.06}$ & $-0.86_{-0.04}^{+0.04}$ \\
          \hline
@@
       \caption{The constraint results of Model 2.}
-      \label{tab:6}
+      \label{tab:5}
    \end{table*}
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:5}
 

### 2025-06-02 wIDM/caculus.py

@@ -32,10 +32,11 @@ def chi_square_OHD(O20, n, H0):
     return chi2
 
 ### SNe Ia
-file_path_SNe = "./SNe/Pantheon+ data/Pantheon+SH0ES.dat"
-pandata_SNe = np.loadtxt(file_path_SNe, skiprows=1, usecols=(2, 10))
-z_hd = pandata_SNe[:, 0]
-mu = pandata_SNe[:, 1]
+file_path = "./SNe/Pantheon+ data/Pantheon+SH0ES.dat"
+data = np.loadtxt(file_path, skiprows=1, usecols=(4, 6, 10))
+z_cmb = data[:, 0]
+z_hel = data[:, 1]
+mu = data[:, 2]
 
 file_path_cov = './SNe/Pantheon+ data/Pantheon+SH0ES_cov.dat'
 cov = np.loadtxt(file_path_cov, skiprows=1)
@@ -44,10 +45,10 @@ cov_matrix_inv = np.linalg.inv(cov_matrix)
 
 def chi_square_SNe(O20, n, H0):
     dl = []
-    for z in z_hd:
+    for z in z_cmb:
         int_value = scipy.integrate.quad(H_ad, 0, z, args=(O20, n, H0))[0]
-        dl.append(const_c*(1 + z)*int_value)
-    dl = np.array(dl)
+        dl.append(const_c * int_value)
+    dl = np.array(dl) * (1 + z_hel)
     muth = 5 * np.log10(dl) + 25
     delta_mu = muth - mu
     A = delta_mu @ cov_matrix_inv @ delta_mu.T

### 2025-06-02 wIDM/methods3.py

@@ -1,9 +1,7 @@
 import numpy as np
 import scipy
-import matplotlib.pyplot as plt
 import multiprocessing as mp
 import emcee
-from getdist import plots, MCSamples
 
 import sys
 import os
@@ -42,3 +40,7 @@ def main():
 
     flat_samples = sampler.get_chain(discard=500, flat=True)
     np.savetxt('./wIDM/output/m3.dat', flat_samples)
+
+if __name__ == "__main__":
+    mp.freeze_support()
+    main()

### 2025-06-02 wIDM/new/BAO.py

@@ -1,0 +1,41 @@
+import numpy as np
+import multiprocessing as mp
+import emcee
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '.'))
+from caculus import chi_square_BAO
+
+def lnlike(paras):
+    log_kC1, O20, n, H0, rdh = paras
+    chi2 = chi_square_BAO(log_kC1, O20, n, H0, rdh)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    log_kC1, O20, n, H0, rdh = paras
+    if -10 < log_kC1 < 0 and 0 < O20 < 1 and -5 < n < 10 and 50 < H0 < 100 and 50 < rdh < 150:
+        return 0.0
+    return -np.inf
+
+def lnprob(paras):
+    lp = lnprior(paras)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(paras)
+
+def main():
+    initial = np.array([-5.0, 0.3, 0, 70, 100]) # expected best values
+    pos = initial + 1e-4 * np.random.randn(50, 5)
+    nwalkers, ndim = pos.shape
+
+    with mp.Pool() as pool:
+        sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
+        sampler.run_mcmc(pos, 5000, progress = True)
+
+    flat_samples = sampler.get_chain(discard=500, flat=True)
+    np.savetxt('./wIDM/new/output/bao.dat', flat_samples)
+
+if __name__ == "__main__":
+    mp.freeze_support()
+    main()

### 2025-06-02 wIDM/new/SNe.py

@@ -1,0 +1,41 @@
+import numpy as np
+import multiprocessing as mp
+import emcee
+
+import sys
+import os
+sys.path.append(os.path.join(os.path.dirname(__file__), '.'))
+from caculus import chi_square_SNe
+
+def lnlike(paras):
+    log_kC1, O20, n, H0 = paras
+    chi2 = chi_square_SNe(log_kC1, O20, n, H0)
+    return -0.5 * chi2
+
+def lnprior(paras):
+    log_kC1, O20, n, H0 = paras
+    if -10 < log_kC1 < 0 and 0 < O20 < 1 and -5 < n < 10 and 50 < H0 < 100:
+        return 0.0
+    return -np.inf
+
+def lnprob(paras):
+    lp = lnprior(paras)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(paras)
+
+def main():
+    initial = np.array([-5.0, 0.3, 0, 70]) # expected best values
+    pos = initial + 1e-4 * np.random.randn(50, 4)
+    nwalkers, ndim = pos.shape
+
+    with mp.Pool() as pool:
+        sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, pool=pool)
+        sampler.run_mcmc(pos, 5000, progress = True)
+
+    flat_samples = sampler.get_chain(discard=500, flat=True)
+    np.savetxt('./wIDM/new/output/sne.dat', flat_samples)  
+
+if __name__ == "__main__":
+    mp.freeze_support()
+    main()

### 2025-06-02 wIDM/new/caculus.py

@@ -1,0 +1,164 @@
+import numpy as np
+import scipy
+from decimal import Decimal, getcontext
+
+import scipy.integrate
+import scipy.interpolate
+getcontext().prec = 100
+
+import astropy.constants as const
+import astropy.units as u
+
+const_c =  const.c.value / 1000
+
+distance_mpc = 1 * u.Mpc
+distance_km = distance_mpc.to(u.km)
+time_gyr = 1 * u.Gyr
+time_s = time_gyr.to(u.s)
+# Unit conversion (1/H0 to Gyr)
+transfer = (distance_km / time_s).value
+
+def solution(log_kC1, O20, n, H0, zmax):
+    Omega_1_0 = 1 - O20
+    Omega_2_0 = O20
+    k = 10**log_kC1 * transfer
+
+    def derivatives(a, y):
+        H, I1, I2 = y
+
+        xp_arg = np.clip(-2 * k * I1, -700, 700)
+
+        dI1da = a**(n - 1) / H
+        dI2da = (a**(-4)) / H * np.exp(xp_arg)
+        
+        N = Omega_2_0 * a**(-3) * np.exp(xp_arg)
+        
+        # D = 1 + (Omega_2_0 / Omega_1_0) * k * I2
+        D = Decimal(1) + Decimal(Omega_2_0 / Omega_1_0) * Decimal(k) * Decimal(I2)
+        D = float(D)
+        
+        dN_da = Omega_2_0 * (-3 * a**(-4) * np.exp(xp_arg) + 
+                a**(-3) * np.exp(xp_arg) * (-2*k) * dI1da)
+        
+        dD_da = (Omega_2_0 / Omega_1_0) * k * dI2da
+        
+        # Term2_prime = (dN_da * D - N * dD_da) / D**2
+        Term2_prime = Decimal(dN_da) / Decimal(D) - Decimal(N) / Decimal(D) * Decimal(dD_da) / Decimal(D)
+        Term2_prime = float(Term2_prime)
+
+        dHda = (H0**2 / (2 * H)) * (n * Omega_1_0 * a**(n-1) + Term2_prime)
+        
+        return [dHda, dI1da, dI2da]
+    
+    a_initial = 1.0
+    y_initial = [H0, 0.0, 0.0]  # H(1)=H0, I1(1)=0, I2(1)=0
+
+    a_end = 1 / (1 + zmax)
+    a_span = (a_initial, a_end)
+
[…]

### 2025-06-03 article/article.tex
remove the figures

@@
 
-   We use the fiducial SNe Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
-   host distances (\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
-   give the $\chi^2$ as 
+   The $\chi^2$ of SNe Ia can be defined as 
    \begin{equation}
-      \chi_{\text{SNe}}^2=\Delta C^{-1} \Delta^{\text{T}},
+      \chi_{\text{SNe}}^2=\Delta C^{-1} \Delta^{\text{T}}-\frac{B^2}{\mathcal{C}}+\ln\left(\frac{\mathcal{C}}{2\pi}\right),
       \label{eq:15}
    \end{equation}
-   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
-   covariance matrix of the SNe Ia data, the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
-   luminosity distance $d_L$ can be given as a function of redshift $z$
+   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$, $C^{-1}$ is the inverse of the
+   covariance matrix of the SNe Ia data, $B$ is the sum of $\Delta C^{-1}$ and 
+   $\mathcal{C}$ is the sum of $C^{-1}$, the distance modulus is 
+   $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the luminosity distance $d_L$ 
+   can be given as a function of redshift $z$
    \begin{equation}
@@
    \end{equation}
-   To eliminate the advanced restriction to $H_0$ from $M_b$, we adopt
-   the likelihood function as
-   \begin{equation}
-      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{\mathcal{C}}+\ln\left(\frac{\mathcal{C}}{2\pi}\right),
-      \label{eq:17}
-   \end{equation}
-   where $B$ is the sum of $\Delta C^{-1}$ and $\mathcal{C}$ is the sum of $C^{-1}$.
 
@@
       \chi_{\text{BAO}}^2=\sum_i\frac{(D_{\text{th}}/r_{\text{d}}-D_{\text{data}}/r_{\text{d}})^2}{\sigma_i^2},
-      \label{eq:18}
+      \label{eq:17}
    \end{equation}
@@
       D_{\text{V}}(z)&=&\left[zD_{\text{M}}^2(z)D_{\text{H}}(z)\right]^{1/3},
-      \label{eq:19-21}
+      \label{eq:18-20}
    \end{eqnarray}
@@
       r_{\text{d}}=\int_{z_{\text{drag}}}^{\infty}\frac{c_s(z')\text{d}z'}{H(z')},
-      \label{eq:22}
+      \label{eq:21}
    \end{equation}
@@
 
-   However, the solution of Eq.(\ref{eq:8}) only gives an upper 
-   limit of redshift $z_{\max}$ (see Appendix), and the cross 
+   Mathematically, the solution of Eq.(\ref{eq:8}) will encounter the singularity
+   at the upper limit of the redshift $z_{\max}$ (see Appendix), and the cross 
    parameter $r_{\text{d}}h$ is used to give the constraints.
@@
       \centering
-      \begin{tabular}{l|l|cccc}
+      \begin{tabular}{l|cccc}
          \hline\hline
-         Dataset & Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
+         Dataset/Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
          $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
          \hline
-         \textbf{SDSS-IV} & MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
-                      & BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
-                      & BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
-                      & eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
-                      & eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
-                      & eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
-                      & Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
-                      & Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
+         \textbf{SDSS-IV} \\
+         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
+         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
+         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
+         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
+         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
+         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
+         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
+         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
          \hline\hline
-         \textbf{DESI DR2} & BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
-                           & LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
-                           & LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
-                           & LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
-                           & ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
-                           & QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
-                           & Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
+         \textbf{DESI DR2} \\ 
+         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
+         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
+         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
+         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
+         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
+         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
+         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
          \hline
-                           & LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
-                           & ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
+         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
+         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
          \hline\hline
@@
 
-\section{Constraint results}\label{sec:4}
+\section{Constraint results and discussion}\label{sec:4}
+
+\subsection{Constraint results to the IDM model}
 
@@
    Model 1 and $n$ in Model 2.
-   Besides, we also add the parameter $H_0$ or $h$ to give the constraints
-   to the dark matter particle mass $M_{\chi}$.
-   The prior range set for free parameters are given at Table \ref{tab:3}
+   The prior range set for free parameters are given at Table \ref{tab:3}.
 
@@
          $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
          $n$ & 0 & $\mathcal{U}[-5,5]$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
-         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
          \hline
+         $H_0$[km/(s$\cdot$Mpc)] & 70 & $\mathcal{U}[60,80]$ \\
          $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
@@
 
+   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
+   $\log_{10}(\kappa C_1)\to-\infty$, thus the constraints
+   could only give the upper limit of what, and we use the
+   95\% quantiles to determine the upper bounds of the parameters. 
+   The constraint results are shown in 
+   Figure \ref{fig:1}-\ref{fig:3} and summarized in Table \ref{tab:4}.
+
    For the dataset which cannot give a constraint to $H_0$, 
    we use $h \simeq 0.7$ as the default value to calculate the 
-   annihilation parameter $\kappa$ and dark matter particle mass $M_{\chi}$.
+   annihilation parameter $\kappa$.
 
-\subsection{Model 1: mimicking the ΛCDM model}
+   \begin{table*}
+      \centering
+      \begin{tabular}{l|ccccc}
+         \hline\hline
+         Model/Dataset & $\Omega_{2,0}$ & $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $10^{15}\kappa$[cm${}^3$/(s$\cdot$GeV)] & $n$ & $w_{\text{IDM}}$ \\
+         \hline
+         \textbf{Model 1} \\
+         SNe Ia & $0.380 \pm 0.020$ & $<-3.05$ & $<8.82$ & --- & --- \\
+         BAO & $0.2980 \pm 0.0070$ & $<-3.66$ & $<1.91$ & --- & --- \\
+         BAO + SNe Ia + OHD & $0.3079_{-0.0067}^{+0.0051}$ & $<-3.99$ & $<0.907$ & --- & --- \\
+         \hline
+         \textbf{Model 2 ($\kappa=0$)} \\
+         SNe Ia & $0.215_{-0.073}^{+0.10}$ & --- & --- & $-0.82_{-0.45}^{+0.29}$ & $-0.73_{-0.10}^{+0.15}$ \\
+         BAO & $0.2952 \pm 0.0073$ & --- & --- & $-0.29_{-0.18}^{+0.15}$ & $-0.90_{-0.05}^{+0.06}$ \\
+         BAO + SNe Ia + OHD & $0.2945 \pm 0.0075$ & --- & --- & $-0.42 \pm 0.11$ & $-0.86 \pm 0.04$ \\
+         \hline
+         \textbf{Model 2 ($\kappa\neq0$)} \\
+         SNe Ia & $0.143_{-0.11}^{+0.067}$ & $<-2.15$ & $<50.7$ &  $-1.17_{-0.35}^{+0.17}$ & $-0.61_{-0.06}^{+0.12}$ \\
+         BAO & $0.287_{-0.0022}^{+0.017}$ & $<-2.44$ & $<31.3$ & $-0.34_{-0.17}^{+0.22}$ & $-0.89_{-0.07}^{+0.06}$ \\
+         BAO + SNe Ia + OHD & $0.241 \pm 0.062$ & $<-1.90$ & $<101.8$ & $-0.73_{-0.24}^{+0.33}$ & $-0.76_{-0.11}^{+0.08}$ \\
+         \hline\hline
+      \end{tabular}
+      \caption{The constraint results of the IDM model.}
+      \label{tab:4}
+   \end{table*}
 
-   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
-   $\log_{10}(\kappa C_1)\to-\infty$, thus the constraints
-   could only give the upper limit of what, and give the lower limit
-   of $M_{\chi}$ according to Eq.(\ref{eq:9}), respectively. We 
-   assume the dark matter annihilation cross section in IDM model
-   a constant that $\langle\sigma v\rangle \simeq 10^{-23}\text{cm}^{3}\text{s}^{-1}$.
-
-   We use the 95\% and 5\% quantiles to determine the upper and lower
-   bounds of the parameters. The  constraint results are shown in 
-   Figure \ref{fig:1} and summarized in Table \ref{tab:4}.
+\subsection{Compared with other results}
 
@@
       \centering
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{sne_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{sne_2.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_2.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_2.pdf}
-      }
       \caption{The constraint result from the supernovae Ia data
@@
 
-   \begin{table*}
-      \centering
-      \begin{tabular}{lccc}
-         \hline\hline
-         Model 1 & SNe Ia & BAO & BAO + SNe Ia + OHD \\
-         \hline
-         $\Omega_{2,0}$ & $0.380_{-0.020}^{+0.020}$
-          & $0.2980_{-0.0070}^{+0.0070}$ & $0.3079_{-0.0067}^{+0.0051}$ \\
-         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-3.05$ 
-         & $<-3.66$  & $<-3.99$ \\
-         $\log_{10}(M_{\chi}/$GeV) & $>-8.94$
-         & $>-8.28$ & $>-7.97$ \\
-         \hline
-      \end{tabular}
-      \caption{The constraint results of Model 1.}
-      \label{tab:4}
-   \end{table*}
-
    The SNe Ia dataset gives a value $\Omega_{2,0} \simeq 0.38$. The constraint result to Pantheon+
@@
 
-\subsection{Model 2: mimicking the wCDM model}
-
-   The constraint results of Model 2 are shown in Table \ref{tab:5}.
-
    \begin{figure*}
       \centering
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{sne_widm_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_widm_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_widm_1.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{sne_widm_2.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{bao_widm_2.pdf}
-      }
-      \subfigure{
-         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_widm_2.pdf}
-      }
       \caption{The constraint result from the supernovae Ia data
       (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
+      \label{fig:2}
    \end{figure*}
-
-   \begin{table*}
-      \centering
-      \begin{tabular}{lccc}
-         \hline\hline
-         Model 2 & SNe Ia & BAO & BAO + SNe Ia + OHD \\
-         \hline
-         $\Omega_{2,0}$ & $0.215_{-0.073}^{+0.10}$
-          & $0.2952_{-0.0073}^{+0.0073}$ & $0.2945_{-0.0075}^{+0.0075}$ \\
-         $n$ & $-0.82_{-0.45}^{+0.29}$
-          & $-0.29_{-0.18}^{+0.15}$ & $-0.42_{-0.11}^{+0.11}$ \\
-         $w_{\text{IDM}}$ & $-0.73_{-0.10}^{+0.15}$
-          & $-0.90_{-0.05}^{+0.06}$ & $-0.86_{-0.04}^{+0.04}$ \\
-         \hline
-      \end{tabular}
-      \caption{The constraint results of Model 2.}
-      \label{tab:5}
-   \end{table*}
 
@@
       \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
+      \label{fig:3}
    \end{figure}

### 2025-06-11 article/article.tex
add dark matter annihilation

@@
       \end{tabular}
-      \caption{The OHD dataset from different reference.}
+      \caption{
+         The OHD dataset from different reference.
+      }
       \label{tab:1}
@@
       \end{tabular}
-      \caption{The BAO+RSD measurements dataset from SDSS-IV and DESI DR2.}
+      \caption{
+         The BAO+RSD measurements dataset from SDSS-IV and DESI DR2.
+      }
       \label{tab:2}
@@
       \end{tabular}
-      \caption{Parameters and priors used in analysis. 
+      \caption{
+         Parameters and priors used in analysis. 
          All of the priors are flat in the ranges given. 
@@
          and the initial value of each chain is selected randomly uniformly
-      within the prior range.}
+         within the prior range.
+      }
       \label{tab:3}
@@
    The constraint results are shown in 
-   Figure \ref{fig:1}-\ref{fig:3} and summarized in Table \ref{tab:4}.
+   Figure \ref{fig:1}-\ref{fig:2} and summarized in Table \ref{tab:4}.
 
@@
    annihilation parameter $\kappa$.
+   The constraint result to the upper limit of the annihilation parameter 
+   is given in Table \ref{tab:4}, which reaches a value of $\kappa = 9.07 \times 10^{-16}$ cm${}^3$/(s$\cdot$GeV) in Model 1, 
+   and $1.02 \times 10^{-13}$ cm${}^3$/(s$\cdot$GeV) in Model 2 with $\kappa\neq0$ at 95\% confidence level, respectively.
+
+   \begin{figure*}
+      \centering
+      \subfigure{
+         \includegraphics[width=0.45\textwidth]{model1.pdf}
+      }
+      \subfigure{
+         \includegraphics[width=0.45\textwidth]{model2.pdf}
+      }
+      \caption{
+         68\% and 95\% confidence level contours for parameters in 
+         IDM model. The blue, orange and green contours are the results from
+         the SNe Ia dataset, the BAO dataset and the BAO + SNe Ia + OHD dataset, respectively.
+         \emph{Left panel}: constraint results to $\Omega_{2,0}$ and 
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ in Model 1. 
+         \emph{Right panel}: constraint results to $\Omega_{2,0}$ and $n$ in Model 2. 
+         The dashed line is $n=0$, what implies $w_{\text{IDM}}=-1$.
+      }
+      \label{fig:1}
+   \end{figure*}
+
+   \begin{figure*}
+      \centering
+      \includegraphics[width=0.9\textwidth]{model2_kneq0.pdf}
+      \caption{
+         Marginalized 68\% and 95\% posterior constraints on $\Omega_{2,0}$, 
+         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ and $n$ in Model 2 with $\kappa\neq0$,
+         from the SNe Ia dataset (blue), the BAO dataset (orange) and the 
+         combination of BAO + SNe Ia + OHD dataset (green). Noted that
+         the combination of BAO + SNe Ia + OHD dataset gives a two-side constraint
+         to the parameter $\log_{10}(\kappa C_1/$Gyr${}^{-1})$, while we still
+         use the 95\% quantile upper limit to give the constraint.
+         The dashed line is $n=0$, what implies $w_{\text{IDM}}=-1$.
+      }
+      \label{fig:2}
+   \end{figure*}
 
@@
          BAO & $0.2980 \pm 0.0070$ & $<-3.66$ & $<1.91$ & --- & --- \\
-         BAO + SNe Ia + OHD & $0.3079_{-0.0067}^{+0.0051}$ & $<-3.99$ & $<0.907$ & --- & --- \\
+         BAO+SNe Ia+OHD & $0.3079_{-0.0067}^{+0.0051}$ & $<-3.99$ & $<0.907$ & --- & --- \\
          \hline
@@
          BAO & $0.2952 \pm 0.0073$ & --- & --- & $-0.29_{-0.18}^{+0.15}$ & $-0.90_{-0.05}^{+0.06}$ \\
-         BAO + SNe Ia + OHD & $0.2945 \pm 0.0075$ & --- & --- & $-0.42 \pm 0.11$ & $-0.86 \pm 0.04$ \\
+         BAO+SNe Ia+OHD & $0.2945 \pm 0.0075$ & --- & --- & $-0.42 \pm 0.11$ & $-0.86 \pm 0.04$ \\
          \hline
@@
          BAO & $0.287_{-0.0022}^{+0.017}$ & $<-2.44$ & $<31.3$ & $-0.34_{-0.17}^{+0.22}$ & $-0.89_{-0.07}^{+0.06}$ \\
-         BAO + SNe Ia + OHD & $0.241 \pm 0.062$ & $<-1.90$ & $<101.8$ & $-0.73_{-0.24}^{+0.33}$ & $-0.76_{-0.11}^{+0.08}$ \\
+         BAO+SNe Ia+OHD & $0.241 \pm 0.062$ & $<-1.90$ & $<101.8$ & $-0.73_{-0.24}^{+0.33}$ & $-0.76_{-0.11}^{+0.08}$ \\
          \hline\hline
       \end{tabular}
-      \caption{The constraint results of the IDM model.}
+      \caption{
+         Summary table of the parameter constraints from the different datasets in
+         the IDM model. Results for the parameters $\Omega_{2,0}$ and $n$ are the
+         mean values with 68\% confidence level, while the $\log_{10}(\kappa C_1)$
+         is the 95\% quantile upper limit.
+      }
       \label{tab:4}
@@
 
-\subsection{Compared with other results}
+\subsection{The dark matter annihilation}
+
+   We assume that the dark matter particle $\chi$ consists of Weakly Interacting Massive Particles (WIMPs),
+   which can annihilate into Standard Model (SM) particles with a cross section $\langle\sigma v\rangle$, 
+   and the dark matter particle in the IDM model acts as a self-annihilation process.
+
+   The WIMPs assumption gives that the thermal relic abundance of dark matter requires 
+   an annihilation cross section of $\langle\sigma v \rangle $ about $ 3\times 10^{-26}$ cm${}^3$/s
+   to match the observed cosmological density
+   (\cite{PhysRevLett.39.165,annurev:/content/journals/10.1146/annurev.ns.29.120179.001525, GONDOLO1991145}).
+   Adopting this value in the IDM model, the lower limit of the dark matter particle mass can be given as
+   $M_{\chi} \gtrsim 3 \times 10^{-2}$ eV in Model 1 and 
+   $3 \times 10^{-4}$ eV in Model 2 with $\kappa\neq0$.
 
@@
       \centering
-      \caption{The constraint result from the supernovae Ia data
-      (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
-      \label{fig:1}
-   \end{figure*}
-
-   The SNe Ia dataset gives a value $\Omega_{2,0} \simeq 0.38$. The constraint result to Pantheon+
-   SNe Ia dataset in the flat $\Lambda$CDM model is $\Omega_{m} \simeq 0.33$ (\cite{Borghi_2022}),
-
-   \begin{figure*}
-      \centering
-      \caption{The constraint result from the supernovae Ia data
-      (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
-      \label{fig:2}
+      \includegraphics[width=0.9\textwidth]{dm_ann.pdf}
+      \caption{The dark matter annihilation cross section $\langle\sigma v\rangle$ 
+         as a function of the dark matter particle mass $M_{\chi}$ in the IDM model.
+      }
+      \label{fig:3}
    \end{figure*}
@@
       \includegraphics[width=0.7\textwidth]{zmax.pdf}
-      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
+      \caption{The redshift $z_{\max}$ as $H_0=70$ km/(s$\cdot$Mpc)}
       \label{fig:3}
